### 2023-03-02 outputs/paper/paper.qmd
Format report structure

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Sakura Ariga
  - Aliyah Maxine Ramos
  - Annie Yan
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
```

# 1 Introduction

You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.

# 2 Data {#sec-data}

## 2.1 Survey

## 2.2 Questionnaire

Our data is of penguins (@fig-bills).

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

Also bills and their average (@fig-billssssss). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)

```{r}
#| label: fig-billssssss
#| fig-cap: More bills of penguins
#| echo: false
#| fig-width: 8
#| fig-height: 4

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk way more about it.

# Model

$$
Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
$$ {#eq-bayes}

@eq-bayes seems useful, eh?

Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR]. We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.

We can use maths by including latex between dollar signs, for instance $\theta$.

# 3 Results

# 4 Discussion

## 4.1 First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## 4.2 Second discussion point

## 4.3 Third discussion point

## 4.4 Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# 5 Appendix {.unnumbered}

# 6 Additional details

\newpage

# 7 References

### 2023-03-02 scripts/01-download_data.R
imported raw data and started preliminary cleaning.

@@ -16,11 +16,14 @@ library(tidyverse)
 #### Download data ####
 # [...ADD CODE HERE TO DOWNLOAD...]
 
+library(haven)
+library(tidyverse)
 
+raw_2016gss_data <- read_dta("GSS2016.dta")
 
 #### Save data ####
 # [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_csv(the_raw_data, "inputs/data/raw_data.csv") 
+write_dta(raw_2016gss_data, "inputs/data/raw_2016gss_data.dta") 
 
          

### 2023-03-02 scripts/02-data_cleaning.R

@@ -14,13 +14,18 @@ library(tidyverse)
 
 #### Clean data ####
 # [...UPDATE THIS...]
-raw_data <- read_csv("inputs/data/raw_data.csv")
 
+library(haven)
+library(tidyverse)
 
+raw_2016gss_data <- read_dta("inputs/data/raw_2016gss_data.dta")
 
+cleaned_2016gss_data <- 
+  raw_2016gss_data |> 
+  select(starts_with("int"), starts_with("sns"), age, race, income, rincome, educ, degree, health, childs, marital, sex)
 
 #### Save data ####
 # [...UPDATE THIS...]
 # change cleaned_data to whatever name you end up with at the end of cleaning
-write_csv(cleaned_data, "outputs/data/cleaned_data.csv")
+write_dta(cleaned_data, "outputs/data/cleaned_data.dta")
 

### 2023-03-02 scripts/02-data_cleaning.R
Writing cleaned data

@@ -27,5 +27,5 @@ cleaned_2016gss_data <-
 #### Save data ####
 # [...UPDATE THIS...]
 # change cleaned_data to whatever name you end up with at the end of cleaning
-write_dta(cleaned_data, "outputs/data/cleaned_data.dta")
+write_dta(cleaned_2016gss_data, "outputs/data/cleaned_2016gss_data.dta")
 

### 2023-03-02 scripts/02-data_cleaning.R
Did some more data cleaning.

@@ -22,7 +22,7 @@ raw_2016gss_data <- read_dta("inputs/data/raw_2016gss_data.dta")
 
 cleaned_2016gss_data <- 
   raw_2016gss_data |> 
-  select(starts_with("int"), starts_with("sns"), age, race, income, rincome, educ, degree, health, childs, marital, sex)
+  select(intuse, intmbile, intrecnt, twitter, facebook, instagrm, linkedin, snapchat, tumblr, whatsapp, googlesn, pinterst, flickr, vine, clssmtes, starts_with("sns"), wwwhr, wwwmin, age, race, income, rincome, educ, childs, marital, sex)
 
 #### Save data ####
 # [...UPDATE THIS...]

### 2023-03-02 scripts/01-download_data.R
update download data

@@ -24,6 +24,6 @@ raw_2016gss_data <- read_dta("GSS2016.dta")
 #### Save data ####
 # [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_dta(raw_2016gss_data, "inputs/data/raw_2016gss_data.dta") 
+write_csv(raw_2016gss_data, "inputs/data/raw_2016gss_data.csv") 
 
          

### 2023-03-02 scripts/02-data_cleaning.R
update data cleaning

@@ -18,7 +18,7 @@ library(tidyverse)
 library(haven)
 library(tidyverse)
 
-raw_2016gss_data <- read_dta("inputs/data/raw_2016gss_data.dta")
+raw_2016gss_data <- read_csv("inputs/data/raw_2016gss_data.csv")
 
 cleaned_2016gss_data <- 
   raw_2016gss_data |> 
@@ -27,5 +27,5 @@ cleaned_2016gss_data <-
 #### Save data ####
 # [...UPDATE THIS...]
 # change cleaned_data to whatever name you end up with at the end of cleaning
-write_dta(cleaned_2016gss_data, "outputs/data/cleaned_2016gss_data.dta")
+write_csv(cleaned_2016gss_data, "outputs/data/cleaned_2016gss_data.csv")
 

### 2023-03-02 scripts/01-download_data.R
Removed "library(opendatatoronto)".

@@ -9,7 +9,6 @@
 
 
 #### Workspace setup ####
-library(opendatatoronto)
 library(tidyverse)
 # [...UPDATE THIS...]
 

### 2023-03-02 scripts/01-download_data.R
Update cleaned data

@@ -9,15 +9,10 @@
 
 
 #### Workspace setup ####
-library(opendatatoronto)
-library(tidyverse)
-# [...UPDATE THIS...]
-
-#### Download data ####
-# [...ADD CODE HERE TO DOWNLOAD...]
-
 library(haven)
 library(tidyverse)
+
+#### Download data ####
 
 raw_2016gss_data <- read_dta("GSS2016.dta")
 

### 2023-03-02 scripts/02-data_cleaning.R

@@ -10,14 +10,9 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+library(haven)
 
 #### Clean data ####
-# [...UPDATE THIS...]
-
-library(haven)
-library(tidyverse)
-
 raw_2016gss_data <- read_dta("inputs/data/raw_2016gss_data.dta")
 
 cleaned_2016gss_data <- 
@@ -25,7 +20,6 @@ cleaned_2016gss_data <-
   select(intuse, intmbile, intrecnt, twitter, facebook, instagrm, linkedin, snapchat, tumblr, whatsapp, googlesn, pinterst, flickr, vine, clssmtes, starts_with("sns"), wwwhr, wwwmin, age, race, income, rincome, educ, childs, marital, sex)
 
 #### Save data ####
-# [...UPDATE THIS...]
 # change cleaned_data to whatever name you end up with at the end of cleaning
 write_dta(cleaned_2016gss_data, "outputs/data/cleaned_2016gss_data.dta")
 

### 2023-03-02 scripts/01-download_data.R
Update script

@@ -9,7 +9,10 @@
 
 
 #### Workspace setup ####
+<<<<<<< HEAD
 library(haven)
+=======
+>>>>>>> 63a9385e6e37c8970f7df55844df1669c4164ed1
 library(tidyverse)
 
 #### Download data ####
@@ -19,6 +22,6 @@ raw_2016gss_data <- read_dta("GSS2016.dta")
 #### Save data ####
 # [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
-write_dta(raw_2016gss_data, "inputs/data/raw_2016gss_data.dta") 
+write_csv(raw_2016gss_data, "inputs/data/raw_2016gss_data.csv") 
 
          

### 2023-03-02 scripts/02-data_cleaning.R

@@ -12,8 +12,12 @@
 library(tidyverse)
 library(haven)
 
+<<<<<<< HEAD
 #### Clean data ####
 raw_2016gss_data <- read_dta("inputs/data/raw_2016gss_data.dta")
+=======
+raw_2016gss_data <- read_csv("inputs/data/raw_2016gss_data.csv")
+>>>>>>> 63a9385e6e37c8970f7df55844df1669c4164ed1
 
 cleaned_2016gss_data <- 
   raw_2016gss_data |> 
@@ -21,5 +25,5 @@ cleaned_2016gss_data <-
 
 #### Save data ####
 # change cleaned_data to whatever name you end up with at the end of cleaning
-write_dta(cleaned_2016gss_data, "outputs/data/cleaned_2016gss_data.dta")
+write_csv(cleaned_2016gss_data, "outputs/data/cleaned_2016gss_data.csv")
 

### 2023-03-02 scripts/01-download_data.R
Update script

@@ -9,10 +9,7 @@
 
 
 #### Workspace setup ####
-<<<<<<< HEAD
 library(haven)
-=======
->>>>>>> 63a9385e6e37c8970f7df55844df1669c4164ed1
 library(tidyverse)
 
 #### Download data ####

### 2023-03-02 scripts/02-data_cleaning.R
Ultimate update script

@@ -12,12 +12,10 @@
 library(tidyverse)
 library(haven)
 
-<<<<<<< HEAD
+
 #### Clean data ####
-raw_2016gss_data <- read_dta("inputs/data/raw_2016gss_data.dta")
-=======
+
 raw_2016gss_data <- read_csv("inputs/data/raw_2016gss_data.csv")
->>>>>>> 63a9385e6e37c8970f7df55844df1669c4164ed1
 
 cleaned_2016gss_data <- 
   raw_2016gss_data |> 

### 2023-03-02 scripts/00-simulate_data.R
Update script

@@ -10,7 +10,6 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
 
 #### Simulate data ####
 # [...ADD CODE HERE...]

### 2023-03-02 scripts/02-data_cleaning.R

@@ -19,7 +19,8 @@ raw_2016gss_data <- read_csv("inputs/data/raw_2016gss_data.csv")
 
 cleaned_2016gss_data <- 
   raw_2016gss_data |> 
-  select(intuse, intmbile, intrecnt, twitter, facebook, instagrm, linkedin, snapchat, tumblr, whatsapp, googlesn, pinterst, flickr, vine, clssmtes, starts_with("sns"), wwwhr, wwwmin, age, race, income, rincome, educ, childs, marital, sex)
+  select(intuse, intmbile, intrecnt, wwwhr, wwwmin, age, race, income, rincome, educ, childs, marital, sex, happy)
+  # focus on internet and other variables
 
 #### Save data ####
 # change cleaned_data to whatever name you end up with at the end of cleaning

### 2023-03-02 scripts/03-rough_work.R
Adding rough work script

@@ -1,0 +1,8 @@
+#### Preamble ####
+# Purpose: Rough work.
+# Author: Sakura Ariga, Annie Yan, Aliyah Maxine Ramos
+# Data: 2  March 2023
+# Contact: aliyahmaxine.ramos@mail.utoronto.ca
+# License: MIT
+# Pre-requisites: None.
+# Any other information needed? None

### 2023-03-02 scripts/03-rough_work.R
Update script

@@ -6,3 +6,11 @@
 # License: MIT
 # Pre-requisites: None.
 # Any other information needed? None
+
+#### Graphs ####
+
+
+
+#### Tables ####
+
+

### 2023-03-02 scripts/00-simulate_data.R
update script

@@ -16,3 +16,37 @@ library(tidyverse)
 
 
 
+set.seed(853)
+
+simulated_bullying_data <-
+  tibble(
+    Date = rep(x = as.Date("2021-01-01") + c(0:364), times = 3),
+    
+    State = c(
+      rep(x = "AK", times = 365),
+      rep(x = "CA", times = 365),
+      rep(x = "NY", times = 365)
+    ),
+    
+    Cyberbullying =
+      rpois(
+        n = 365 * 3,
+        lambda = 10
+      ),
+    
+    Schoolbullying =
+      rpois(
+        n = 365 * 3,
+        lambda = 20
+      ),
+    
+    School_cyber_bullying =
+      rpois(
+        n = 365 * 3,
+        lambda = 80
+      )
+    
+  )
+
+
+head(simulated_bullying_data)

### 2023-03-02 scripts/03-rough_work.R

@@ -9,7 +9,18 @@
 
 #### Graphs ####
 
+library(tidyverse)
 
+sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
+  labs(
+    x = "Date",
+    y = "Search Frequency",
+    fill = "State Name"
+  )
 
 #### Tables ####
 

### 2023-03-02 scripts/03-rough_work.R
First set of graphs made

@@ -11,16 +11,63 @@
 
 library(tidyverse)
 
-sum_bully_data |> ggplot(aes(x = date, y = sum)) + 
+# Age VS. Internet Hours
+cleaned_2016gss_data |> ggplot(aes(x = age, y = wwwhr)) + 
   geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
         axis.line = element_line(colour = "black"),
         title = element_text(size = 8)) +
   labs(
-    x = "Date",
-    y = "Search Frequency",
-    fill = "State Name"
+    x = "Age",
+    y = "Internet Hours"
   )
+
+# Income VS. Internet Hours
+cleaned_2016gss_data |> ggplot(aes(x = income, y = wwwhr)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
+  labs(
+    x = "Income",
+    y = "Internet Hours"
+  )
+
+# Education VS. Internet Hours
+cleaned_2016gss_data |> ggplot(aes(x = educ, y = wwwhr)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
+  labs(
+    x = "Education",
+    y = "Internet Hours"
+  )
+# REMINDER: find average THEN graph
+
+# Sex VS. Internet Hours
+cleaned_2016gss_data |> ggplot(aes(x = sex, y = wwwhr)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
+  labs(
+    x = "Sex",
+    y = "Internet Hours"
+  )
+# REMINDER: find average THEN graph
+
+# Race VS. Internet Hours
+cleaned_2016gss_data |> ggplot(aes(x = race, y = wwwhr)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 8)) +
+  labs(
+    x = "Race",
+    y = "Internet Hours"
+  )
+# REMINDER: find average THEN graph
 
 #### Tables ####
 

### 2023-03-12 scripts/03-rough_work.R
Added graphs to demonstrate each variable and the number of respondents for each survey option under that variable.

@@ -20,7 +20,71 @@ library(reshape2)
 cleaned_2016gss_data <- read_csv("outputs/data/cleaned_2016gss_data.csv")
 
 
+# BAR GRAPHS SHOWING EACH VARIABLE AND HOW MANY RESPONDENTS ARE IN EACH CATEGORY
 
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = `Age Group`)) +
+  geom_bar() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(x = "Age", y = "Number of Respondents")
+
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = Sex)) +
+  geom_bar() +
+  labs(x = "Sex", y = "Number of Respondents")
+
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = Race)) +
+  geom_bar() +
+  labs(x = "Race", y = "Number of Respondents")
+
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = Race)) +
+  geom_bar() +
+  labs(x = "Race", y = "Number of Respondents")
+
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = `Personal Income`)) +
+  geom_bar() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(x = "Personal Income", y = "Number of Respondents")
+
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = `Total Family Income`)) +
+  geom_bar() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(x = "Total Family Income", y = "Number of Respondents")
+
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = `Highest Education Obtained`)) +
+  geom_bar() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(x = "Education", y = "Number of Respondents")
+
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = `Number of Children`)) +
+  geom_bar() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(x = "Number of Children", y = "Number of Respondents")
+
+
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = `Marital Status`)) +
+  geom_bar() +
[…]

### 2023-03-12 scripts/03-rough_work.R
Added graphs for each variable to demonstrate the number of respondents for each variable and their survey options

@@ -20,75 +20,79 @@ library(reshape2)
 cleaned_2016gss_data <- read_csv("outputs/data/cleaned_2016gss_data.csv")
 
 
-# BAR GRAPHS SHOWING EACH VARIABLE AND HOW MANY RESPONDENTS ARE IN EACH CATEGORY
+### BAR GRAPHS OF EACH VARIABLE to show how many respondents for each option ###
 
+# age
 cleaned_2016gss_data |>
   ggplot(mapping = aes(x = `Age Group`)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Age", y = "Number of Respondents")
 
+# sex
 cleaned_2016gss_data |>
   ggplot(mapping = aes(x = Sex)) +
   geom_bar() +
   labs(x = "Sex", y = "Number of Respondents")
 
+# race
 cleaned_2016gss_data |>
   ggplot(mapping = aes(x = Race)) +
   geom_bar() +
   labs(x = "Race", y = "Number of Respondents")
 
-cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = Race)) +
-  geom_bar() +
-  labs(x = "Race", y = "Number of Respondents")
-
+# personal income
 cleaned_2016gss_data |>
   ggplot(mapping = aes(x = `Personal Income`)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Personal Income", y = "Number of Respondents")
 
+# total family income
 cleaned_2016gss_data |>
   ggplot(mapping = aes(x = `Total Family Income`)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Total Family Income", y = "Number of Respondents")
 
+# education
 cleaned_2016gss_data |>
   ggplot(mapping = aes(x = `Highest Education Obtained`)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Education", y = "Number of Respondents")
 
+# number of children
 cleaned_2016gss_data |>
   ggplot(mapping = aes(x = `Number of Children`)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Number of Children", y = "Number of Respondents")
 
-
[…]

### 2023-03-12 scripts/03-rough_work.R
Added package ggplot2

@@ -14,6 +14,7 @@ library(lessR)
 library(dplyr)
 library(tidyr)
 library(reshape2)
+library(ggplot2)
 
 
 #read csv

### 2023-03-12 scripts/02-data_cleaning.R
Removed "intuse" and "intrecnt" variables from our dataset and analysis.

@@ -20,7 +20,7 @@ raw_2016gss_data <- read_csv("inputs/data/raw_2016gss_data.csv")
 # Focus on internet variables and demographic variables
 cleaned_2016gss_data <- 
   raw_2016gss_data |> 
-  select(age, sex, race, income, rincome, degree, childs, marital, happy, intuse, intmbile, intrecnt, wwwhr)
+  select(age, sex, race, income, rincome, degree, childs, marital, happy, intmbile, wwwhr)
 
 # Rename ages to age groups 
 cleaned_2016gss_data$age [cleaned_2016gss_data$age == 18] <- "Ages 18 - 20"
@@ -183,27 +183,11 @@ cleaned_2016gss_data$happy [cleaned_2016gss_data$happy == -99] <- "No answer"
 cleaned_2016gss_data$happy [cleaned_2016gss_data$happy == -98] <- "Do not know"
 cleaned_2016gss_data$happy [cleaned_2016gss_data$happy == -97] <- "Skipped"
 
-# Rename intuse to be more understandable 
-cleaned_2016gss_data$intuse [cleaned_2016gss_data$intuse == 1] <- "Yes"
-cleaned_2016gss_data$intuse [cleaned_2016gss_data$intuse == 2] <- "No"
-cleaned_2016gss_data$intuse [cleaned_2016gss_data$intuse == -100] <- "NA"
-cleaned_2016gss_data$intuse [cleaned_2016gss_data$intuse == -99] <- "No answer"
-cleaned_2016gss_data$intuse [cleaned_2016gss_data$intuse == -98] <- "Do not know"
-
 # Rename intmbile to be more understandable 
 cleaned_2016gss_data$intmbile [cleaned_2016gss_data$intmbile == 1] <- "Yes"
 cleaned_2016gss_data$intmbile [cleaned_2016gss_data$intmbile == 2] <- "No"
 cleaned_2016gss_data$intmbile [cleaned_2016gss_data$intmbile == -100] <- "NA"
 cleaned_2016gss_data$intmbile [cleaned_2016gss_data$intmbile == -99] <- "No answer"
-
-# Rename intrecnt to be more understandable 
-cleaned_2016gss_data$intrecnt [cleaned_2016gss_data$intrecnt == 1] <- "Yes"
-cleaned_2016gss_data$intrecnt [cleaned_2016gss_data$intrecnt == 2] <- "No"
[…]

### 2023-03-12 scripts/02-data_cleaning.R
Removed "intmbile" from our dataset and analysis.

@@ -20,7 +20,7 @@ raw_2016gss_data <- read_csv("inputs/data/raw_2016gss_data.csv")
 # Focus on internet variables and demographic variables
 cleaned_2016gss_data <- 
   raw_2016gss_data |> 
-  select(age, sex, race, income, rincome, degree, childs, marital, happy, intmbile, wwwhr)
+  select(age, sex, race, income, rincome, degree, childs, marital, happy, wwwhr)
 
 # Rename ages to age groups 
 cleaned_2016gss_data$age [cleaned_2016gss_data$age == 18] <- "Ages 18 - 20"
@@ -183,12 +183,6 @@ cleaned_2016gss_data$happy [cleaned_2016gss_data$happy == -99] <- "No answer"
 cleaned_2016gss_data$happy [cleaned_2016gss_data$happy == -98] <- "Do not know"
 cleaned_2016gss_data$happy [cleaned_2016gss_data$happy == -97] <- "Skipped"
 
-# Rename intmbile to be more understandable 
-cleaned_2016gss_data$intmbile [cleaned_2016gss_data$intmbile == 1] <- "Yes"
-cleaned_2016gss_data$intmbile [cleaned_2016gss_data$intmbile == 2] <- "No"
-cleaned_2016gss_data$intmbile [cleaned_2016gss_data$intmbile == -100] <- "NA"
-cleaned_2016gss_data$intmbile [cleaned_2016gss_data$intmbile == -99] <- "No answer"
-
 # Renaming column titles to more understandable labels
 cleaned_2016gss_data <-
   cleaned_2016gss_data %>%
@@ -202,7 +196,6 @@ cleaned_2016gss_data <-
     "Number of Children" = childs,
     "Marital Status" = marital, 
     "Level of Happiness" = happy, 
-    "Use of Internet from Handheld Device" = intmbile,
     "Weekly Total of Internet Use (Hours)" = wwwhr
   )
 

### 2023-03-12 scripts/03-rough_work.R
Created graphs for Marital Status vs. Internet Hours and Level of Happiness vs. Internet Hours.

@@ -239,6 +239,67 @@ mean_race |> ggplot(aes(x = variable, y = value)) +
 
 
 
+## Income VS. Marital Status ##
+mean_marital<- cleaned_2016gss_data %>%
+  select(`Marital Status`,`Weekly Total of Internet Use (Hours)`) %>%
+  group_by(`Marital Status`)%>%
+  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "Marital Status", values_from = c("Mean_total"))
+
+## mutate from wide to long 
+mean_marital <- melt(mean_marital)  #the function melt reshapes it from wide to long
+mean_marital <- mean_marital[-6,]  # delete NA row
+
+# save mean data
+write_csv(mean_marital, "outputs/data/mean_marital.csv")
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_marital |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Marital Status",
+    y = "Internet Usage Hours"
+  )
+
+
+
+
+
+
+## Income VS. Level of Happiness ##
+mean_happy<- cleaned_2016gss_data %>%
+  select(`Level of Happiness`,`Weekly Total of Internet Use (Hours)`) %>%
+  group_by(`Level of Happiness`)%>%
+  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "Level of Happiness", values_from = c("Mean_total"))
+
+## mutate from wide to long 
+mean_happy <- melt(mean_happy)  #the function melt reshapes it from wide to long
+mean_happy <- mean_happy[-4,]  # delete NA row
+
+# save mean data
+write_csv(mean_happy, "outputs/data/mean_happy.csv")
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_happy |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Level of Happiness",
[…]

### 2023-03-12 outputs/paper/paper.qmd
- Updated the comments on "03-rough_work" - Started adding to the "paper" Quarto doc

@@
 #| message: false
+# Set up workspace
 
+install.packages("kableExtra")
+install.packages("tidyverse")
+
+library(kableExtra)
 library(tidyverse)
+```
+
+```{r}
+#| include: false
+# Import cleaned data from the outputs folder, originally imported via the 01-download_data.R file
+cleaned_2016gss_data <- read.csv(here::here("outputs/data/cleaned_2016gss_data.csv"))
 ```
@@
 
-Our data is of penguins (@fig-bills).
+# 3 Results
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-maritalandinternet
+#| fig-cap: Weekly Total of Internet Use by Marital Status
 #| echo: false
+## Graph Marital Status VS. Internet Hours ##
+mean_marital <- cleaned_2016gss_data %>%
+  select(`Marital Status`,`Weekly Total of Internet Use (Hours)`) %>%
+  group_by(`Marital Status`)%>%
+  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "Marital Status", values_from = c("Mean_total"))
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+## mutate from wide to long 
+mean_marital <- melt(mean_marital)  #the function melt reshapes it from wide to long
+mean_marital <- mean_marital[-6,]  # delete NA row
+
+# save mean data
+write_csv(mean_marital, "outputs/data/mean_marital.csv")
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_marital |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Marital Status",
+    y = "Internet Usage Hours"
+  )
 ```
 
-Talk more about it.
+```{r}
+## Graph Level of Happiness VS. Internet Hours##
+mean_happy<- cleaned_2016gss_data %>%
+  select(`Level of Happiness`,`Weekly Total of Internet Use (Hours)`) %>%
+  group_by(`Level of Happiness`)%>%
+  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "Level of Happiness", values_from = c("Mean_total"))
 
-Also bills and their average (@fig-billssssss).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work.)
+## mutate from wide to long 
+mean_happy <- melt(mean_happy)  #the function melt reshapes it from wide to long
+mean_happy <- mean_happy[-4,]  # delete NA row
 
-```{r}
-#| label: fig-billssssss
-#| fig-cap: More bills of penguins
-#| echo: false
-#| fig-width: 8
-#| fig-height: 4
+# save mean data
+write_csv(mean_happy, "outputs/data/mean_happy.csv")
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
+# use tidyverse-style code to pivot and summarise the data 
+mean_happy |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Level of Happiness",
+    y = "Internet Usage Hours"
+  )
 ```
-
-Talk way more about it.
-
-# Model
-
-$$
-Pr(\theta | y) = \frac{Pr(y | \theta) Pr(\theta)}{Pr(y)}
-$$ {#eq-bayes}
-
-@eq-bayes seems useful, eh?
-
-Here's a dumb example of how to use some references: In paper we run our analysis in `R` [@citeR].
-We also use the `tidyverse` which was written by @thereferencecanbewhatever If we were interested in baseball data then @citeLahman could be useful.
-
-We can use maths by including latex between dollar signs, for instance $\theta$.
-
-# 3 Results
 
@@
 ## 4.1 First discussion point {#sec-first-point}
-
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
 
@@
 
-Weaknesses and next steps should also be included.
-
-\newpage
-
-\appendix
-
 # 5 Appendix {.unnumbered}
@@
 
-\newpage
-
 # 7 References

### 2023-03-12 scripts/03-rough_work.R

@@ -239,7 +239,7 @@ mean_race |> ggplot(aes(x = variable, y = value)) +
 
 
 
-## Income VS. Marital Status ##
+## Marital Status VS. Internet Hours ##
 mean_marital<- cleaned_2016gss_data %>%
   select(`Marital Status`,`Weekly Total of Internet Use (Hours)`) %>%
   group_by(`Marital Status`)%>%
@@ -269,7 +269,7 @@ mean_marital |> ggplot(aes(x = variable, y = value)) +
 
 
 
-## Income VS. Level of Happiness ##
+## Level of Happiness VS. Internet Hours##
 mean_happy<- cleaned_2016gss_data %>%
   select(`Level of Happiness`,`Weekly Total of Internet Use (Hours)`) %>%
   group_by(`Level of Happiness`)%>%

### 2023-03-12 outputs/paper/paper.qmd
- Added a potential summary statistics table to the end of "03-rough_work" script - Copied the same potential summary statistics table to the Data section of the "paper" Quarto doc

@@
 install.packages("tidyverse")
+install.packages("lessR")
+install.packages("tidyr")
+install.packages("reshape2")
+install.packages("knitr")
+install.packages("haven")
+install.packages("vtable")
 
@@
 library(tidyverse)
+library(lessR)
+library(tidyr)
+library(reshape2)
+library(knitr)
+library(haven)
+library(vtable)
 ```
@@
 # 2 Data {#sec-data}
+
+```{r}
+# Summary statistics of our GSS data 
+summ_gss <- cleaned_2016gss_data %>% 
+  select(`Age.Group`, `Sex`, `Race`, `Personal.Income`, `Total.Family.Income`, 
+         `Highest.Education.Obtained`, `Number.of.Children`, `Marital.Status`,
+         `Level.of.Happiness`, `Weekly.Total.of.Internet.Use..Hours.`)
+# sumtable(summ_gss,  title = "Summary Statistics of Our Variables", out = "kable")
+## the final line doesn't work for some reason and i'm mad
+```
 
@@
 ```{r}
+#| label: fig-happyandinternet
+#| fig-cap: Weekly Total of Internet Use by Level of Happiness
+#| echo: false
 ## Graph Level of Happiness VS. Internet Hours##
@@
 
+```{r}
+#| label: fig-educandinternet
+#| fig-cap: Weekly Total of Internet Use by Highest Education Obtained
+#| echo: false
+## Highest Education Obtained VS. Internet Hours ##
+mean_edu<- cleaned_2016gss_data %>%
+  select(`Highest Education Obtained`,`Weekly Total of Internet Use (Hours)`) %>%
+  group_by(`Highest Education Obtained`)%>%
+  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "Highest Education Obtained", values_from = c("Mean_total"))
+
+## mutate from wide to long 
+mean_edu <- melt(mean_edu)  #the function melt reshapes it from wide to long
+mean_edu <- mean_edu[-6,]  # delete NA row
+
+# save mean data
+write_csv(mean_edu, "outputs/data/mean_edu.csv")
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_edu |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Highest Education Obtained",
+    y = "Internet Usage Hours"
+  )
+```
+
 # 4 Discussion

### 2023-03-12 scripts/03-rough_work.R

@@ -295,12 +295,17 @@ mean_happy |> ggplot(aes(x = variable, y = value)) +
   )
 
 
-
-
-
+install.packages("vtable")
+install.packages("kableExtra")
+library(vtable)
+library(kableExtra)
 
 
 
 #### Tables ####
-
-
+# Summary statistics of our GSS data 
+summ_gss <- cleaned_2016gss_data %>% 
+  select(`Age Group`, `Sex`, `Race`, `Personal Income`, `Total Family Income`, 
+         `Highest Education Obtained`, `Number of Children`, `Marital Status`,
+         `Level of Happiness`, `Weekly Total of Internet Use (Hours)`)
+sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')

### 2023-03-13 outputs/paper/paper.qmd
- Changed all variable/column names in cleaned dataset back to original - Applied these changes to all graphs and tables that used the former variable names - Deleted saving mean of variables as a csv in paper.qmd as it was giving an error

@@
 summ_gss <- cleaned_2016gss_data %>% 
-  select(`Age.Group`, `Sex`, `Race`, `Personal.Income`, `Total.Family.Income`, 
-         `Highest.Education.Obtained`, `Number.of.Children`, `Marital.Status`,
-         `Level.of.Happiness`, `Weekly.Total.of.Internet.Use..Hours.`)
-# sumtable(summ_gss,  title = "Summary Statistics of Our Variables", out = "kable")
+  select(age, sex, race, income, rincome, 
+         degree, childs, marital,
+         happy, wwwhr)
+sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
 ## the final line doesn't work for some reason and i'm mad
@@
 ## Graph Marital Status VS. Internet Hours ##
-mean_marital <- cleaned_2016gss_data %>%
-  select(`Marital Status`,`Weekly Total of Internet Use (Hours)`) %>%
-  group_by(`Marital Status`)%>%
-  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
-  pivot_wider(names_from = "Marital Status", values_from = c("Mean_total"))
+mean_marital<- cleaned_2016gss_data %>%
+  select(marital,wwwhr) %>%
+  group_by(marital)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "marital", values_from = c("Mean_total"))
 
@@
 mean_marital <- mean_marital[-6,]  # delete NA row
-
-# save mean data
-write_csv(mean_marital, "outputs/data/mean_marital.csv")
 
@@
 ```
+@fig-maritalandinternet displays the relationship between marital status and internet usage in 2016.
 
@@
 mean_happy<- cleaned_2016gss_data %>%
-  select(`Level of Happiness`,`Weekly Total of Internet Use (Hours)`) %>%
-  group_by(`Level of Happiness`)%>%
-  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
-  pivot_wider(names_from = "Level of Happiness", values_from = c("Mean_total"))
+  select(happy,wwwhr) %>%
+  group_by(happy)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "happy", values_from = c("Mean_total"))
 
@@
 mean_happy <- mean_happy[-4,]  # delete NA row
-
-# save mean data
-write_csv(mean_happy, "outputs/data/mean_happy.csv")
 
@@
 mean_edu<- cleaned_2016gss_data %>%
-  select(`Highest Education Obtained`,`Weekly Total of Internet Use (Hours)`) %>%
-  group_by(`Highest Education Obtained`)%>%
-  summarise(Mean_total = mean(`Weekly Total of Internet Use (Hours)` , na.rm=TRUE) )%>%
-  pivot_wider(names_from = "Highest Education Obtained", values_from = c("Mean_total"))
+  select(degree, wwwhr) %>%
+  group_by(degree)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "degree", values_from = c("Mean_total"))
 
@@
 mean_edu <- mean_edu[-6,]  # delete NA row
-
-# save mean data
-write_csv(mean_edu, "outputs/data/mean_edu.csv")
 

### 2023-03-13 scripts/02-data_cleaning.R

@@ -184,20 +184,20 @@ cleaned_2016gss_data$happy [cleaned_2016gss_data$happy == -98] <- "Do not know"
 cleaned_2016gss_data$happy [cleaned_2016gss_data$happy == -97] <- "Skipped"
 
 # Renaming column titles to more understandable labels
-cleaned_2016gss_data <-
-  cleaned_2016gss_data %>%
-  rename(
-    "Age Group" = age,
-    "Sex" = sex,
-    "Race" = race,
-    "Personal Income" = income,
-    "Total Family Income" = rincome,
-    "Highest Education Obtained" = degree,
-    "Number of Children" = childs,
-    "Marital Status" = marital, 
-    "Level of Happiness" = happy, 
-    "Weekly Total of Internet Use (Hours)" = wwwhr
-  )
+#cleaned_2016gss_data <-
+#  cleaned_2016gss_data %>%
+#  rename(
+#    "Age Group" = age,
+#    "Sex" = sex,
+#    "Race" = race,
+#    "Personal Income" = income,
+#    "Total Family Income" = rincome,
+#    "Highest Education Obtained" = degree,
+#    "Number of Children" = childs,
+#    "Marital Status" = marital, 
+#    "Level of Happiness" = happy, 
+#    "Weekly Total of Internet Use (Hours)" = wwwhr
+#  )
 
 
 #### Save data ####

### 2023-03-13 scripts/03-rough_work.R

@@ -25,68 +25,68 @@ cleaned_2016gss_data <- read_csv("outputs/data/cleaned_2016gss_data.csv")
 
 # age
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = `Age Group`)) +
+  ggplot(mapping = aes(x = age)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Age", y = "Number of Respondents")
 
 # sex
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = Sex)) +
+  ggplot(mapping = aes(x = sex)) +
   geom_bar() +
   labs(x = "Sex", y = "Number of Respondents")
 
 # race
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = Race)) +
+  ggplot(mapping = aes(x = race)) +
   geom_bar() +
   labs(x = "Race", y = "Number of Respondents")
 
 # personal income
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = `Personal Income`)) +
+  ggplot(mapping = aes(x = income)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Personal Income", y = "Number of Respondents")
 
 # total family income
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = `Total Family Income`)) +
+  ggplot(mapping = aes(x = rincome)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Total Family Income", y = "Number of Respondents")
 
 # education
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = `Highest Education Obtained`)) +
+  ggplot(mapping = aes(x = degree)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Education", y = "Number of Respondents")
 
 # number of children
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = `Number of Children`)) +
+  ggplot(mapping = aes(x = childs)) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Number of Children", y = "Number of Respondents")
 
 # marital status
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = `Marital Status`)) +
[…]

### 2023-03-13 outputs/paper/paper.qmd
Added our Github repo link to the beginning of "paper.qmd" file.

@@
   - Annie Yan
-thanks: "Code and data are available at: LINK."
+thanks: "Code and data are available at: https://github.com/AnnieYan0807/GSS-data-analysis.git."
 date: "`r Sys.time()`"
@@
 ```{r}
-#| label: fig-educandinternet
+#| label: fig-degreeandinternet
 #| fig-cap: Weekly Total of Internet Use by Highest Education Obtained

### 2023-03-14 scripts/03-rough_work.R
Adjusted graph figures and their variables

@@ -23,24 +23,46 @@ cleaned_2016gss_data <- read_csv("outputs/data/cleaned_2016gss_data.csv")
 
 ### BAR GRAPHS OF EACH VARIABLE to show how many respondents for each option ###
 
+### COMPARE SEX, RACE, DEGREE WITH AGE ###
+
 # age
-cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = age)) +
-  geom_bar() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-  labs(x = "Age", y = "Number of Respondents")
+# cleaned_2016gss_data |>
+#   ggplot(mapping = aes(x = age)) +
+#   geom_bar() +
+#   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+#   labs(x = "Age", y = "Number of Respondents")
 
 # sex
+# cleaned_2016gss_data |>
+#   ggplot(mapping = aes(x = sex)) +
+#   geom_bar() +
+#   labs(x = "Sex", y = "Number of Respondents")
+
+# age and sex
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = sex)) +
-  geom_bar() +
-  labs(x = "Sex", y = "Number of Respondents")
+  ggplot(mapping = aes(x = age, fill = sex)) + 
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  geom_bar(position = "dodge2")
 
 # race
+# cleaned_2016gss_data |>
+#   ggplot(mapping = aes(x = race)) +
+#   geom_bar() +
+#   labs(x = "Race", y = "Number of Respondents")
+
+# age and race
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = race)) +
-  geom_bar() +
-  labs(x = "Race", y = "Number of Respondents")
+  ggplot(mapping = aes(x = age, fill = race)) + 
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  geom_bar(position = "dodge2")
+
+# age and education
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = age, fill = degree)) + 
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  geom_bar(position = "dodge2")
+
+### PERSONAL VS TOTAL FAMILY INCOME ###
 
 # personal income
 cleaned_2016gss_data |>
@@ -57,25 +79,34 @@ cleaned_2016gss_data |>
[…]

### 2023-03-14 scripts/03-rough_work.R
Added a new potential graph

@@ -25,6 +25,24 @@ cleaned_2016gss_data <- read_csv("outputs/data/cleaned_2016gss_data.csv")
 
 ### COMPARE SEX, RACE, DEGREE WITH AGE ###
 
+# age sex and race
+# cleaned_2016gss_data |>
+#   ggplot(mapping = aes(x = age, fill = race)) +
+#     geom_bar() +
+#     theme_minimal() +
+#     theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+#     labs(
+#       x = "Age-group of respondent",
+#       y = "Number of respondents",
+#       fill = "Voted for"
+#     ) +
+#     facet_wrap(
+#       vars(sex),
+#       dir = "v",
+#       scales = "free"
+#     ) +
+#     theme(legend.position = "bottom")
+
 # age
 # cleaned_2016gss_data |>
 #   ggplot(mapping = aes(x = age)) +

### 2023-03-14 scripts/03-rough_work.R
Adjusted the x-axis for the bar graphs showing the personal and total family income (originally out of chronological numerical order)

@@ -84,14 +84,14 @@ cleaned_2016gss_data |>
 
 # personal income
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = income)) +
+  ggplot(mapping = aes(x = factor(income, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '9', '10', '11', '$25,000+', 'NA')))) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Personal Income", y = "Number of Respondents")
 
 # total family income
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = rincome)) +
+  ggplot(mapping = aes(x = factor(rincome, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '$10,000 to $14,999', '$15,000 to $19,999', '$20,000 to $24,999', '$25,000+', 'NA')))) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Total Family Income", y = "Number of Respondents")

### 2023-03-14 outputs/paper/paper.qmd
update paper

@@
 # Set up workspace 
-
-install.packages("kableExtra")
-install.packages("tidyverse")
-install.packages("lessR")
-install.packages("tidyr")
-install.packages("reshape2")
-install.packages("knitr")
-install.packages("haven")
-install.packages("vtable")
+#install.packages("kableExtra")
+#install.packages("tidyverse")
+#install.packages("lessR")
+#install.packages("tidyr")
+#install.packages("reshape2")
+#install.packages("knitr")
+#install.packages("haven")
+#install.packages("vtable")
 
@@
 cleaned_2016gss_data <- read.csv(here::here("outputs/data/cleaned_2016gss_data.csv"))
+
+## import averaged variable datasets 
+mean_age <- read.csv(here::here("outputs/data/mean_age.csv"))
+mean_edu <- read.csv(here::here("outputs/data/mean_edu.csv"))
+mean_happy <- read.csv(here::here("outputs/data/mean_happy.csv"))
+mean_income <- read.csv(here::here("outputs/data/mean_income.csv"))
+mean_marital <- read.csv(here::here("outputs/data/mean_marital.csv"))
+mean_race <- read.csv(here::here("outputs/data/mean_race.csv"))
+mean_sex <- read.csv(here::here("outputs/data/mean_sex.csv"))
+
 ```
 
-# 1 Introduction
+# Introduction
 
@@
 
-# 2 Data {#sec-data}
+# Data {#sec-data}
 
 ```{r}
+#| echo: false
 # Summary statistics of our GSS data 
@@
          happy, wwwhr)
-sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
-## the final line doesn't work for some reason and i'm mad
+# sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
+## the final line doesn't w
+#ork for some reason and i'm mad
 ```
 
-## 2.1 Survey
+## Survey
 
-## 2.2 Questionnaire
+## Questionnaire
 
-# 3 Results
+# Results
+
+```{r}
+#| label: fig-ageandinternet
+#| fig-cap: Average Weekly Total of Internet Use by Age Group
+#| echo: false
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_age |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Age Group",
+    y = "Average Internet Usage Hours"
+  )
+
+```
+@fig-ageandinternet depicting the relationship between age and average weekly internet usage.
+The data on internet usage hours for various age groups are averaged to reduce any bias due to selectively chosen survey responses.
+The curve on the graph is skewed to the right, with its peak occurring in the 21 to 29 age group, which has the highest internet usage of approximately 18 hours per week.
+Subsequently, internet usage gradually declines with age, with the lowest usage recorded in the 89+ age group at an average of 2 hours per week.
+This graph indicates that young adults, particularly those aged 21 to 29, spend more time on the internet.
+As people age, their internet usage tends to decline gradually.
+The graph suggests a statistically significant correlation between age and internet usage, and the trend is relatively clear.
+
+```{r}
+#| label: fig-genderandinternet
+#| fig-cap: Average Weekly Total of Internet Use by Gender
+#| echo: false
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_sex |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Sex",
+    y = "Average Internet Usage Hours"
+  )
+
+```
+@fig-genderandinternet illustrates the average weekly internet usage of two genders.
+Similarly to the age and internet usage graph, the data on internet usage hours for different genders are averaged to minimize any volunteering bias.
+The data shows that there is no substantial difference between male and female internet usage.
+Female participants have an average of 12.9 hours per week spent on the internet, while male participants have an slightly higher average of 13.3 hours per week spent on the internet.
+However, the gender selection in this survey is limited, and further discussion regarding this limitation can be found in the ethics and bias section @sec-bias.
+
+```{r}
+#| label: fig-raceandinternet
+#| fig-cap: Average Weekly Total of Internet Use by Race
+#| echo: false
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_race |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Race",
+    y = "Average Internet Usage Hours"
+  )
+
+```
+
+@fig-raceandinternet displays the average weekly internet usage of individuals belonging to different races.
+Based on the data, we can observe that individuals who do not identify as either Black or White have the highest internet usage, with an average of 15.5 hours per week.
+African American individuals have a similar level of internet usage, also averaging 15.2 hours per week.
+In contrast, white individuals tend to have the lowest internet usage, with an average of 12.3 hours per week.
+
+```{r}
+#| label: fig-personalincomeandinternet
+#| fig-cap: Average Weekly Total of Internet Use by Personal Income
+#| echo: false
+
+# personal income
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = factor(income, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '9', '10', '11', '$25,000+', 'NA')))) +
+  geom_bar() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(x = "Personal Income", y = "Number of Respondents")
+
+```
+Max
+
+```{r}
+#| label: fig-familyincomeandinternet
+#| fig-cap: Average Weekly Total of Internet Use by Family Income
+#| echo: false
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_income |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Average Total Family Income",
+    y = "Internet Usage Hours"
+  )
+
+# total family income
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = factor(rincome, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '$10,000 to $14,999', '$15,000 to $19,999', '$20,000 to $24,999', '$25,000+', 'NA')))) +
+  geom_bar() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(x = "Total Family Income", y = "Number of Respondents")
+
+```
+Max
+
+```{r}
+#| label: fig-childrenandinternet
+#| fig-cap: Average Weekly Total of Internet Use by Children
+#| echo: false
+
+# number of children and marital status
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = childs, fill = marital)) + 
+  geom_bar(position = "dodge2")
+
+```
+Max
 
@@
 #| label: fig-maritalandinternet
-#| fig-cap: Weekly Total of Internet Use by Marital Status
+#| fig-cap: Average Weekly Total of Internet Use by Marital Status
 #| echo: false
-## Graph Marital Status VS. Internet Hours ##
-mean_marital<- cleaned_2016gss_data %>%
-  select(marital,wwwhr) %>%
-  group_by(marital)%>%
-  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
-  pivot_wider(names_from = "marital", values_from = c("Mean_total"))
-
-## mutate from wide to long 
-mean_marital <- melt(mean_marital)  #the function melt reshapes it from wide to long
-mean_marital <- mean_marital[-6,]  # delete NA row
-
+## Marital 
 # use tidyverse-style code to pivot and summarise the data 
@@
     x = "Marital Status",
-    y = "Internet Usage Hours"
+    y = "Average Internet Usage Hours"
   )
@@
 @fig-maritalandinternet displays the relationship between marital status and internet usage in 2016.
-
-```{r}
-#| label: fig-happyandinternet
-#| fig-cap: Weekly Total of Internet Use by Level of Happiness
-#| echo: false
-## Graph Level of Happiness VS. Internet Hours##
-mean_happy<- cleaned_2016gss_data %>%
-  select(happy,wwwhr) %>%
-  group_by(happy)%>%
-  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
-  pivot_wider(names_from = "happy", values_from = c("Mean_total"))
-
-## mutate from wide to long 
-mean_happy <- melt(mean_happy)  #the function melt reshapes it from wide to long
-mean_happy <- mean_happy[-4,]  # delete NA row
-
-# use tidyverse-style code to pivot and summarise the data 
-mean_happy |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1), 
-        axis.line = element_line(colour = "black"),
-        title = element_text(size = 12)) +
-  labs(
-    x = "Level of Happiness",
-    y = "Internet Usage Hours"
-  )
-```
+In accordance with popular opinion, people who have never been married use the Internet the most.
+Most notably, people who are widowed use the Internet the least, perhaps due to the correlation between age and widowhood.
 
@@
 #| echo: false
-## Highest Education Obtained VS. Internet Hours ##
-mean_edu<- cleaned_2016gss_data %>%
-  select(degree, wwwhr) %>%
-  group_by(degree)%>%
-  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
-  pivot_wider(names_from = "degree", values_from = c("Mean_total"))
-
-## mutate from wide to long 
-mean_edu <- melt(mean_edu)  #the function melt reshapes it from wide to long
-mean_edu <- mean_edu[-6,]  # delete NA row
 
@@
 ```
+@fig-degreeandinternet displays the relationship between highest level of education obtained by the respondent and internet usage in 2016.
+Those who have completed a less than high school degree use the internet the least.
 
-# 4 Discussion
+```{r}
+#| label: fig-happyandinternet
+#| fig-cap: Average Weekly Total of Internet Use by Level of Happiness
+#| echo: false
 
-## 4.1 First discussion point {#sec-first-point}
+# use tidyverse-style code to pivot and summarise the data 
+mean_happy |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Level of Happiness",
+    y = "Average Internet Usage Hours"
+  )
+```
 
-## 4.2 Second discussion point
+@fig-happyandinternet displays the relationship between perceived level of happiness and internet usage in 2016.
+There seems to be a direct decrease in internet usage the more happy the respondent measures themselves to be, with a difference of 2.5 hours between the happiest respondents and least happy respondents.
 
-## 4.3 Third discussion point
+# Discussion {#sec-discussion}
 
-## 4.4 Weaknesses and next steps
+## First discussion point {#sec-first-point}
 
-# 5 Appendix {.unnumbered}
+## Second discussion point {#sec-second-point}
 
-# 6 Additional details
+## Third discussion point {#sec-third-point}
 
-# 7 References
+## Weaknesses and next steps {#sec-weaknesses}
+
+## Ethics and Bias {#sec-bias}
+
+Based on the data collection methodology provided by GSS, we have identified some potential biases that could arise.
+The survey's target population consists of adults aged 18 and above who reside in households in the United States.
+Since this sampling approach focuses only on a specific age group, our analysis may be biased with respect to the age factor.
+Gss also claimed to be strictly voluntary.
+While this approach supports research ethics by respecting individuals' autonomy and right to privacy, it can also result in volunteer bias.
+GSS sample are from a mix of urban, suburban, and rural geographic areas, but only a few thousand respondents are interviewed in the main study.
+The small sample size may be lead to chance findings.
+It is likely not statistically significant enough.
+We also suspect potential sampling bias may screw our end result.
+However, with not enough information disclosed, we are unable to confirm that.
+The gender and race options provided by the GSS survey are limited.
+Participants are only given the options of selecting either "Female" or "Male" for gender, and "Blacks," "Whites," or "Others" for race.
+This narrow selection does not provide an adequate range of options for survey participants.
+
+# Appendix {.unnumbered}
+
+# Additional details
+
+# References

### 2023-03-14 scripts/02-data_cleaning.R

@@ -14,15 +14,17 @@ library(haven)
 
 
 #### Clean data ####
-# Import raw data 
+
+### main data set ###
+## Import raw data ##
 raw_2016gss_data <- read_csv("inputs/data/raw_2016gss_data.csv")
 
-# Focus on internet variables and demographic variables
+## Focus on internet variables and demographic variables ##
 cleaned_2016gss_data <- 
   raw_2016gss_data |> 
   select(age, sex, race, income, rincome, degree, childs, marital, happy, wwwhr)
 
-# Rename ages to age groups 
+##  Rename ages to age groups ##
 cleaned_2016gss_data$age [cleaned_2016gss_data$age == 18] <- "Ages 18 - 20"
 cleaned_2016gss_data$age [cleaned_2016gss_data$age == 19] <- "Ages 18 - 20"
 cleaned_2016gss_data$age [cleaned_2016gss_data$age == 20] <- "Ages 18 - 20"
@@ -200,6 +202,123 @@ cleaned_2016gss_data$happy [cleaned_2016gss_data$happy == -97] <- "Skipped"
 #  )
 
 
-#### Save data ####
+## Save data ##
 # change cleaned_data to whatever name you end up with at the end of cleaning
 write_csv(cleaned_2016gss_data, "outputs/data/cleaned_2016gss_data.csv")
+
+
+
+
+
+
+
+#### AVERAGES OF EACH VARIABLE AGAINST INTERNET USE HOURS ####
+
+## Age VS. Internet Hours ##
+mean_age<- cleaned_2016gss_data %>%
+  select(age,wwwhr) %>%
+  group_by(age)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "age", values_from = c("Mean_total"))
+
+# mutate from wide to long #
+mean_age <- melt(mean_age)  #the function melt reshapes it from wide to long
+mean_age <- mean_age[-10,]  # delete NA row
+
+# save mean data #
+write_csv(mean_age, "outputs/data/mean_age.csv")
+
+
+
+## Income VS. Internet Hours ##
+mean_income<- cleaned_2016gss_data %>%
+  select(rincome,wwwhr) %>%
+  group_by(rincome)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "rincome", values_from = c("Mean_total"))
+
+# mutate from wide to long 
[…]

### 2023-03-14 scripts/03-rough_work.R

@@ -140,212 +140,6 @@ cleaned_2016gss_data |>
   labs(x = "Weekly Total of Internet Use (Hours)", y = "Number of Respondents")
 
 
-### AVERAGES OF EACH VARIABLE AGAINST INTERNET USE HOURS ###
-
-## Age VS. Internet Hours ##
-mean_age<- cleaned_2016gss_data %>%
-  select(age,wwwhr) %>%
-  group_by(age)%>%
-  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
-  pivot_wider(names_from = "age", values_from = c("Mean_total"))
-
-## mutate from wide to long 
-mean_age <- melt(mean_age)  #the function melt reshapes it from wide to long
-mean_age <- mean_age[-10,]  # delete NA row
-
-# save mean data
-write_csv(mean_age, "outputs/data/mean_age.csv")
-
-# use tidyverse-style code to pivot and summarise the data 
-mean_age |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1), 
-        axis.line = element_line(colour = "black"),
-        title = element_text(size = 12)) +
-  labs(
-    x = "Age Group",
-    y = "Internet Usage Hours"
-  )
-
-
-
-
-
-
-## Income VS. Internet Hours ##
-mean_income<- cleaned_2016gss_data %>%
-  select(rincome,wwwhr) %>%
-  group_by(rincome)%>%
-  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
-  pivot_wider(names_from = "rincome", values_from = c("Mean_total"))
-
-## mutate from wide to long 
-mean_income <- melt(mean_income)  #the function melt reshapes it from wide to long
-mean_income <- mean_income[-8,]  # delete NA row
-
-# save mean data
-write_csv(mean_income, "outputs/data/mean_income.csv")
-
-# use tidyverse-style code to pivot and summarise the data 
-mean_income |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1), 
-        axis.line = element_line(colour = "black"),
-        title = element_text(size = 12)) +
-  labs(
-    x = "Total Family Income",
-    y = "Internet Usage Hours"
-  )
-
-
-
-
-
-
-## Education VS. Internet Hours ##
[…]

### 2023-03-14 scripts/03-rough_work.R
Adjusted rough work script

@@ -140,6 +140,212 @@ cleaned_2016gss_data |>
   labs(x = "Weekly Total of Internet Use (Hours)", y = "Number of Respondents")
 
 
+### AVERAGES OF EACH VARIABLE AGAINST INTERNET USE HOURS ###
+
+## Age VS. Internet Hours ##
+mean_age<- cleaned_2016gss_data %>%
+  select(age,wwwhr) %>%
+  group_by(age)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "age", values_from = c("Mean_total"))
+
+## mutate from wide to long 
+mean_age <- melt(mean_age)  #the function melt reshapes it from wide to long
+mean_age <- mean_age[-10,]  # delete NA row
+
+# save mean data
+write_csv(mean_age, "outputs/data/mean_age.csv")
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_age |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Age Group",
+    y = "Internet Usage Hours"
+  )
+
+
+
+
+
+
+## Income VS. Internet Hours ##
+mean_income<- cleaned_2016gss_data %>%
+  select(rincome,wwwhr) %>%
+  group_by(rincome)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "rincome", values_from = c("Mean_total"))
+
+## mutate from wide to long 
+mean_income <- melt(mean_income)  #the function melt reshapes it from wide to long
+mean_income <- mean_income[-8,]  # delete NA row
+
+# save mean data
+write_csv(mean_income, "outputs/data/mean_income.csv")
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_income |> ggplot(aes(x = variable, y = value)) + 
+  geom_point() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Total Family Income",
+    y = "Internet Usage Hours"
+  )
+
+
+
+
+
+
+## Education VS. Internet Hours ##
[…]

### 2023-03-14 outputs/paper/paper.qmd
In "paper.qmd", replaced all "geom_point()" with "geom_col()" to make our graphs bar charts instead of scatterplots.

@@
 mean_age |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
@@
 mean_sex |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
@@
 mean_race |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
@@
 mean_income |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
@@
 mean_marital |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
@@
 mean_edu |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
@@
 mean_happy |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 

### 2023-03-14 scripts/03-rough_work.R
Changed internet use graphs from point graphs to column graphs

@@ -158,7 +158,7 @@ write_csv(mean_age, "outputs/data/mean_age.csv")
 
 # use tidyverse-style code to pivot and summarise the data 
 mean_age |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
         axis.line = element_line(colour = "black"),
         title = element_text(size = 12)) +
@@ -188,7 +188,7 @@ write_csv(mean_income, "outputs/data/mean_income.csv")
 
 # use tidyverse-style code to pivot and summarise the data 
 mean_income |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
         axis.line = element_line(colour = "black"),
         title = element_text(size = 12)) +
@@ -218,7 +218,7 @@ write_csv(mean_edu, "outputs/data/mean_edu.csv")
 
 # use tidyverse-style code to pivot and summarise the data 
 mean_edu |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
         axis.line = element_line(colour = "black"),
         title = element_text(size = 12)) +
@@ -247,7 +247,7 @@ write_csv(mean_sex, "outputs/data/mean_sex.csv")
 
 # use tidyverse-style code to pivot and summarise the data 
 mean_sex |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
         axis.line = element_line(colour = "black"),
         title = element_text(size = 12)) +
@@ -276,7 +276,7 @@ write_csv(mean_race, "outputs/data/mean_race.csv")
 
 # use tidyverse-style code to pivot and summarise the data 
 mean_race |> ggplot(aes(x = variable, y = value)) + 
-  geom_point() +
+  geom_col() +
   theme(axis.text.x = element_text(angle = 45,hjust=1), 
         axis.line = element_line(colour = "black"),
         title = element_text(size = 12)) +
@@ -304,7 +304,7 @@ write_csv(mean_marital, "outputs/data/mean_marital.csv")
 
 # use tidyverse-style code to pivot and summarise the data 
[…]

### 2023-03-14 outputs/paper/paper.qmd
Edits to Quarto paper layout

@@
 ```
+
 @fig-ageandinternet depicting the relationship between age and average weekly internet usage.
@@
 ```
+
 @fig-genderandinternet illustrates the average weekly internet usage of two genders.
@@
 ```
+
 Max
@@
 ```
+
 @fig-maritalandinternet displays the relationship between marital status and internet usage in 2016.
@@
 ```
+
 @fig-degreeandinternet displays the relationship between highest level of education obtained by the respondent and internet usage in 2016.

### 2023-03-14 scripts/03-rough_work.R
Added Personal Income graph

@@ -172,7 +172,7 @@ mean_age |> ggplot(aes(x = variable, y = value)) +
 
 
 
-## Income VS. Internet Hours ##
+## Total Family Income VS. Internet Hours ##
 mean_income<- cleaned_2016gss_data %>%
   select(rincome,wwwhr) %>%
   group_by(rincome)%>%
@@ -197,6 +197,32 @@ mean_income |> ggplot(aes(x = variable, y = value)) +
     y = "Internet Usage Hours"
   )
 
+
+
+## Personal Income VS. Internet Hours ##
+mean_pincome<- cleaned_2016gss_data %>%
+  select(income,wwwhr) %>%
+  group_by(income)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "income", values_from = c("Mean_total"))
+
+## mutate from wide to long 
+mean_pincome <- melt(mean_pincome)  #the function melt reshapes it from wide to long
+mean_pincome <- mean_pincome[-8,]  # delete NA row
+
+# save mean data
+write_csv(mean_pincome, "outputs/data/mean_income.csv")
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_pincome |> ggplot(aes(x = variable, y = value)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Personal Income",
+    y = "Internet Usage Hours"
+  )
 
 
 

### 2023-03-14 scripts/02-data_cleaning.R
Added missing values to personal income cleaning.

@@ -114,7 +114,7 @@ cleaned_2016gss_data$race [cleaned_2016gss_data$race == 2] <- "Black"
 cleaned_2016gss_data$race [cleaned_2016gss_data$race == 3] <- "Other"
 cleaned_2016gss_data$race [cleaned_2016gss_data$race == -100] <- "NA"
 
-# Rename family income to be more understandable 
+# Rename personal income to be more understandable 
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == 1] <- "<$1,000"
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == 2] <- "$1,000 to $4,999"
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == 3] <- "$1,000 to $4,999"
@@ -123,6 +123,9 @@ cleaned_2016gss_data$income [cleaned_2016gss_data$income == 5] <- "$5,000 to $9,
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == 6] <- "$5,000 to $9,999"
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == 7] <- "$5,000 to $9,999"
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == 8] <- "$5,000 to $9,999"
+cleaned_2016gss_data$income [cleaned_2016gss_data$income == 9] <- "$10,000 to $14,999"
+cleaned_2016gss_data$income [cleaned_2016gss_data$income == 10] <- "$15,000 to $19,999"
+cleaned_2016gss_data$income [cleaned_2016gss_data$income == 11] <- "$20,000 to $24,999"
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == 12] <- "$25,000+"
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == -100] <- "NA"
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == -99] <- "No answer"
@@ -130,7 +133,7 @@ cleaned_2016gss_data$income [cleaned_2016gss_data$income == -98] <- "Do not know
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == -97] <- "Skipped"
 cleaned_2016gss_data$income [cleaned_2016gss_data$income == -90] <- "Refused"
 
-# Rename personal income to be more understandable 
+# Rename family income to be more understandable 
[…]

### 2023-03-14 scripts/03-rough_work.R
Adjusted Personal Income graphs

@@ -84,7 +84,7 @@ cleaned_2016gss_data |>
 
 # personal income
 cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = factor(income, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '9', '10', '11', '$25,000+', 'NA')))) +
+  ggplot(mapping = aes(x = factor(income, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '$10,000 to $14,999', '$15,000 to $19,999', '$20,000 to $24,999', '$25,000+', 'NA')))) +
   geom_bar() +
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
   labs(x = "Personal Income", y = "Number of Respondents")

### 2023-03-14 scripts/03-rough_work.R
Added graph to show the relationship between internet use and number of children respondents have

@@ -342,6 +342,34 @@ mean_marital |> ggplot(aes(x = variable, y = value)) +
 
 
 
+## Number of Children VS. Internet Hours ##
+mean_childs<- cleaned_2016gss_data %>%
+  select(childs,wwwhr) %>%
+  group_by(childs)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "childs", values_from = c("Mean_total"))
+
+## mutate from wide to long 
+mean_childs <- melt(mean_childs)  #the function melt reshapes it from wide to long
+mean_childs <- mean_childs[-10,]  # delete NA row
+
+# save mean data
+write_csv(mean_childs, "outputs/data/mean_marital.csv")
+
+# use tidyverse-style code to pivot and summarise the data 
+mean_childs |> ggplot(aes(x = variable, y = value)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Number of Children",
+    y = "Internet Usage Hours"
+  )
+
+
+
+
 
 
 ## Level of Happiness VS. Internet Hours##

### 2023-03-14 outputs/paper/paper.qmd
Added table that shows a subset of the key features of our cleaned dataset.

@@
 #| echo: false
-# Summary statistics of our GSS data 
-summ_gss <- cleaned_2016gss_data %>% 
-  select(age, sex, race, income, rincome, 
+# ATTEMPT: Summary statistics of our GSS data 
+# summ_gss <- cleaned_2016gss_data %>% 
+#   select(age, sex, race, income, rincome, 
+#          degree, childs, marital,
+#          happy, wwwhr)
+# sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
+## the final line doesn't work for some reason and i'm mad
+
+# Table showing the first 10 rows of our cleaned dataset 
+cleaned_2016gss_data |>
+  select(age, sex, race, 
          degree, childs, marital,
-         happy, wwwhr)
-# sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
-## the final line doesn't w
-#ork for some reason and i'm mad
+         happy, wwwhr) |> 
+  slice(1:8) |> 
+  kable(caption='A subset of key features',
+        col.names = c("Age", "Sex", "Race", "Highest Degree", 
+                      "Number of Children", "Marital Status", "Happiness Level", 
+                      "Weekly Internet Hours"),
+        digits = 1,
+        booktabs = FALSE,
+        linesep = "") |>
+  kable_styling(full_width = T)
 ```

### 2023-03-15 outputs/paper/paper.qmd
Added table that shows a subset of the key features of our dataset.
Adding headers to Quarto paper

@@
 
-# Introduction
+# 1 Introduction
 
@@
 
-# Data {#sec-data}
+# 2 Data {#sec-data}
+
+## 2.1 Overview of Data
+
+### 2.1.1 Data Source
+
+### 2.1.2 Variables of Interest
 
@@
 
-## Survey
+## 2.2 Survey
 
-## Questionnaire
+## 2.3 Questionnaire
 
-# Results
+# 3 Results
 
@@
 
-# Discussion {#sec-discussion}
+# 4 Discussion {#sec-discussion}
 
-## First discussion point {#sec-first-point}
+## 4.1 First discussion point {#sec-first-point}
 
-## Second discussion point {#sec-second-point}
+## 4.2 Second discussion point {#sec-second-point}
 
-## Third discussion point {#sec-third-point}
+## 4.3 Third discussion point {#sec-third-point}
 
-## Weaknesses and next steps {#sec-weaknesses}
+## 4.4 Weaknesses and next steps {#sec-weaknesses}
 
-## Ethics and Bias {#sec-bias}
+## 4.5 Ethics and Bias {#sec-bias}
 
@@
 
-# Appendix {.unnumbered}
+# 5 Appendix {.unnumbered}
 
-# Additional details
+# 6 Additional details
 
-# References
+# 7 References

### 2023-03-15 scripts/02-data_cleaning.R
Added "library(reshape2)" to "02-data_cleaning" script so that recently added melt() function can work

@@ -11,6 +11,7 @@
 #### Workspace setup ####
 library(tidyverse)
 library(haven)
+library(reshape2)
 
 
 #### Clean data ####

### 2023-03-15 outputs/paper/paper.qmd
Added summary statistics graphs and results graphs to Quarto document

@@
 mean_sex <- read.csv(here::here("outputs/data/mean_sex.csv"))
+mean_childs <- read.csv(here::here("outputs/data/mean_childs.csv"))
 
@@
 
-## 2.1 Overview of Data
+## 2.1 Survey
 
-### 2.1.1 Data Source
+Saku
 
-### 2.1.2 Variables of Interest
+### 2.1.1 Key Features
+
+Saku
+
+### 2.1.2 Methodology
+
+Saku
+
+### 2.1.3 Strengths & Weaknesses
+
+Saku
+
+## 2.2 Questionnaire
+
+Saku
+
+## 2.3 Overview of Data
+
+### 2.3.1 Data Source
+
+Max
+
+### 2.3.2 Variables of Interest
+
+Max
 
@@
 
-## 2.2 Survey
+Table :)
 
-## 2.3 Questionnaire
+```{r}
+#| label: fig-agesidebyside
+#| fig-cap: Caption
+#| fig-subcap: ["Subcaption"]
+#| layout-ncol: 2
+#| echo: false
+#| warning: false
+
+# bar graph showing relationship between age and sex
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = age, fill = sex)) + 
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  geom_bar(position = "dodge2")
+
+# bar graph showing relationship between age and sex
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = age, fill = race)) + 
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  geom_bar(position = "dodge2")
+```
+
+@fig-agesidebyside
+
+```{r}
+#| label: fig-childsandmarital
+#| fig-cap: Caption
+#| echo: false
+
+# bar graph showing relationship between number of children and marital status
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = childs, fill = marital)) + 
+  geom_bar(position = "dodge2")
+```
+
+@fig-childsandmarital
+
+```{r}
+#| label: fig-happiness
+#| fig-cap: Caption
+#| echo: false
+
+# bar graph showing the different levels of happiness and number of respondents for each response
+cleaned_2016gss_data |>
+  ggplot(mapping = aes(x = happy)) +
+  geom_bar() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
+  labs(x = "Level of Happiness", y = "Number of Respondents")
+
+```
+
+@fig-happiness
 
@@
 
-Max
+Max - might emit...
 
@@
 
-Max
+Max - might emit
 
@@
 
-# number of children and marital status
-cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = childs, fill = marital)) + 
-  geom_bar(position = "dodge2")
-
+# use tidyverse-style code to pivot and summarise the data 
+mean_childs |> ggplot(aes(x = variable, y = value)) + 
+  geom_col() +
+  theme(axis.text.x = element_text(angle = 45,hjust=1), 
+        axis.line = element_line(colour = "black"),
+        title = element_text(size = 12)) +
+  labs(
+    x = "Number of Children",
+    y = "Internet Usage Hours"
+  )
 ```
@@
 #| echo: false
-## Marital 
+
 # use tidyverse-style code to pivot and summarise the data 

### 2023-03-15 scripts/03-rough_work.R

@@ -354,7 +354,7 @@ mean_childs <- melt(mean_childs)  #the function melt reshapes it from wide to lo
 mean_childs <- mean_childs[-10,]  # delete NA row
 
 # save mean data
-write_csv(mean_childs, "outputs/data/mean_marital.csv")
+write_csv(mean_childs, "outputs/data/mean_childs.csv")
 
 # use tidyverse-style code to pivot and summarise the data 
 mean_childs |> ggplot(aes(x = variable, y = value)) + 

### 2023-03-15 outputs/paper/paper 2.tex
Edits to the Quarto paper

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[many]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={Sakura Ariga; Aliyah Maxine Ramos; Annie Yan},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
https://github.com/AnnieYan0807/GSS-data-analysis.git.}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{My subtitle if needed}
\author{Sakura Ariga \and Aliyah Maxine Ramos \and Annie Yan}
\date{15 March 2023}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{1 Introduction}\label{introduction}}

You can and should cross-reference sections and sub-sections. For
instance, Section~\ref{sec-data} and Section~\ref{sec-first-point}.

\hypertarget{sec-data}{%
\section{2 Data}\label{sec-data}}

\hypertarget{survey}{%
\subsection{2.1 Survey}\label{survey}}

Saku

\hypertarget{key-features}{%
\subsubsection{2.1.1 Key Features}\label{key-features}}

Saku

\hypertarget{methodology}{%
\subsubsection{2.1.2 Methodology}\label{methodology}}

Saku

\hypertarget{strengths-weaknesses}{%
\subsubsection{2.1.3 Strengths \&
Weaknesses}\label{strengths-weaknesses}}

Saku

\hypertarget{questionnaire}{%
\subsection{2.2 Questionnaire}\label{questionnaire}}

Saku

\hypertarget{overview-of-data}{%
\subsection{2.3 Overview of Data}\label{overview-of-data}}

\hypertarget{data-source}{%
\subsubsection{2.3.1 Data Source}\label{data-source}}

Max

\hypertarget{variables-of-interest}{%
\subsubsection{2.3.2 Variables of
Interest}\label{variables-of-interest}}

Max

\begin{table}

\caption{A subset of key features}
\centering
\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X}
\hline
Age & Sex & Race & Highest Degree & Number of Children & Marital Status & Happiness Level & Weekly Internet Hours\\
\hline
Ages 40 - 49 & Male & White & Bachelor's & 3 & Married & Pretty happy & 15\\
Ages 60 - 69 & Male & White & High school & 0 & Never married & Pretty happy & 5\\
Ages 70 - 79 & Male & White & Bachelor's & 2 & Married & Very happy & NA\\
Ages 40 - 49 & Female & White & High school & 4 & Married & Pretty happy & 7\\
Ages 50 - 59 & Female & White & Graduate & 2 & Married & Very happy & NA\\
Ages 50 - 59 & Female & White & Associate/junior college & 2 & Married & Very happy & 2\\
Ages 50 - 59 & Male & White & High school & 2 & Married & Pretty happy & 5\\
Ages 21 - 29 & Female & Other & High school & 3 & Married & Very happy & NA\\
\hline
\end{tabu}
\end{table}

Table :)

\begin{figure}

\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-agesidebyside-1.pdf}

}

}

\subcaption{\label{fig-agesidebyside-1}Subcaption}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-agesidebyside-2.pdf}

}

}

\subcaption{\label{fig-agesidebyside-2}Subcaption}
\end{minipage}%

\caption{\label{fig-agesidebyside}Caption}

\end{figure}

Figure~\ref{fig-agesidebyside}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-childsandmarital-1.pdf}

}

\caption{\label{fig-childsandmarital}Caption}

\end{figure}

Figure~\ref{fig-childsandmarital}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-happiness-1.pdf}

}

\caption{\label{fig-happiness}Caption}

\end{figure}

Figure~\ref{fig-happiness}

\hypertarget{results}{%
\section{3 Results}\label{results}}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-ageandinternet-1.pdf}

}

\caption{\label{fig-ageandinternet}Average Weekly Total of Internet Use
by Age Group}

\end{figure}

Figure~\ref{fig-ageandinternet} depicting the relationship between age
and average weekly internet usage. The data on internet usage hours for
various age groups are averaged to reduce any bias due to selectively
chosen survey responses. The curve on the graph is skewed to the right,
with its peak occurring in the 21 to 29 age group, which has the highest
internet usage of approximately 18 hours per week. Subsequently,
internet usage gradually declines with age, with the lowest usage
recorded in the 89+ age group at an average of 2 hours per week. This
graph indicates that young adults, particularly those aged 21 to 29,
spend more time on the internet. As people age, their internet usage
tends to decline gradually. The graph suggests a statistically
significant correlation between age and internet usage, and the trend is
relatively clear.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-genderandinternet-1.pdf}

}

\caption{\label{fig-genderandinternet}Average Weekly Total of Internet
Use by Gender}

\end{figure}

Figure~\ref{fig-genderandinternet} illustrates the average weekly
internet usage of two genders. Similarly to the age and internet usage
graph, the data on internet usage hours for different genders are
averaged to minimize any volunteering bias. The data shows that there is
no substantial difference between male and female internet usage. Female
participants have an average of 12.9 hours per week spent on the
internet, while male participants have an slightly higher average of
13.3 hours per week spent on the internet. However, the gender selection
in this survey is limited, and further discussion regarding this
limitation can be found in the ethics and bias section
Section~\ref{sec-bias}.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-raceandinternet-1.pdf}

}

\caption{\label{fig-raceandinternet}Average Weekly Total of Internet Use
by Race}

\end{figure}

Figure~\ref{fig-raceandinternet} displays the average weekly internet
usage of individuals belonging to different races. Based on the data, we
can observe that individuals who do not identify as either Black or
White have the highest internet usage, with an average of 15.5 hours per
week. African American individuals have a similar level of internet
usage, also averaging 15.2 hours per week. In contrast, white
individuals tend to have the lowest internet usage, with an average of
12.3 hours per week.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-personalincomeandinternet-1.pdf}

}

\caption{\label{fig-personalincomeandinternet}Average Weekly Total of
Internet Use by Personal Income}

\end{figure}

Max - might emit\ldots{}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-familyincomeandinternet-1.pdf}

}

\caption{\label{fig-familyincomeandinternet-1}Average Weekly Total of
Internet Use by Family Income}

\end{figure}

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-familyincomeandinternet-2.pdf}

}

\caption{\label{fig-familyincomeandinternet-2}Average Weekly Total of
Internet Use by Family Income}

\end{figure}

Max - might emit

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-childrenandinternet-1.pdf}

}

\caption{\label{fig-childrenandinternet}Average Weekly Total of Internet
Use by Children}

\end{figure}

Max

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-maritalandinternet-1.pdf}

}

\caption{\label{fig-maritalandinternet}Average Weekly Total of Internet
Use by Marital Status}

\end{figure}

Figure~\ref{fig-maritalandinternet} displays the relationship between
marital status and internet usage in 2016. In accordance with popular
opinion, people who have never been married use the Internet the most.
Most notably, people who are widowed use the Internet the least, perhaps
due to the correlation between age and widowhood.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-degreeandinternet-1.pdf}

}

\caption{\label{fig-degreeandinternet}Weekly Total of Internet Use by
Highest Education Obtained}

\end{figure}

Figure~\ref{fig-degreeandinternet} displays the relationship between
highest level of education obtained by the respondent and internet usage
in 2016. Those who have completed a less than high school degree use the
internet the least.

\begin{figure}

{\centering \includegraphics{paper_files/figure-pdf/fig-happyandinternet-1.pdf}

}

\caption{\label{fig-happyandinternet}Average Weekly Total of Internet
Use by Level of Happiness}

\end{figure}

Figure~\ref{fig-happyandinternet} displays the relationship between
perceived level of happiness and internet usage in 2016. There seems to
be a direct decrease in internet usage the more happy the respondent
measures themselves to be, with a difference of 2.5 hours between the
happiest respondents and least happy respondents.

\hypertarget{sec-discussion}{%
\section{4 Discussion}\label{sec-discussion}}

\hypertarget{sec-first-point}{%
\subsection{4.1 First discussion point}\label{sec-first-point}}

\hypertarget{sec-second-point}{%
\subsection{4.2 Second discussion point}\label{sec-second-point}}

\hypertarget{sec-third-point}{%
\subsection{4.3 Third discussion point}\label{sec-third-point}}

\hypertarget{sec-weaknesses}{%
\subsection{4.4 Weaknesses and next steps}\label{sec-weaknesses}}

\hypertarget{sec-bias}{%
\subsection{4.5 Ethics and Bias}\label{sec-bias}}

Based on the data collection methodology provided by GSS, we have
identified some potential biases that could arise. The survey's target
population consists of adults aged 18 and above who reside in households
in the United States. Since this sampling approach focuses only on a
specific age group, our analysis may be biased with respect to the age
factor. Gss also claimed to be strictly voluntary. While this approach
supports research ethics by respecting individuals' autonomy and right
to privacy, it can also result in volunteer bias. GSS sample are from a
mix of urban, suburban, and rural geographic areas, but only a few
thousand respondents are interviewed in the main study. The small sample
size may be lead to chance findings. It is likely not statistically
significant enough. We also suspect potential sampling bias may screw
our end result. However, with not enough information disclosed, we are
unable to confirm that. The gender and race options provided by the GSS
survey are limited. Participants are only given the options of selecting
either ``Female'' or ``Male'' for gender, and ``Blacks,'' ``Whites,'' or
``Others'' for race. This narrow selection does not provide an adequate
range of options for survey participants.

\hypertarget{appendix}{%
\section*{5 Appendix}\label{appendix}}
\addcontentsline{toc}{section}{5 Appendix}

\hypertarget{additional-details}{%
\section{6 Additional details}\label{additional-details}}

\hypertarget{references}{%
\section{7 References}\label{references}}

\end{document}

### 2023-03-15 outputs/paper/paper.tex
Edits to the Quarto paper

--- 2023-03-15 outputs/paper/paper 2.tex
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, borderline west={3pt}{0pt}{shadecolor}, sharp corners, frame hidden, boxrule=0pt, enhanced]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced]}{\end{tcolorbox}}\fi
 

### 2023-03-15 outputs/paper/paper.qmd
Quarto paper edit
edits to the quarto paper

@@
 
-Saku
+Saku :)
 
@@
 cleaned_2016gss_data |> 
-  select(age, sex, race, 
+  select(wwwhr, age, sex, race, 
          degree, childs, marital,
-         happy, wwwhr) |> 
+         happy) |> 
   slice(1:8) |> 
   kable(caption='A subset of key features',
-        col.names = c("Age", "Sex", "Race", "Highest Degree", 
-                      "Number of Children", "Marital Status", "Happiness Level", 
-                      "Weekly Internet Hours"),
+        col.names = c("Weekly Internet Hours", "Age", "Sex", "Race", "Highest Degree", 
+                      "Number of Children", "Marital Status", "Happiness Level"),
         digits = 1,

### 2023-03-15 outputs/paper/paper.qmd
Removed the variables "degree", "income", and "rincome" from our entire analysis as we chose not to focus on them in our final analysis.

--- 2023-03-15 outputs/paper/paper.qmd
@@
 mean_age <- read.csv(here::here("outputs/data/mean_age.csv"))
-mean_edu <- read.csv(here::here("outputs/data/mean_edu.csv"))
 mean_happy <- read.csv(here::here("outputs/data/mean_happy.csv"))
-mean_income <- read.csv(here::here("outputs/data/mean_income.csv"))
 mean_marital <- read.csv(here::here("outputs/data/mean_marital.csv"))
@@
 
-Saku
+Saku :) :)
 
@@
 #| echo: false
-# ATTEMPT: Summary statistics of our GSS data 
-# summ_gss <- cleaned_2016gss_data %>% 
-#   select(age, sex, race, income, rincome, 
-#          degree, childs, marital,
-#          happy, wwwhr)
-# sumtable(cleaned_2016gss_data,  title = 'Summary Statistics of Our Variables', out = 'kable')
-## the final line doesn't work for some reason and i'm mad
-
 # Table showing the first 10 rows of our cleaned dataset
 cleaned_2016gss_data |> 
-  select(age, sex, race, 
+  select(wwwhr, age, sex, race, 
          degree, childs, marital,
-         happy, wwwhr) |> 
+         happy) |> 
   slice(1:8) |> 
   kable(caption='A subset of key features',
-        col.names = c("Age", "Sex", "Race", "Highest Degree", 
-                      "Number of Children", "Marital Status", "Happiness Level", 
-                      "Weekly Internet Hours"),
+        col.names = c("Weekly Internet Hours", "Age", "Sex", "Race", "Highest Degree", 
+                      "Number of Children", "Marital Status", "Happiness Level"),
         digits = 1,
@@
 ```{r}
-#| label: fig-personalincomeandinternet
-#| fig-cap: Average Weekly Total of Internet Use by Personal Income
-#| echo: false
-
-# personal income
-cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = factor(income, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '9', '10', '11', '$25,000+', 'NA')))) +
-  geom_bar() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-  labs(x = "Personal Income", y = "Number of Respondents")
-
-```
-
-Max - might emit...
-
-```{r}
-#| label: fig-familyincomeandinternet
-#| fig-cap: Average Weekly Total of Internet Use by Family Income
-#| echo: false
-
-# use tidyverse-style code to pivot and summarise the data 
-mean_income |> ggplot(aes(x = variable, y = value)) + 
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1), 
-        axis.line = element_line(colour = "black"),
-        title = element_text(size = 12)) +
-  labs(
-    x = "Average Total Family Income",
-    y = "Internet Usage Hours"
-  )
-
-# total family income
-cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = factor(rincome, level=c('<$1,000', '$1,000 to $4,999', '$5,000 to $9,999', '$10,000 to $14,999', '$15,000 to $19,999', '$20,000 to $24,999', '$25,000+', 'NA')))) +
-  geom_bar() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-  labs(x = "Total Family Income", y = "Number of Respondents")
-
-```
-
-Max - might emit
-
-```{r}
 #| label: fig-childrenandinternet
@@
 Most notably, people who are widowed use the Internet the least, perhaps due to the correlation between age and widowhood.
-
-```{r}
-#| label: fig-degreeandinternet
-#| fig-cap: Weekly Total of Internet Use by Highest Education Obtained
-#| echo: false
-
-# use tidyverse-style code to pivot and summarise the data 
-mean_edu |> ggplot(aes(x = variable, y = value)) + 
-  geom_col() +
-  theme(axis.text.x = element_text(angle = 45,hjust=1), 
-        axis.line = element_line(colour = "black"),
-        title = element_text(size = 12)) +
-  labs(
-    x = "Highest Education Obtained",
-    y = "Internet Usage Hours"
-  )
-```
-
-@fig-degreeandinternet displays the relationship between highest level of education obtained by the respondent and internet usage in 2016.
-Those who have completed a less than high school degree use the internet the least.
 

### 2023-03-15 scripts/01-download_data.R

@@ -20,5 +20,3 @@ raw_2016gss_data <- read_dta("GSS2016.dta")
 # [...UPDATE THIS...]
 # change the_raw_data to whatever name you assigned when you downloaded it.
 write_csv(raw_2016gss_data, "inputs/data/raw_2016gss_data.csv") 
-
-         

### 2023-03-15 scripts/02-data_cleaning.R

@@ -23,7 +23,7 @@ raw_2016gss_data <- read_csv("inputs/data/raw_2016gss_data.csv")
 ## Focus on internet variables and demographic variables ##
 cleaned_2016gss_data <- 
   raw_2016gss_data |> 
-  select(age, sex, race, income, rincome, degree, childs, marital, happy, wwwhr)
+  select(age, sex, race, childs, marital, happy, wwwhr)
 
 ##  Rename ages to age groups ##
 cleaned_2016gss_data$age [cleaned_2016gss_data$age == 18] <- "Ages 18 - 20"
@@ -115,54 +115,6 @@ cleaned_2016gss_data$race [cleaned_2016gss_data$race == 2] <- "Black"
 cleaned_2016gss_data$race [cleaned_2016gss_data$race == 3] <- "Other"
 cleaned_2016gss_data$race [cleaned_2016gss_data$race == -100] <- "NA"
 
-# Rename personal income to be more understandable 
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 1] <- "<$1,000"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 2] <- "$1,000 to $4,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 3] <- "$1,000 to $4,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 4] <- "$1,000 to $4,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 5] <- "$5,000 to $9,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 6] <- "$5,000 to $9,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 7] <- "$5,000 to $9,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 8] <- "$5,000 to $9,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 9] <- "$10,000 to $14,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 10] <- "$15,000 to $19,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 11] <- "$20,000 to $24,999"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == 12] <- "$25,000+"
-cleaned_2016gss_data$income [cleaned_2016gss_data$income == -100] <- "NA"
[…]

### 2023-03-15 scripts/02-data_cleaning.R
Removing unnecessary variables

@@ -161,18 +161,6 @@ mean_age <- mean_age[-10,]  # delete NA row
 # save mean data #
 write_csv(mean_age, "outputs/data/mean_age.csv")
 
-## Education VS. Internet Hours ##
-mean_edu<- cleaned_2016gss_data %>%
-  select(degree,wwwhr) %>%
-  group_by(degree)%>%
-  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
-  pivot_wider(names_from = "degree", values_from = c("Mean_total"))
-# mutate from wide to long 
-mean_edu <- melt(mean_edu)  #the function melt reshapes it from wide to long
-mean_edu <- mean_edu[-6,]  # delete NA row
-# save mean data
-write_csv(mean_edu, "outputs/data/mean_edu.csv")
-
 ## Sex VS. Internet Hours ##
 mean_sex<- cleaned_2016gss_data %>%
   select(sex,wwwhr) %>%

### 2023-03-15 scripts/02-data_cleaning.R
Adding childs variable to cleaned data

@@ -195,6 +195,18 @@ mean_marital <- mean_marital[-6,]  # delete NA row
 # save mean data
 write_csv(mean_marital, "outputs/data/mean_marital.csv")
 
+## Number of Children VS. Internet Hours ##
+mean_childs<- cleaned_2016gss_data %>%
+  select(childs,wwwhr) %>%
+  group_by(childs)%>%
+  summarise(Mean_total = mean(wwwhr , na.rm=TRUE) )%>%
+  pivot_wider(names_from = "childs", values_from = c("Mean_total"))
+# mutate from wide to long 
+mean_childs <- melt(mean_childs)  #the function melt reshapes it from wide to long
+mean_childs <- mean_childs[-10,]  # delete NA row
+# save mean data
+write_csv(mean_childs, "outputs/data/mean_childs.csv")
+
 ## Level of Happiness VS. Internet Hours##
 mean_happy<- cleaned_2016gss_data %>%
   select(happy,wwwhr) %>%

### 2023-03-15 outputs/paper/paper.qmd
Commented all lines of code on "paper.qmd".

@@
 #| message: false
+
 # Set up workspace 
@@
 #| include: false
+
 # Import cleaned data from the outputs folder, originally imported via the 01-download_data.R file
@@
 
-## import averaged variable datasets 
+## Import averaged variable datasets from the outputs folder, originally created in the 02-data_cleaning.R file
 mean_age <- read.csv(here::here("outputs/data/mean_age.csv"))
@@
 mean_childs <- read.csv(here::here("outputs/data/mean_childs.csv"))
-
 ```
@@
 #| echo: false
+
 # Table showing the first 10 rows of our cleaned dataset
@@
 
-# bar graph showing relationship between age and sex
+# Bar graph showing relationship between age and sex
 cleaned_2016gss_data |>
@@
 
-# bar graph showing relationship between age and sex
+# Bar graph showing relationship between age and race 
 cleaned_2016gss_data |>
@@
 
-# bar graph showing relationship between number of children and marital status
+# Bar graph showing relationship between number of children and marital status
 cleaned_2016gss_data |>
@@
 
-# bar graph showing the different levels of happiness and number of respondents for each response
+# Bar graph showing the different levels of happiness and number of respondents for each response
 cleaned_2016gss_data |>
@@
   labs(x = "Level of Happiness", y = "Number of Respondents")
-
 ```
@@
 
-# use tidyverse-style code to pivot and summarise the data 
+# Bar graph showing relationship between age and internet use, using tidyverse-style code to pivot and summarise the data 
 mean_age |> ggplot(aes(x = variable, y = value)) + 
@@
   )
-
 ```
@@
 
-# use tidyverse-style code to pivot and summarise the data 
+# Bar graph showing relationship between sex and internet use, using tidyverse-style code to pivot and summarise the data 
 mean_sex |> ggplot(aes(x = variable, y = value)) + 
@@
 
-# use tidyverse-style code to pivot and summarise the data 
+# Bar graph showing relationship between race and internet use, using tidyverse-style code to pivot and summarise the data 
 mean_race |> ggplot(aes(x = variable, y = value)) + 
@@
 
-# use tidyverse-style code to pivot and summarise the data 
+# Bar graph showing relationship between number of children and internet use, using tidyverse-style code to pivot and summarise the data 
 mean_childs |> ggplot(aes(x = variable, y = value)) + 
@@
 
-# use tidyverse-style code to pivot and summarise the data 
+# Bar graph showing relationship between marital status and internet use, using tidyverse-style code to pivot and summarise the data 
 mean_marital |> ggplot(aes(x = variable, y = value)) + 
@@
 
-# use tidyverse-style code to pivot and summarise the data 
+# Bar graph showing relationship between level of happiness and internet use, using tidyverse-style code to pivot and summarise the data 
 mean_happy |> ggplot(aes(x = variable, y = value)) + 

### 2023-03-15 outputs/paper/paper.qmd
update paper

@@
 
-# Import cleaned data from the outputs folder, originally imported via the 01-download_data.R file
+# Import cleaned data from the outputs folder, originally imported via the 02-data_cleaning.R file
 cleaned_2016gss_data <- read.csv(here::here("outputs/data/cleaned_2016gss_data.csv"))
@@
 
-# 1 Introduction
+# Introduction
 
@@
 
-# 2 Data {#sec-data}
+# Data {#sec-data}
 
-## 2.1 Survey
+## Survey
 
-Saku :) :)
+### Key Features
 
-### 2.1.1 Key Features
+The General Social Survey (GSS) is a national survey conducted in the United States of America that aims to better understand trends in the American adult population’s social characteristics and attitudes to better inform research and public policy.
+(@cite3) Beginning in 1972, this interview-based survey is conducted biennially on five key themes: gender and marriage, current affairs, civil liberties, politics, and religion and spirituality.(@cite4) The 2016 GSS is unique in that it also includes questions about internet-usage behaviours, which is why our analysis focuses on the GSS of this year.
+In 2016, there is data for 2,867 respondents for 961 variables.
 
-Saku
+### Methodology
 
-### 2.1.2 Methodology
+The GSS’ target population is adults aged 18 years and older living in the United States.
+The sampling frame for the 2016 GSS is people living in the US aged 18+ who can speak English or Spanish and live in households.
+(@cite5) Thus, those living outside households (e.g.
+university dorms, nursing homes, institutions, military quarters) are not included in the GSS.(@cite6) The frame was created using the NORC National Sampling Frame, which first uses Census data to stratify US geographic regions by size and then chooses metropolitan areas and non-metropolitan counties within these regions, as the first stage of selection.(@cite6) In the second stage of selection, these metropolitan areas and non-metropolitan counties were stratified by race and income and further divided into blocks.(@cite6) Then, the sample is gathered by interviewers beginning from the northwest corner of a given block and moving from household to household until the equal-sex quota has been filled.(@cite6)
 
-Saku
+Thus, the sample for the 2016 GSS was an area-probability sample gathered by the clustered sampling approach, as households are selected and then one random member from the household is selected to be included in the survey.(@cite6) A key tradeoff of this approach is that while cluster sampling is that while this method is much easier than completely random sampling, it can lead to bias in that there is more bias if the clusters are similar to each other.
 
-### 2.1.3 Strengths & Weaknesses
+Non-response is handled by inputting it in the GSS dataset as one of the following options depending on the method of non-response: “NA”, “no answer”, “do not know”, or “skipped”.
 
-Saku
+### Strengths & Weaknesses
 
-## 2.2 Questionnaire
+A strength of this 2016 GSS survey was that it was delivered both in English and in Spanish, allowing for a greater reach than had the survey just been conducted in English, like in the years previous to 2006.(@cite6) Of the people who had been excluded from this survey due to the English-only delivery, Spanish-speakers made up the majority, so this dual language delivery addressed this key exclusion.
+(@cite6)
 
-Saku
+Another weakness of this sample is the lack of a gender variable, as the sample only provides a variable on sex.
+A gender variable would be more useful for data analysis, as it better reflects the respondent’s lived experience.
+The lack of a gender variable that better accommodates for people’s lived experience might lead to those who feel uncomfortable with the binary categories of sex to refrain from participating in the survey, leading to selection bias.
 
-## 2.3 Overview of Data
+Another weakness of the 2016 GSS survey is that the interviewer physically fills out the response for the respondent.
+This can potentially lead to measurement error.
+When the interviewer fills out the survey on behalf of the respondent, there may be a difference in the observed responses of the interviewer and the actual responses of the interviewee.
+This creates difficulty in verifying responses.
+(@cite13)
 
-### 2.3.1 Data Source
+## Questionnaire
+
+A strength of the questionnaire was the clear wording of the question regarding Internet usage per week in hours.
+The survey question was formatted as follows: “Not counting e-mail, about how many minutes or hours per week do you use the Web?
+(Include time you spend visiting regular web sites and time spent using interactive Internet services like chat rooms, Usenet groups, discussion forums, bulletin boards, and the like.)”.
+The giving of examples was likely helpful in jogging the respondents’ memory of what exactly Internet usage can look like, as if one is flat out asked whether they use the Internet, it can be hard to conceptualize what that looks like.
+
+A key weakness of this questionnaire is the race variable, as it only allows for three options: “Black”, “White”, or “Other”, which does not take into account the largest ethnic minority group, Hispanics and Latino Americans, as well as other ethnic groups, such as Asians and Native Americans in the United States.
+In comparison, while not without fault itself, the US Census identifies 5 minimum categories of race (White, Black or African American, American Indian or Alaska Native, Asian, Native Hawaiian or Other Pacific Islander) and also allows for the reporting of more than one race.
+(@cite14)
+
+This questionnaire has a limitation in terms of selection bias because of our limited ability to reach the entire population.
+The respondents who receive the questionnaire are likely to share a similar background with us, which does not achieve a random selection of the population, which is all U.S.
+citizens.
+Our study may also be susceptible to volunteering bias because the data is reliant on participants willingly providing their answers, which could lead to biased results.
+
+Relatedly, another weakness of this questionnaire is that questions are allowed non-responses.
+This results in truncated data, in which the dataset has been incompletely collected.
+Having no response for a question can only be observed as null, despite there being a possible actual value.
+(@cite15) There are a variety of reasons as to why a respondent did not want to answer a question, but can only be observed as a non-response to avoid biased assumptions and inaccurate results.
+
+## Overview of Data
+
+### Data Source
 
@@
 
-### 2.3.2 Variables of Interest
+### Variables of Interest
 
@@
 
-# 3 Results
+# Results
 
@@
 
-Max
+@fig-childrenandinternet shows the relationship between respondents with a specific number of children and their weekly total hours of Internet use.
+Respondents that do not have any children are the group that uses the internet the most during the week.
+The data demonstrates that there is an inverse relationship between the two variables.
+This means that there is a gradual decrease of internet use hours as the number of children increases.
+However, the second largest group that uses the internet are those that reported having 8 children or more, making it an outlier.
 
@@
 
-# 4 Discussion {#sec-discussion}
+# Discussion {#sec-discussion}
 
-## 4.1 First discussion point {#sec-first-point}
+## Aging reduces the amount of hours spent using the Internet {#sec-first-point}
 
-## 4.2 Second discussion point {#sec-second-point}
+## Second discussion point {#sec-second-point}
 
-## 4.3 Third discussion point {#sec-third-point}
+### Marital Status
+As seen in @fig-maritalandinternet, people who have never married use the Internet significantly more than those who are married or who are widowed.
+This trend could partially be explained by the correlation between age and being married, as those who have never been married are more likely to be younger.
+In the United States in 2016, at the time this survey data was collected, the median age of marriage was 28 years old for women and 30 years old for men.
+(@cite19) This statistic is consistent with the findings of @fig-ageandinternet, which shows that Internet usage is highest for people aged 21 to 29, people who are just prior to the median age of marriage.
+This explanation is supported by the finding that widowed people use the Internet the least, out of all of the marital categories.
+Because widowhood is more likely in people who are older, the correlation between age and Internet use is further reflected here.
+(@cite20) Thus, the relationship between marriage vs.
+non-marriage and Internet use, in which those who have never been married use the Internet more than those who are married, is related to the inverse relationship between age and amount of average Internet use stated in Section 4.1 above.
 
-## 4.4 Weaknesses and next steps {#sec-weaknesses}
+This trend of younger and non-married people using the Internet more than older, married people could be further explained by the use of online and digital dating apps by younger, non-married people as ways to connect with people romantically.
+The United States is one of the countries that uses online dating sites and apps the most, suggesting that online dating is normalized in American culture and partially explaining why younger, non-married people use the Internet much more than their older, married counterparts.(@cite21) The widespread usage of handheld mobile devices that has become the norm for all age groups, but especially younger people who are more likely to use social media and online dating apps, furthers this.
 
-## 4.5 Ethics and Bias {#sec-bias}
+A third contributing factor to this trend could be that non-married individuals feel more isolated due to not meeting societal norms of marriage and turn to the Internet to seek connections and community.
+People who live in societies in which marriage is socially expected, such as the United States, can feel isolated, for which using the Internet can help them feel a sense of belonging that they find missing in their lives.(@cite22)
+
+### Number of Children
+
+@fig-childrenandinternet demonstrates the relationship between number of children of respondents and average weekly Internet use.
+This graph shows that people with no children use the Internet more than people who have children.
+Like Section 4.2.1 above, this could be due to the correlation between age and having children: those who are older are more likely to have children than those who are younger.
+The median age at which women have children is 30 years of age, which is consistent with the findings of @fig-ageandinternet, which states that people in their 20s use the Internet the most.(@cite23) This generally inverse relationship between number of children and Internet use, is related to the inverse relationship between age and amount of average Internet use stated in Section 4.1 above.
+The outlier of the “8+” children category has a high Internet usage because there were only 6 people who responded about their Internet usage in that category (compared to the approximately 500 people who responded about their Internet usage in the “0” children category), such that the result was skewed by one participant who reported 60 hours of Internet use.
+
+This trend could also be explained by the amount of personal time that people have for themselves.
+Personal use is one of the main activities of Internet use (including instant messaging and social media), and people with children are less likely to have time for themselves as they spend time caring for their children.(@cite24) This likely increases with more children.
+Thus, the relatively inverted relationship between number of children and Internet use could be partially explained by the inverted relationship between number of children and personal time.
+
+However, the Internet has increasingly come to be a key resource for parenting, both for getting information and for receiving support.(@cite25) This explains why average Internet use is relatively similar across people with 1 child to 5 children.
+
+## Third discussion point {#sec-third-point}
+
+## Weaknesses and next steps {#sec-weaknesses}
+
+## Ethics and Bias {#sec-bias}
 
@@
 
-# 5 Appendix {.unnumbered}
+# Appendix {.unnumbered}
 
-# 6 Additional details
+# Additional details
 
-# 7 References
+# References

### 2023-03-15 outputs/paper/paper.qmd
update reference

@@
 ## Third discussion point {#sec-third-point}
+In a previous study, we found a potential correlation between happiness and internet usage.
+Specifically, individuals who reported lower internet usage tended to have higher levels of happiness.
+There are few reasons may be contribute to this finding.
+
+We suspect this finding may be attributed to various factors related to social media usage, given that people spend an average of 2 hours and 31 minutes daily on social media.(@citea1) Our secondary research indicates that certain aspects of the internet, such as social media, can negatively impact psychological health.
+Excessive use of social media can result in addiction, anxiety, depression, or isolation.
+Furthermore, social media can become a substitute for real-life social interaction, causing individuals to feel lonely and disconnected.
+Comparing oneself unfavorably with internet social figures can also lead to low self-esteem and negative body image, while cyberbullying can have potential mental health implications for individuals who spend long hours on the internet.
+A study by the University of Pennsylvania in 2018 found that reducing social media use to 30 minutes a day resulted in a significant reduction in anxiety, depression, loneliness, and sleep problems.(@citea2)
+
+Additionally, research suggests that spending more time online can make children less happy with their lives.
+For instance, a study by the University of Sheffield concluded that spending an extra hour a day on social networks reduces the probability of being completely happy with life overall by approximately 14 percentage points.
+Thus, we have reason to believe that internet usage, particularly social media usage, can have a negative impact on happiness levels to some extent and affect the relationship between happiness and internet usage.
+
+Another factor that could contribute to the correlation between happiness and internet usage is a fulfilling real life.
+Engaging in offline activities, such as spending time with loved ones, pursuing hobbies, or achieving personal goals, can be more rewarding than spending time online.
+This can lead individuals to prioritize fulfilling activities over aimless scrolling through the internet and decrease their need for validation or connection through social media and other online platforms.
+Thus, individuals who are fulfilled in their offline lives may have lower internet usage hours and higher happiness levels.
 

### 2023-03-15 outputs/paper/paper.qmd
Added introduction, data overview, variables of interest, discussion point 1 section to the quarto paper.

--- 2023-03-15 outputs/paper/paper.qmd
@@
 
-You can and should cross-reference sections and sub-sections. For instance, @sec-data and @sec-first-point.
+The Internet has become a widely used computer network that allows for connection, to communicate, and access to information.
+By the mid 1990s, the Internet began reaching millions of users from around the world, where using a web of information, known as the World Wide Web, was a popular way of browsing information and facilitating communication online \[**cite**\].
+Throughout the years, the different ways in which the Internet is used have expanded, where users could also make purchases through electronic commerce platforms and share different forms of media on social media platforms.
+
+This report aims to investigate the characteristics of those that use the Internet the most in comparison to those that use it the least.
+We wanted to understand the reasons as to why these factors are correlated with a higher internet use pattern and a lower internet use pattern.
+Our estimand is the mean number of weekly hours of internet usage of American adults.
+Using the survey data from the United States General Social Survey (GSS) recorded in 2016, we constructed different models on 6 factors and their relationship with total weekly hours of internet use: age, race, sex, marital status, number of children, and happiness.
+
+Through examining the different relationships between the various variables and the weekly total number of hours of internet use, we found that those of young adults tend to use the internet more than older adults.
+This may be due to physical, psychological, and social barriers when using the internet.
+We also found that those who have never been married use the internet more than others with different marital statuses.
+This could be correlated with age and the difference in reasons for using the internet.
+Additionally, as social media is a large part of internet usage, we found that the use of social media platforms has a negative impact on emotional health, demonstrating a possible correlation between low internet usage and a high level of happiness.
+
+Using the internet more regularly can improve the lives of individuals for its convenience and its accessibility.
+It is beneficial because it allows for easier and instantaneous communication, for learning, for increasing access to services, for encouraging connections and decreasing isolation, and for gathering information.
+
+The remainder of this report is structured as follows: Section 2 discusses the dataset of interest, including the methodology of the survey and its strengths and weaknesses, Section 3 presents the results through data visualizations, Section 4 discusses our findings, its weaknesses, and next steps, and Section 5 consists of the supplementary survey as an extension of the survey data to improve and enhance the study.
 
@@
 
-The General Social Survey (GSS) is a national survey conducted in the United States of America that aims to better understand trends in the American adult population’s social characteristics and attitudes to better inform research and public policy.
+The General Social Survey (GSS) is a national survey conducted in the United States of America that aims to better understand trends in the American adult population's social characteristics and attitudes to better inform research and public policy.
 (@cite3) Beginning in 1972, this interview-based survey is conducted biennially on five key themes: gender and marriage, current affairs, civil liberties, politics, and religion and spirituality.(@cite4) The 2016 GSS is unique in that it also includes questions about internet-usage behaviours, which is why our analysis focuses on the GSS of this year.
@@
 
-The GSS’ target population is adults aged 18 years and older living in the United States.
+The GSS' target population is adults aged 18 years and older living in the United States.
 The sampling frame for the 2016 GSS is people living in the US aged 18+ who can speak English or Spanish and live in households.
@@
 
-Non-response is handled by inputting it in the GSS dataset as one of the following options depending on the method of non-response: “NA”, “no answer”, “do not know”, or “skipped”.
+Non-response is handled by inputting it in the GSS dataset as one of the following options depending on the method of non-response: "NA", "no answer", "do not know", or "skipped".
 
@@
 Another weakness of this sample is the lack of a gender variable, as the sample only provides a variable on sex.
-A gender variable would be more useful for data analysis, as it better reflects the respondent’s lived experience.
-The lack of a gender variable that better accommodates for people’s lived experience might lead to those who feel uncomfortable with the binary categories of sex to refrain from participating in the survey, leading to selection bias.
+A gender variable would be more useful for data analysis, as it better reflects the respondent's lived experience.
+The lack of a gender variable that better accommodates for people's lived experience might lead to those who feel uncomfortable with the binary categories of sex to refrain from participating in the survey, leading to selection bias.
 
@@
 A strength of the questionnaire was the clear wording of the question regarding Internet usage per week in hours.
-The survey question was formatted as follows: “Not counting e-mail, about how many minutes or hours per week do you use the Web?
-(Include time you spend visiting regular web sites and time spent using interactive Internet services like chat rooms, Usenet groups, discussion forums, bulletin boards, and the like.)”.
-The giving of examples was likely helpful in jogging the respondents’ memory of what exactly Internet usage can look like, as if one is flat out asked whether they use the Internet, it can be hard to conceptualize what that looks like.
+The survey question was formatted as follows: "Not counting e-mail, about how many minutes or hours per week do you use the Web?
+(Include time you spend visiting regular web sites and time spent using interactive Internet services like chat rooms, Usenet groups, discussion forums, bulletin boards, and the like.)".
+The giving of examples was likely helpful in jogging the respondents' memory of what exactly Internet usage can look like, as if one is flat out asked whether they use the Internet, it can be hard to conceptualize what that looks like.
 
-A key weakness of this questionnaire is the race variable, as it only allows for three options: “Black”, “White”, or “Other”, which does not take into account the largest ethnic minority group, Hispanics and Latino Americans, as well as other ethnic groups, such as Asians and Native Americans in the United States.
+A key weakness of this questionnaire is the race variable, as it only allows for three options: "Black", "White", or "Other", which does not take into account the largest ethnic minority group, Hispanics and Latino Americans, as well as other ethnic groups, such as Asians and Native Americans in the United States.
 In comparison, while not without fault itself, the US Census identifies 5 minimum categories of race (White, Black or African American, American Indian or Alaska Native, Asian, Native Hawaiian or Other Pacific Islander) and also allows for the reporting of more than one race.
@@
 
-Max
+In this report, the 2867 observations from the 2016 United States General Social Survey are used.
+The survey data was obtained from the University of Chicago National Opinion Research Centre (NORC) \[**cite**\].
+
+This report was created using the R statistical programming language \[**cite**\].
+The here package was utilized to retrieve files from another folder within the same R project.
+\[**cite**\].
+For the results and analysis of this report, all figures were created using the tidyverse package \[**cite**\].
+Additionally, the tables were created using the packages vtable \[**cite**\] and kableExtra \[**cite**\], and the graphs were created using the packages lessR \[**cite**\], dplyr \[**cite**\], tidyr \[**cite**\], reshape2 \[**cite**\], and ggplot2 \[**cite**\].
 
@@
 
-Max
+There are **7** variables that were selected to conduct the analysis of this report.
+We aimed to focus on **6** particular factors that supposedly affect the amount of Internet use: age, sex, race, number of children, marital status, and happiness.
+In this paper, we wanted to investigate the influence of these various factors on the total number of hours of weekly Internet usage.
+The packages tidyverse \[**cite**\], haven \[**cite**\], and reshape2 \[**cite**\] were used to clean the dataset by grouping or converting the questionnaire responses into categorical or textual answers.
 
@@
 
-Table :)
+Table 1 shows the first 10 rows of the cleaned dataset.
+The variables, Number of Children and Weekly Internet Hours, are recorded as a numerical value.
+Weekly Internet Hours has a maximum value of 168, as there are only 168 hours in a week.
+Age is also recorded as a numerical value, but is cleaned to represent ages in groups.
+The other variables, Sex, Race, Highest Degree, Number of Children, Marital Status and Happiness Level, are all recorded as a textual option for respondents to choose from.
 
@@
 
+Most of the respondents of the 2016 GSS are adults ranging from ages 21 to 69 years old.
+The size of each age group between that range oscillates within the right skewed distribution.
+The largest age group respondent size is 50 to 59 years old.
+By graphing the variables, age and sex in \[FIG #\], we observe that there are more female adults in each age group participating in this survey than there are male adults.
+The overall distribution is skewed to the right.
+The visualization of age and race in \[FIG #\] demonstrates that the respondents that identify with the White racial group comprises most of the respondent sample.
+This racial group is also shown to have a near-symmetrical distribution.
+Conversely, the other racial groups in this survey, Black and Other, are significantly the minority of the survey sample.
+The Black and Other racial groups are skewed to the right, illustrating that there are less individuals that identify with these racial groups in the older age groups.
+According to the 2020 census surveys, the most common racial group in America is White or Caucasian, which means that the 2016 GSS data on this group provides an accurate representation of American society.
+
 ```{r}
@@
 @fig-childsandmarital
+
+According to \[FIG #\], respondents who are married have a right skew distribution of the number of children they have, where the mode of the data is having two children.
+As for individuals that responded as never having been married, the distribution was exponential, in which the mode of this distribution is having zero children.
+As the number of children increases, the number of individuals who have never been married decreases.
+The distribution of the other minority marital groups are skewed to the right.
+Overall, most survey respondents have zero children.
 
@@
 @fig-happiness
+
+Considering general happiness, \[FIG #\] exhibits a left skew distribution.
+This illustrates that a significant proportion of the respondents indicate that they are fairly happy and an adequate proportion indicate that they are very happy.
+With a limited number of options to measure happiness quantitatively, it is difficult to discern a distribution on varying levels of happiness.
 
@@
 
-## Aging reduces the amount of hours spent using the Internet {#sec-first-point}
+## Aging Reduces the Amount of Hours Spent Using the Internet {#sec-first-point}
+
+Based on the results, we find that as aging increases, the amount of weekly total hour Internet use decreases.
+As shown in \@fig-ageandinternet, the majority of respondents that have the highest number of weekly hours of Internet use are those between the ages of 18 and 39 years old.
+The three age groups within this range have the three largest Internet usage.
+By observing the tail of the right-skewed distribution in \@fig-ageandinternet, it illustrates that as the age of respondents increases from the age range 20-29 years old, the use of the Internet is reduced.
+In this age of developing technology and digital services, the Internet has become a widely used source for information, commerce, communication, and entertainment.
+According to our results, many young adults are commonly online.
+This may be because they have the functional capabilities of learning how to use the Internet and actually using the Internet.
+Its ease and convenience allows users to have access to instant information and communication, popularly used by young adults.
+In comparison, those of older age tend to use the Internet less.
+The reason for this may be because, as individuals age, they experience declining changes in their physical, mental, and social abilities, affecting their functional capacities.
+Research has shown that 23% of older adults indicate that having a physical or health condition makes reading difficult or challenging \[**cite**\].
+This shows that those in older age groups have barriers when it comes to using the Internet.
+Although using the Internet is valuable to those of older age, as it helps them connect with family remotely and experience socialization, the factors that make using the Internet challenging keeps them from increasing their weekly use.
+Many older adults have expressed that, when using technology and digital services, they would need assistance \[**cite**\].
+Despite seniors being less likely than the rest of the population to go online, once they understand how to use it, it becomes a part of their everyday lives.
+Research has shown that 71% of seniors go online almost everyday and 11% go online three or five times weekly \[**cite**\].
+While many older adults understand the beneficial aspect of the Internet, there still remain non-users of the Internet due to disabilities that come with aging \[**cite**\].
 
@@
 ### Marital Status
+
 As seen in @fig-maritalandinternet, people who have never married use the Internet significantly more than those who are married or who are widowed.
@@
 The median age at which women have children is 30 years of age, which is consistent with the findings of @fig-ageandinternet, which states that people in their 20s use the Internet the most.(@cite23) This generally inverse relationship between number of children and Internet use, is related to the inverse relationship between age and amount of average Internet use stated in Section 4.1 above.
-The outlier of the “8+” children category has a high Internet usage because there were only 6 people who responded about their Internet usage in that category (compared to the approximately 500 people who responded about their Internet usage in the “0” children category), such that the result was skewed by one participant who reported 60 hours of Internet use.
+The outlier of the "8+" children category has a high Internet usage because there were only 6 people who responded about their Internet usage in that category (compared to the approximately 500 people who responded about their Internet usage in the "0" children category), such that the result was skewed by one participant who reported 60 hours of Internet use.
 

### 2023-03-15 outputs/paper/paper.qmd
upload reference

@@
 Additionally, research suggests that spending more time online can make children less happy with their lives.
-For instance, a study by the University of Sheffield concluded that spending an extra hour a day on social networks reduces the probability of being completely happy with life overall by approximately 14 percentage points.
-Thus, we have reason to believe that internet usage, particularly social media usage, can have a negative impact on happiness levels to some extent and affect the relationship between happiness and internet usage.
+For instance, a study by the University of Sheffield concluded that spending an extra hour a day on social networks reduces the probability of being completely happy with life overall by approximately 14 percentage points.(@citea3) Thus, we have reason to believe that internet usage, particularly social media usage, can have a negative impact on happiness levels to some extent and affect the relationship between happiness and internet usage.
 
@@
 ## Weaknesses and next steps {#sec-weaknesses}
+
+### Weakness
+A key weakness in our analysis was that we removed non-responses from our data, which may have made our data for Internet use not as accurate in reflecting what the actual population’s Internet use looks like.
+A central reason as to why participant’s may have chosen not to respond to the question about Internet use could be embarrassment: admitting that one spends too much time on the Internet could be embarrassing, so those who have higher Internet usage are more likely not to respond to this question.
+This is a very real concern as Internet addiction is increasing in our increasingly digital world, and several countries have even identified it as a public health concern.
+(@cite26)
+
+Another weakness in our analysis is the self-reported nature of the results, meaning there was some bias in questions with ambiguous word choice, such as our happiness variable.
+The definition of the different response options to the happiness variable survey question of “not so happy”, “fairly happy”, and “very happy” will vary depending on the individual, as well as the day or time of day.
+Thus, our analysis of the relationship between happiness and Internet use may be biased.
+
+### Next Steps
+To address our second identified weakness in Section 4.4.2 above, implementing a supplementary survey with more detailed questions, particularly about race and gender (as mentioned in Section 2.2) and more straightforward question answers (e.g.
+a number scale for happiness variable) would allow for more in-depth analysis.
+
+In addition, conducting further research on the different uses of the Internet based on population groups would be a reasonable next step, now that we have determined which population groups use the Internet the most and least.
+
+Finally, looking at how COVID-19 impacted Internet usage would be a particularly interesting avenue of research to pursue, especially with the increase in online activities (e.g.
+work from home, online classes, widespread use of Zoom, etc.).
+It would be interesting to compare our analysis of American population groups that used the Internet the most in 2016, with 2020 (during the COVID-19 pandemic) and with 2022 (post-COVID-19 pandemic).
 

### 2023-03-15 outputs/paper/paper.qmd
Removed "degree" variable

@@
 cleaned_2016gss_data |> 
-  select(wwwhr, age, sex, race, 
-         degree, childs, marital,
-         happy) |> 
-  slice(1:8) |> 
+  select(wwwhr, age, sex, race, childs, marital, happy) |> 
+  slice(1:7) |> 
   kable(caption='A subset of key features',
-        col.names = c("Weekly Internet Hours", "Age", "Sex", "Race", "Highest Degree", 
+        col.names = c("Weekly Internet Hours", "Age", "Sex", "Race",;
                       "Number of Children", "Marital Status", "Happiness Level"),
@@
 
-# Appendix {.unnumbered}
-
-# Additional details
+# Appendix
 

### 2023-03-15 scripts/draft.R
- Added a detailed README file - Removed example files that we don't need for our final analysis - Removed variables that we are no longer investigating - Renamed our data testing script

@@ -1,86 +1,0 @@
-# Rename wwwhr to groups of 25
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 0] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 1] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 2] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 3] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 4] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 5] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 6] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 7] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 8] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 9] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 10] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 11] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 12] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 13] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 14] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 15] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 16] <- "0 - 24 hours"
-cleaned_2016gss_data$wwwhr [cleaned_2016gss_data$wwwhr == 17] <- "0 - 24 hours"
[…]

### 2023-03-15 outputs/paper/paper.qmd
Adding references to quarto document

@@
 Additionally, as social media is a large part of internet usage, we found that the use of social media platforms has a negative impact on emotional health, demonstrating a possible correlation between low internet usage and a high level of happiness.
-
 Using the internet more regularly can improve the lives of individuals for its convenience and its accessibility.
-It is beneficial because it allows for easier and instantaneous communication, for learning, for increasing access to services, for encouraging connections and decreasing isolation, and for gathering information.
+It is beneficial because it allows for easier and instantaneous communication, for learning, for increasing access to services, for encouraging connections and decreasing isolation, and for gathering information \[**cite**\].
 
@@
 ## Third discussion point {#sec-third-point}
+
 In a previous study, we found a potential correlation between happiness and internet usage.
@@
 ### Weakness
-A key weakness in our analysis was that we removed non-responses from our data, which may have made our data for Internet use not as accurate in reflecting what the actual population’s Internet use looks like.
-A central reason as to why participant’s may have chosen not to respond to the question about Internet use could be embarrassment: admitting that one spends too much time on the Internet could be embarrassing, so those who have higher Internet usage are more likely not to respond to this question.
+
+A key weakness in our analysis was that we removed non-responses from our data, which may have made our data for Internet use not as accurate in reflecting what the actual population's Internet use looks like.
+A central reason as to why participant's may have chosen not to respond to the question about Internet use could be embarrassment: admitting that one spends too much time on the Internet could be embarrassing, so those who have higher Internet usage are more likely not to respond to this question.
 This is a very real concern as Internet addiction is increasing in our increasingly digital world, and several countries have even identified it as a public health concern.
@@
 Another weakness in our analysis is the self-reported nature of the results, meaning there was some bias in questions with ambiguous word choice, such as our happiness variable.
-The definition of the different response options to the happiness variable survey question of “not so happy”, “fairly happy”, and “very happy” will vary depending on the individual, as well as the day or time of day.
+The definition of the different response options to the happiness variable survey question of "not so happy", "fairly happy", and "very happy" will vary depending on the individual, as well as the day or time of day.
 Thus, our analysis of the relationship between happiness and Internet use may be biased.
@@
 ### Next Steps
+
 To address our second identified weakness in Section 4.4.2 above, implementing a supplementary survey with more detailed questions, particularly about race and gender (as mentioned in Section 2.2) and more straightforward question answers (e.g.

### 2023-03-15 outputs/paper/paper.qmd
Edited "paper.qmd" written content.

@@
 ---
-title: "My title"
-subtitle: "My subtitle if needed"
+title: "Younger, Unmarried, Childless, and Less Happy Americans Use the Internet the Most"
+subtitle: "An Analysis of the 2016 US General Social Survey"
 author: 
@@
 date-format: "D MMMM YYYY"
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "In this study, we investigated the 2016 United States General Social Survey to gain an understanding of the characteristics of the people that use the Internet the most, such as age, marital status, number of children, and level of happiness.
+We did this by comparing the average number of weekly Internet use across population groups.
+We found that young adults that have never been married or have children and who are not satisfied with their general happiness are those that use the Internet the most.
+In an era in which the Internet is becoming more and more used in the US, it is important to understand which population group uses the Internet the most in order to inform public policies surrounding Internet addiction and mental health.
+"
 format: pdf
@@
 
-The Internet has become a widely used computer network that allows for connection, to communicate, and access to information.
+The Internet has become a widely used computer network that allows for connection, communication, and access to information.
 By the mid 1990s, the Internet began reaching millions of users from around the world, where using a web of information, known as the World Wide Web, was a popular way of browsing information and facilitating communication online \[**cite**\].
-Throughout the years, the different ways in which the Internet is used have expanded, where users could also make purchases through electronic commerce platforms and share different forms of media on social media platforms.
+Throughout the years, the different ways in which the Internet is used have expanded, and now users can also make purchases through electronic commerce platforms and share different forms of media on social media platforms.
 
-This report aims to investigate the characteristics of those that use the Internet the most in comparison to those that use it the least.
-We wanted to understand the reasons as to why these factors are correlated with a higher internet use pattern and a lower internet use pattern.
-Our estimand is the mean number of weekly hours of internet usage of American adults.
-Using the survey data from the United States General Social Survey (GSS) recorded in 2016, we constructed different models on 6 factors and their relationship with total weekly hours of internet use: age, race, sex, marital status, number of children, and happiness.
+This report aims to investigate the characteristics of American adults that use the Internet the most in comparison to those that use it the least.
+We aim to understand the reasons why these factors are correlated with a higher Internet use pattern and a lower Internet use pattern.
+Our estimand is the mean number of weekly hours of Internet usage of American adults.
+Using the survey data from the United States General Social Survey (GSS) recorded in 2016, we constructed different models on 6 factors and their relationship with total weekly hours of Internet use: age, race, sex, marital status, number of children, and happiness.
 
-Through examining the different relationships between the various variables and the weekly total number of hours of internet use, we found that those of young adults tend to use the internet more than older adults.
-This may be due to physical, psychological, and social barriers when using the internet.
-We also found that those who have never been married use the internet more than others with different marital statuses.
-This could be correlated with age and the difference in reasons for using the internet.
-Additionally, as social media is a large part of internet usage, we found that the use of social media platforms has a negative impact on emotional health, demonstrating a possible correlation between low internet usage and a high level of happiness.
-Using the internet more regularly can improve the lives of individuals for its convenience and its accessibility.
+Through examining the different relationships between the various variables and the weekly total number of hours of Internet use, we found that young adults tend to use the Internet more than older adults.
+This may be due to physical, psychological, and social barriers when using the Internet.
+We also found that those who have never been married use the Internet more than others with different marital statuses.
+This could be correlated with age and the difference in reasons for using the Internet.
+Additionally, as social media is a large part of Internet usage, we found that the use of social media platforms has a negative impact on emotional health, demonstrating a possible correlation between low Internet usage and a high level of happiness.
+These findings are important because using the Internet more regularly can improve the lives of individuals for its convenience and its accessibility.
 It is beneficial because it allows for easier and instantaneous communication, for learning, for increasing access to services, for encouraging connections and decreasing isolation, and for gathering information \[**cite**\].
+However, the consequences of increased Internet usage, such as Internet addiction and mental health issues, should also be kept in mind.
+Our research on which population groups use the Internet the most in the US can set the stage for subsequent research investigating these pros and cons of Internet use on different population groups, and the ways in which the pros and cons affect those who use the Internet more.
 
@@
 
-The General Social Survey (GSS) is a national survey conducted in the United States of America that aims to better understand trends in the American adult population's social characteristics and attitudes to better inform research and public policy.
-(@cite3) Beginning in 1972, this interview-based survey is conducted biennially on five key themes: gender and marriage, current affairs, civil liberties, politics, and religion and spirituality.(@cite4) The 2016 GSS is unique in that it also includes questions about internet-usage behaviours, which is why our analysis focuses on the GSS of this year.
+The General Social Survey (GSS) is a national survey conducted in the United States of America that aims to better understand trends in the American adult population's social characteristics and attitudes to better inform research and public policy (@cite3).
+Beginning in 1972, this interview-based survey is conducted biennially on five key themes: gender and marriage, current affairs, civil liberties, politics, and religion and spirituality (@cite4).
+The 2016 GSS is unique in that it also includes questions about Internet-usage behaviours, which is why our analysis focuses on the GSS of this year.
 In 2016, there is data for 2,867 respondents for 961 variables.
@@
 The GSS' target population is adults aged 18 years and older living in the United States.
-The sampling frame for the 2016 GSS is people living in the US aged 18+ who can speak English or Spanish and live in households.
-(@cite5) Thus, those living outside households (e.g.
-university dorms, nursing homes, institutions, military quarters) are not included in the GSS.(@cite6) The frame was created using the NORC National Sampling Frame, which first uses Census data to stratify US geographic regions by size and then chooses metropolitan areas and non-metropolitan counties within these regions, as the first stage of selection.(@cite6) In the second stage of selection, these metropolitan areas and non-metropolitan counties were stratified by race and income and further divided into blocks.(@cite6) Then, the sample is gathered by interviewers beginning from the northwest corner of a given block and moving from household to household until the equal-sex quota has been filled.(@cite6)
+The sampling frame for the 2016 GSS is people living in the US aged 18+ who can speak English or Spanish and live in households (@cite5).
+Thus, those living outside households (e.g.
+in university dorms, nursing homes, institutions, military quarters) are not included in the GSS (@cite6).
+The frame was created using the NORC National Sampling Frame, which first uses US Census data to stratify US geographic regions by size and then chooses metropolitan areas and non-metropolitan counties within these regions, as the first stage of selection (@cite6).
+In the second stage of selection, these metropolitan areas and non-metropolitan counties were stratified by race and income and further divided into blocks (@cite6).
+Then, the sample is gathered by interviewers beginning from the northwest corner of a given block and moving from household to household until the equal-sex quota has been filled (@cite6).
 
-Thus, the sample for the 2016 GSS was an area-probability sample gathered by the clustered sampling approach, as households are selected and then one random member from the household is selected to be included in the survey.(@cite6) A key tradeoff of this approach is that while cluster sampling is that while this method is much easier than completely random sampling, it can lead to bias in that there is more bias if the clusters are similar to each other.
+Thus, the sample for the 2016 GSS was an area-probability sample gathered by the clustered sampling approach, as households are selected and then one random member from the household is selected to be included in the survey (@cite6).
+A key tradeoff of this approach is that while this method is much easier than completely random sampling, it can lead to bias in that there is more bias if the clusters are similar to each other.
 
@@
 
-A strength of this 2016 GSS survey was that it was delivered both in English and in Spanish, allowing for a greater reach than had the survey just been conducted in English, like in the years previous to 2006.(@cite6) Of the people who had been excluded from this survey due to the English-only delivery, Spanish-speakers made up the majority, so this dual language delivery addressed this key exclusion.
-(@cite6)
+A strength of this 2016 GSS survey was that it was delivered both in English and in Spanish, allowing for a greater reach than had the survey just been conducted in English, like in the years previous to 2006 (@cite6).
+Of the people who had been excluded from this survey due to the English-only delivery, Spanish-speakers made up the majority, so this dual language delivery addressed this key exclusion (@cite6).
 
-Another weakness of this sample is the lack of a gender variable, as the sample only provides a variable on sex.
+A weakness of this sample is the lack of a gender variable, as the sample only provides a variable on sex.
 A gender variable would be more useful for data analysis, as it better reflects the respondent's lived experience.
@@
 When the interviewer fills out the survey on behalf of the respondent, there may be a difference in the observed responses of the interviewer and the actual responses of the interviewee.
-This creates difficulty in verifying responses.
-(@cite13)
+This creates difficulty in verifying responses (@cite13).
 
-## Questionnaire
+A third weakness of the survey is the role of selection bias that exists due to the inability to reach the entire population.
+The survey may also be susceptible to volunteering bias because the data is reliant on participants willingly providing their answers, which could lead to biased results.
+
+## Questionnaire {#sec-questionnaire}
 
@@
 The survey question was formatted as follows: "Not counting e-mail, about how many minutes or hours per week do you use the Web?
-(Include time you spend visiting regular web sites and time spent using interactive Internet services like chat rooms, Usenet groups, discussion forums, bulletin boards, and the like.)".
+(Include time you spend visiting regular web sites and time spent using interactive Internet services like chat rooms, Usenet groups, discussion forums, bulletin boards, and the like.)" (@gss).
 The giving of examples was likely helpful in jogging the respondents' memory of what exactly Internet usage can look like, as if one is flat out asked whether they use the Internet, it can be hard to conceptualize what that looks like.
 
-A key weakness of this questionnaire is the race variable, as it only allows for three options: "Black", "White", or "Other", which does not take into account the largest ethnic minority group, Hispanics and Latino Americans, as well as other ethnic groups, such as Asians and Native Americans in the United States.
-In comparison, while not without fault itself, the US Census identifies 5 minimum categories of race (White, Black or African American, American Indian or Alaska Native, Asian, Native Hawaiian or Other Pacific Islander) and also allows for the reporting of more than one race.
-(@cite14)
+A key weakness of this questionnaire is the race variable, as it only allows for three options: "Black", "White", or "Other", which does not take into account the largest ethnic minority group, Hispanics and Latino Americans, as well as other ethnic groups, such as Asians and Indigenous people in the United States.
+In comparison, while not without fault itself, the US Census identifies 5 minimum categories of race (White, Black or African American, American Indian or Alaska Native, Asian, Native Hawaiian or Other Pacific Islander) and also allows for the reporting of more than one race (@cite14).
+The questionnaire should at least have followed these US Census minimum race categories.
 
-This questionnaire has a limitation in terms of selection bias because of our limited ability to reach the entire population.
-The respondents who receive the questionnaire are likely to share a similar background with us, which does not achieve a random selection of the population, which is all U.S.
-citizens.
-Our study may also be susceptible to volunteering bias because the data is reliant on participants willingly providing their answers, which could lead to biased results.
-
-Relatedly, another weakness of this questionnaire is that questions are allowed non-responses.
+Another weakness of this questionnaire is that questions are allowed non-responses.
 This results in truncated data, in which the dataset has been incompletely collected.
-Having no response for a question can only be observed as null, despite there being a possible actual value.
-(@cite15) There are a variety of reasons as to why a respondent did not want to answer a question, but can only be observed as a non-response to avoid biased assumptions and inaccurate results.
+Having no response for a question can only be observed as null, despite there being a possible actual value (@cite15).
+There are a variety of reasons as to why a respondent may not want to answer a question, but can only be observed as a non-response to avoid biased assumptions and inaccurate results.
 
@@
 This report was created using the R statistical programming language \[**cite**\].
-The here package was utilized to retrieve files from another folder within the same R project.
-\[**cite**\].
+The here package was utilized to retrieve files from another folder within the same R project \[**cite**\].
 For the results and analysis of this report, all figures were created using the tidyverse package \[**cite**\].
@@
 
-There are **7** variables that were selected to conduct the analysis of this report.
-We aimed to focus on **6** particular factors that supposedly affect the amount of Internet use: age, sex, race, number of children, marital status, and happiness.
-In this paper, we wanted to investigate the influence of these various factors on the total number of hours of weekly Internet usage.
+Our report selects 7 variables for analysis.
+We focus on 6 particular factors that we predicted affects the amount of Internet use: age, sex, race, number of children, marital status, and happiness.
+In this paper, we investigate the influence of these various factors on the total number of hours of weekly Internet usage.
 The packages tidyverse \[**cite**\], haven \[**cite**\], and reshape2 \[**cite**\] were used to clean the dataset by grouping or converting the questionnaire responses into categorical or textual answers.
@@
   slice(1:7) |> 
-  kable(caption='A subset of key features',
-        col.names = c("Weekly Internet Hours", "Age", "Sex", "Race",;
+  kable(caption = "The Variables of Study",
+        col.names = c("Weekly Internet Hours", "Age", "Sex", "Race",
                       "Number of Children", "Marital Status", "Happiness Level"),
@@
 Weekly Internet Hours has a maximum value of 168, as there are only 168 hours in a week.
-Age is also recorded as a numerical value, but is cleaned to represent ages in groups.
-The other variables, Sex, Race, Highest Degree, Number of Children, Marital Status and Happiness Level, are all recorded as a textual option for respondents to choose from.
+Age is also recorded as a numerical value, but is cleaned to represent ages in groups of ten years.
+The other variables, Sex, Race, Marital Status and Happiness Level, are all recorded as a textual option for respondents to choose from.
 
@@
 
-@fig-agesidebyside
-
 Most of the respondents of the 2016 GSS are adults ranging from ages 21 to 69 years old.
@@
 The largest age group respondent size is 50 to 59 years old.
-By graphing the variables, age and sex in \[FIG #\], we observe that there are more female adults in each age group participating in this survey than there are male adults.
+By graphing the variables, age and sex in @fig-agesidebyside, we observe that there are more female adults in each age group participating in this survey than there are male adults.
 The overall distribution is skewed to the right.
-The visualization of age and race in \[FIG #\] demonstrates that the respondents that identify with the White racial group comprises most of the respondent sample.
+The visualization of age and race in @fig-agesidebyside demonstrates that the respondents that identify with the White racial group comprises most of the respondent sample.
 This racial group is also shown to have a near-symmetrical distribution.
@@
 The Black and Other racial groups are skewed to the right, illustrating that there are less individuals that identify with these racial groups in the older age groups.
-According to the 2020 census surveys, the most common racial group in America is White or Caucasian, which means that the 2016 GSS data on this group provides an accurate representation of American society.
+According to the 2020 US Census surveys, the most common racial group in America is White or Caucasian, which means that the 2016 GSS data on this group provides a relatively accurate representation of American society [cite].
 
@@
 
-@fig-childsandmarital
-
-According to \[FIG #\], respondents who are married have a right skew distribution of the number of children they have, where the mode of the data is having two children.
+According to @fig-childsandmarital, respondents who are married have a right skew distribution of the number of children they have, where the mode of the data is having two children.
 As for individuals that responded as never having been married, the distribution was exponential, in which the mode of this distribution is having zero children.
@@
 
-@fig-happiness
-
-Considering general happiness, \[FIG #\] exhibits a left skew distribution.
+@fig-happiness demonstrates general happiness trends and exhibits a left skew distribution.
 This illustrates that a significant proportion of the respondents indicate that they are fairly happy and an adequate proportion indicate that they are very happy.
@@
 
-@fig-ageandinternet depicting the relationship between age and average weekly internet usage.
-The data on internet usage hours for various age groups are averaged to reduce any bias due to selectively chosen survey responses.
-The curve on the graph is skewed to the right, with its peak occurring in the 21 to 29 age group, which has the highest internet usage of approximately 18 hours per week.
-Subsequently, internet usage gradually declines with age, with the lowest usage recorded in the 89+ age group at an average of 2 hours per week.
-This graph indicates that young adults, particularly those aged 21 to 29, spend more time on the internet.
-As people age, their internet usage tends to decline gradually.
-The graph suggests a statistically significant correlation between age and internet usage, and the trend is relatively clear.
+@fig-ageandinternet depicts the relationship between age and average weekly Internet usage.
+The data on Internet usage hours for various age groups are averaged to reduce any bias due to selectively chosen survey responses.
+The curve on the graph is skewed to the right, with its peak occurring in the 21 to 29 age group, which has the highest Internet usage of approximately 18 hours per week.
+Subsequently, Internet usage gradually declines with age, with the lowest usage recorded in the 89+ age group at an average of 2 hours per week.
+This graph indicates that young adults, particularly those aged 21 to 29, spend more time on the Internet.
+As people age, their Internet usage tends to decline gradually.
+The graph suggests a statistically significant correlation between age and Internet usage, and the trend is relatively clear.
 
@@
 
-@fig-genderandinternet illustrates the average weekly internet usage of two genders.
-Similarly to the age and internet usage graph, the data on internet usage hours for different genders are averaged to minimize any volunteering bias.
-The data shows that there is no substantial difference between male and female internet usage.
-Female participants have an average of 12.9 hours per week spent on the internet, while male participants have an slightly higher average of 13.3 hours per week spent on the internet.
+@fig-genderandinternet illustrates the average weekly Internet usage of two sexes Similar to the age and Internet usage graph, the data on Internet usage hours for different genders are averaged to minimize any volunteering bias.
+The data shows that there is no substantial difference between male and female Internet usage.
+Female participants have an average of 12.9 hours per week spent on the Internet, while male participants have a slightly higher average of 13.3 hours per week spent on the Internet.
 However, the gender selection in this survey is limited, and further discussion regarding this limitation can be found in the ethics and bias section @sec-bias.
@@
 
-@fig-raceandinternet displays the average weekly internet usage of individuals belonging to different races.
-Based on the data, we can observe that individuals who do not identify as either Black or White have the highest internet usage, with an average of 15.5 hours per week.
-African American individuals have a similar level of internet usage, also averaging 15.2 hours per week.
-In contrast, white individuals tend to have the lowest internet usage, with an average of 12.3 hours per week.
+@fig-raceandinternet displays the average weekly Internet usage of individuals belonging to different races.
+Based on the data, we can observe that individuals who do not identify as either Black or White have the highest Internet usage, with an average of 15.5 hours per week.
+Black individuals have a similar level of Internet usage, also averaging 15.2 hours per week.
+In contrast, white individuals tend to have the lowest Internet usage, with an average of 12.3 hours per week.
 
@@
 @fig-childrenandinternet shows the relationship between respondents with a specific number of children and their weekly total hours of Internet use.
-Respondents that do not have any children are the group that uses the internet the most during the week.
+Respondents that do not have any children are the group that uses the Internet the most during the week.
 The data demonstrates that there is an inverse relationship between the two variables.
-This means that there is a gradual decrease of internet use hours as the number of children increases.
-However, the second largest group that uses the internet are those that reported having 8 children or more, making it an outlier.
+This means that there is a gradual decrease of Internet use hours as the number of children increases.
+However, the second largest group that uses the Internet are those that reported having 8 children or more, making it an outlier.
 
@@
 @fig-maritalandinternet displays the relationship between marital status and internet usage in 2016.
-In accordance with popular opinion, people who have never been married use the Internet the most.
-Most notably, people who are widowed use the Internet the least, perhaps due to the correlation between age and widowhood.
+In accordance with popular opinion, people who have never been married use the Internet the most, with an average of around 17.5 hours per week.
+Most notably, people who are widowed use the Internet the least, with an average of around 9.5 hours per week, perhaps due to the correlation between age and widowhood.
+The graph suggests a significant difference in the Internet use between these two population groups, with a difference of 8 hours between the two.
 
@@
 
-@fig-happyandinternet displays the relationship between perceived level of happiness and internet usage in 2016.
-There seems to be a direct decrease in internet usage the more happy the respondent measures themselves to be, with a difference of 2.5 hours between the happiest respondents and least happy respondents.
+@fig-happyandinternet displays the relationship between perceived level of happiness and Internet usage in 2016.
+People who reported the lowest level of happiness had the highest Internet usage, with an average of around 14 hours per week.
+People who reported the highest level of happiness had the lowest Internet usage, with an average of around 12 hours per week.
+There seems to be a direct decrease in Internet usage the more happy the respondent measures themselves to be, with a difference of 2 hours between the happiest respondents and least happy respondents.
 
@@
 Based on the results, we find that as aging increases, the amount of weekly total hour Internet use decreases.
-As shown in \@fig-ageandinternet, the majority of respondents that have the highest number of weekly hours of Internet use are those between the ages of 18 and 39 years old.
-The three age groups within this range have the three largest Internet usage.
-By observing the tail of the right-skewed distribution in \@fig-ageandinternet, it illustrates that as the age of respondents increases from the age range 20-29 years old, the use of the Internet is reduced.
-In this age of developing technology and digital services, the Internet has become a widely used source for information, commerce, communication, and entertainment.
+As shown in @fig-ageandinternet, the majority of respondents that have the highest number of weekly hours of Internet use are those between the ages of 18 and 39 years old.
+The three age groups within this range have the three largest Internet usages.
+By observing the tail of the right-skewed distribution in @fig-ageandinternet, the graph illustrates that as the age of respondents increases from the age range of 20-29 years old, the use of the Internet is reduced.
+In this era of developing technology and digital services, the Internet has become a widely used source for information, commerce, communication, and entertainment.
 According to our results, many young adults are commonly online.
@@
 Research has shown that 71% of seniors go online almost everyday and 11% go online three or five times weekly \[**cite**\].
-While many older adults understand the beneficial aspect of the Internet, there still remain non-users of the Internet due to disabilities that come with aging \[**cite**\].
+While many older adults understand the beneficial aspect of the Internet, there still remain many non-users of the Internet due to disabilities that come with aging \[**cite**\].
 
-## Second discussion point {#sec-second-point}
+## Marriage and Number of Children Reduces the Amount of Hours Spent Using the Internet {#sec-second-point}
 
@@
 
-## Third discussion point {#sec-third-point}
+## Happiness Reduces the Amount of Hours Spent Using the Internet {#sec-third-point}
 
-In a previous study, we found a potential correlation between happiness and internet usage.
-Specifically, individuals who reported lower internet usage tended to have higher levels of happiness.
-There are few reasons may be contribute to this finding.
+In a previous study, we found a potential correlation between happiness and Internet usage.
+Specifically, individuals who reported lower Internet usage tended to have higher levels of happiness.
+There are a few reasons that may contribute to this finding.
 
-We suspect this finding may be attributed to various factors related to social media usage, given that people spend an average of 2 hours and 31 minutes daily on social media.(@citea1) Our secondary research indicates that certain aspects of the internet, such as social media, can negatively impact psychological health.
+We suspect this finding may be attributed to various factors related to social media usage, given that people spend an average of 2 hours and 31 minutes daily on social media (@citea1).
+Our secondary research indicates that certain aspects of the Internet, such as social media, can negatively impact psychological health.
 Excessive use of social media can result in addiction, anxiety, depression, or isolation.
 Furthermore, social media can become a substitute for real-life social interaction, causing individuals to feel lonely and disconnected.
-Comparing oneself unfavorably with internet social figures can also lead to low self-esteem and negative body image, while cyberbullying can have potential mental health implications for individuals who spend long hours on the internet.
-A study by the University of Pennsylvania in 2018 found that reducing social media use to 30 minutes a day resulted in a significant reduction in anxiety, depression, loneliness, and sleep problems.(@citea2)
+Comparing oneself unfavourably with Internet social figures can also lead to low self-esteem and negative body image, while cyberbullying can have potential mental health implications for individuals who spend long hours on the Internet.
+A study by the University of Pennsylvania in 2018 found that reducing social media use to 30 minutes a day resulted in a significant reduction in anxiety, depression, loneliness, and sleep problems (@citea2).
 
 Additionally, research suggests that spending more time online can make children less happy with their lives.
-For instance, a study by the University of Sheffield concluded that spending an extra hour a day on social networks reduces the probability of being completely happy with life overall by approximately 14 percentage points.(@citea3) Thus, we have reason to believe that internet usage, particularly social media usage, can have a negative impact on happiness levels to some extent and affect the relationship between happiness and internet usage.
+For instance, a study by the University of Sheffield concluded that spending an extra hour a day on social networks reduces the probability of being completely happy with life overall by approximately 14 percentage points (@citea3).
+Thus, we have reason to believe that Internet usage, particularly social media usage, can have a negative impact on happiness levels to some extent and affect the relationship between happiness and Internet usage.
 
-Another factor that could contribute to the correlation between happiness and internet usage is a fulfilling real life.
+Another factor that could contribute to the correlation between happiness and Internet usage is a fulfilling real life.
 Engaging in offline activities, such as spending time with loved ones, pursuing hobbies, or achieving personal goals, can be more rewarding than spending time online.
-This can lead individuals to prioritize fulfilling activities over aimless scrolling through the internet and decrease their need for validation or connection through social media and other online platforms.
-Thus, individuals who are fulfilled in their offline lives may have lower internet usage hours and higher happiness levels.
+This can lead individuals to prioritize fulfilling activities over aimless scrolling through the Internet and decrease their need for validation or connection through social media and other online platforms.
+Thus, individuals who are fulfilled in their offline lives may have lower Internet usage hours and higher happiness levels.
 
-## Weaknesses and next steps {#sec-weaknesses}
+## Weaknesses and Next Steps {#sec-weaknessesandnextsteps}
 
-### Weakness
+### Weakness {#sec-weaknesses}
 
@@
 A central reason as to why participant's may have chosen not to respond to the question about Internet use could be embarrassment: admitting that one spends too much time on the Internet could be embarrassing, so those who have higher Internet usage are more likely not to respond to this question.
-This is a very real concern as Internet addiction is increasing in our increasingly digital world, and several countries have even identified it as a public health concern.
-(@cite26)
+This is a very real concern as Internet addiction is increasing in our increasingly digital world, and several countries have even identified it as a public health concern (@cite26).
 
@@
 
-To address our second identified weakness in Section 4.4.2 above, implementing a supplementary survey with more detailed questions, particularly about race and gender (as mentioned in Section 2.2) and more straightforward question answers (e.g.
+To address our second identified weakness in @sec-weaknesses above, implementing a supplementary survey with more detailed questions, particularly about race and gender (as mentioned in @sec-questionnaire) and more straightforward question answers (e.g.
 a number scale for happiness variable) would allow for more in-depth analysis.
@@
 Since this sampling approach focuses only on a specific age group, our analysis may be biased with respect to the age factor.
-Gss also claimed to be strictly voluntary.
+GSS also claimed to be strictly voluntary.
 While this approach supports research ethics by respecting individuals' autonomy and right to privacy, it can also result in volunteer bias.
-GSS sample are from a mix of urban, suburban, and rural geographic areas, but only a few thousand respondents are interviewed in the main study.
-The small sample size may be lead to chance findings.
-It is likely not statistically significant enough.
-We also suspect potential sampling bias may screw our end result.
+The GSS sample is from a mix of urban, suburban, and rural geographic areas, but only a few thousand respondents are interviewed in the main study.
+The small sample size may lead to chance findings.
+We also suspect potential sampling bias may bias our end result.
 However, with not enough information disclosed, we are unable to confirm that.
 The gender and race options provided by the GSS survey are limited.
-Participants are only given the options of selecting either "Female" or "Male" for gender, and "Blacks," "Whites," or "Others" for race.
+Participants are only given the options of selecting either "Female" or "Male" for gender, and "Black," "White," or "Other" for race.
 This narrow selection does not provide an adequate range of options for survey participants.

### 2023-03-16 scripts/03-rough_work.R
Removed our rough work script from our final version.

@@ -1,414 +1,0 @@
-#### Preamble ####
-# Purpose: Rough work.
-# Author: Sakura Ariga, Annie Yan, Aliyah Maxine Ramos
-# Data: 2  March 2023
-# Contact: aliyahmaxine.ramos@mail.utoronto.ca
-# License: MIT
-# Pre-requisites: None.
-# Any other information needed? None
-
-#### Graphs ####
-
-library(tidyverse)
-library(lessR)
-library(dplyr)
-library(tidyr)
-library(reshape2)
-library(ggplot2)
-
-
-#read csv
-cleaned_2016gss_data <- read_csv("outputs/data/cleaned_2016gss_data.csv")
-
-
-### BAR GRAPHS OF EACH VARIABLE to show how many respondents for each option ###
-
-### COMPARE SEX, RACE, DEGREE WITH AGE ###
-
-# age sex and race
-# cleaned_2016gss_data |>
-#   ggplot(mapping = aes(x = age, fill = race)) +
-#     geom_bar() +
-#     theme_minimal() +
-#     theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-#     labs(
-#       x = "Age-group of respondent",
-#       y = "Number of respondents",
-#       fill = "Voted for"
-#     ) +
-#     facet_wrap(
-#       vars(sex),
-#       dir = "v",
-#       scales = "free"
-#     ) +
-#     theme(legend.position = "bottom")
-
-# age
-# cleaned_2016gss_data |>
-#   ggplot(mapping = aes(x = age)) +
-#   geom_bar() +
-#   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-#   labs(x = "Age", y = "Number of Respondents")
-
-# sex
-# cleaned_2016gss_data |>
-#   ggplot(mapping = aes(x = sex)) +
-#   geom_bar() +
-#   labs(x = "Sex", y = "Number of Respondents")
-
-# age and sex
-cleaned_2016gss_data |>
-  ggplot(mapping = aes(x = age, fill = sex)) + 
-  theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-  geom_bar(position = "dodge2")
-
-# race
-# cleaned_2016gss_data |>
-#   ggplot(mapping = aes(x = race)) +
-#   geom_bar() +
-#   labs(x = "Race", y = "Number of Respondents")
-
-# age and race
-cleaned_2016gss_data |>
[…]

### 2023-03-16 scripts/00-simulate_data.R
Deleted license line from each of the scripts as the license was deleted from the final version.

@@ -3,7 +3,6 @@
 # Author: Sakura Ariga, Annie Yan, Aliyah Maxine Ramos
 # Data: 2  March 2023
 # Contact: aliyahmaxine.ramos@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: Need to know where to get survey data.
 # Any other information needed? None
 

### 2023-03-16 scripts/01-download_data.R

@@ -3,7 +3,6 @@
 # Author: Sakura Ariga, Annie Yan, Aliyah Maxine Ramos
 # Data: 2 March 2023
 # Contact: aliyahmaxine.ramos@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: Need to know where to get survey data.
 # Any other information needed? None.
 

### 2023-03-16 scripts/02-data_cleaning.R

@@ -3,7 +3,6 @@
 # Author: Sakura Ariga, Annie Yan, Aliyah Maxine Ramos
 # Data: 2 March 2023
 # Contact: aliyahmaxine.ramos@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: None.
 # Any other information needed? None.
 

### 2023-03-16 scripts/03-test_data.R

@@ -3,7 +3,6 @@
 # Author: Sakura Ariga, Annie Yan, Aliyah Maxine Ramos
 # Data: 2 March 2023
 # Contact: aliyahmaxine.ramos@mail.utoronto.ca
-# License: MIT
 # Pre-requisites: Must have simulated data.
 # Any other information needed? None.
 

### 2023-03-16 outputs/paper/paper.qmd
Final edits of Quarto document

@@
 The Internet has become a widely used computer network that allows for connection, communication, and access to information.
-By the mid 1990s, the Internet began reaching millions of users from around the world, where using a web of information, known as the World Wide Web, was a popular way of browsing information and facilitating communication online \[**cite**\].
+By the mid 1990s, the Internet began reaching millions of users from around the world, where using a web of information, known as the World Wide Web, was a popular way of browsing information and facilitating communication online [@citem1].
 Throughout the years, the different ways in which the Internet is used have expanded, and now users can also make purchases through electronic commerce platforms and share different forms of media on social media platforms.
@@
 
-Through examining the different relationships between the various variables and the weekly total number of hours of Internet use, we found that young adults tend to use the Internet more than older adults.
+Through examining the relationships between the variables and the weekly number of hours of Internet use, we found that young adults tend to use the Internet more than older adults.
 This may be due to physical, psychological, and social barriers when using the Internet.
 We also found that those who have never been married use the Internet more than others with different marital statuses.
-This could be correlated with age and the difference in reasons for using the Internet.
-Additionally, as social media is a large part of Internet usage, we found that the use of social media platforms has a negative impact on emotional health, demonstrating a possible correlation between low Internet usage and a high level of happiness.
+This could be related to age and the difference in reasons for using the Internet.
+Additionally, as social media is a large part of Internet usage, we found that the using these platforms have a negative impact on emotional health, demonstrating a possible correlation between high Internet usage and a low level of happiness.
 These findings are important because using the Internet more regularly can improve the lives of individuals for its convenience and its accessibility.
-It is beneficial because it allows for easier and instantaneous communication, for learning, for increasing access to services, for encouraging connections and decreasing isolation, and for gathering information \[**cite**\].
+It is beneficial because it allows for easier and instantaneous communication, for learning, for increasing access to services, for encouraging connections and decreasing isolation, and for gathering information [@citem2].
 However, the consequences of increased Internet usage, such as Internet addiction and mental health issues, should also be kept in mind.
-Our research on which population groups use the Internet the most in the US can set the stage for subsequent research investigating these pros and cons of Internet use on different population groups, and the ways in which the pros and cons affect those who use the Internet more.
+Our research on which population groups use the Internet the most in the US can lay the foundation for subsequent research investigating the pros and cons of Internet use on different population groups, and the ways in which the pros and cons affect those who use the Internet more.
 
@@
 
-The General Social Survey (GSS) is a national survey conducted in the United States of America that aims to better understand trends in the American adult population's social characteristics and attitudes to better inform research and public policy (@cite3).
-Beginning in 1972, this interview-based survey is conducted biennially on five key themes: gender and marriage, current affairs, civil liberties, politics, and religion and spirituality (@cite4).
+The General Social Survey (GSS) is a national survey conducted in the United States of America that aims to better understand trends in the American adult population's social characteristics and attitudes to better inform research and public policy [@cite3].
+Beginning in 1972, this interview-based survey is conducted biennially on five key themes: gender and marriage, current affairs, civil liberties, politics, and religion and spirituality [@cite4].
 The 2016 GSS is unique in that it also includes questions about Internet-usage behaviours, which is why our analysis focuses on the GSS of this year.
@@
 The GSS' target population is adults aged 18 years and older living in the United States.
-The sampling frame for the 2016 GSS is people living in the US aged 18+ who can speak English or Spanish and live in households (@cite5).
+The sampling frame for the 2016 GSS is people living in the US aged 18+ who can speak English or Spanish and live in households [@cite5].
 Thus, those living outside households (e.g.
-in university dorms, nursing homes, institutions, military quarters) are not included in the GSS (@cite6).
-The frame was created using the NORC National Sampling Frame, which first uses US Census data to stratify US geographic regions by size and then chooses metropolitan areas and non-metropolitan counties within these regions, as the first stage of selection (@cite6).
-In the second stage of selection, these metropolitan areas and non-metropolitan counties were stratified by race and income and further divided into blocks (@cite6).
-Then, the sample is gathered by interviewers beginning from the northwest corner of a given block and moving from household to household until the equal-sex quota has been filled (@cite6).
+in university dorms, nursing homes, institutions, military quarters) are not included in the GSS [@cite6].
+The frame was created using the NORC National Sampling Frame, which first uses US Census data to stratify US geographic regions by size and then chooses metropolitan areas and non-metropolitan counties within these regions, as the first stage of selection [@cite6].
+In the second stage of selection, these metropolitan areas and non-metropolitan counties were stratified by race and income and further divided into blocks [@cite6].
+Then, the sample is gathered by interviewers beginning from the northwest corner of a given block and moving from household to household until the equal-sex quota has been filled [@cite6].
 
-Thus, the sample for the 2016 GSS was an area-probability sample gathered by the clustered sampling approach, as households are selected and then one random member from the household is selected to be included in the survey (@cite6).
-A key tradeoff of this approach is that while this method is much easier than completely random sampling, it can lead to bias in that there is more bias if the clusters are similar to each other.
+Thus, the sample for the 2016 GSS was an area-probability sample gathered by the clustered sampling approach, as households are selected and then one random member from the household is selected to be included in the survey [@cite6].
+A key tradeoff of this approach is that, while this method is much easier than solely random sampling, it can lead to bias in that there is more bias if the clusters are similar to each other.
 
@@
 
-A strength of this 2016 GSS survey was that it was delivered both in English and in Spanish, allowing for a greater reach than had the survey just been conducted in English, like in the years previous to 2006 (@cite6).
-Of the people who had been excluded from this survey due to the English-only delivery, Spanish-speakers made up the majority, so this dual language delivery addressed this key exclusion (@cite6).
+A strength of this 2016 GSS survey was that it was delivered both in English and in Spanish, allowing for a greater reach than had the survey just been conducted in English, like in the years previous to 2006 [@cite6].
+Of the people who had been excluded from this survey due to the English-only delivery, Spanish-speakers made up the majority, so this dual language delivery addressed this key exclusion [@cite6].
 
@@
 
-Another weakness of the 2016 GSS survey is that the interviewer physically fills out the response for the respondent.
+Another weakness of the 2016 GSS survey is that the interviewer physically fills out the responses for the respondent.
 This can potentially lead to measurement error.
 When the interviewer fills out the survey on behalf of the respondent, there may be a difference in the observed responses of the interviewer and the actual responses of the interviewee.
-This creates difficulty in verifying responses (@cite13).
+This creates difficulty in verifying responses [@cite13].
 
@@
 (Include time you spend visiting regular web sites and time spent using interactive Internet services like chat rooms, Usenet groups, discussion forums, bulletin boards, and the like.)" (@gss).
-The giving of examples was likely helpful in jogging the respondents' memory of what exactly Internet usage can look like, as if one is flat out asked whether they use the Internet, it can be hard to conceptualize what that looks like.
+The providing of examples was likely helpful in stimulating the respondents' memory of what exactly Internet usage can look like, as if one is flat out asked whether they use the Internet, it can be hard to conceptualize what that looks like.
 
-A key weakness of this questionnaire is the race variable, as it only allows for three options: "Black", "White", or "Other", which does not take into account the largest ethnic minority group, Hispanics and Latino Americans, as well as other ethnic groups, such as Asians and Indigenous people in the United States.
-In comparison, while not without fault itself, the US Census identifies 5 minimum categories of race (White, Black or African American, American Indian or Alaska Native, Asian, Native Hawaiian or Other Pacific Islander) and also allows for the reporting of more than one race (@cite14).
+A key weakness of this questionnaire is the race variable, as it only allows for three options: "Black", "White", or "Other", which does not take into account the largest ethnic minority group, Hispanics and Latino Americans, as well as other ethnic groups, such as Asians and Indigenous Americans in the United States.
+In comparison, while not without fault itself, the US Census identifies 5 minimum categories of race (White, Black or African American, American Indian or Alaska Native, Asian, Native Hawaiian or Other Pacific Islander) and also allows for the reporting of more than one race [@cite14].
 The questionnaire should at least have followed these US Census minimum race categories.
@@
 This results in truncated data, in which the dataset has been incompletely collected.
-Having no response for a question can only be observed as null, despite there being a possible actual value (@cite15).
-There are a variety of reasons as to why a respondent may not want to answer a question, but can only be observed as a non-response to avoid biased assumptions and inaccurate results.
+Having no response for a question can only be observed as null, despite there being a possible actual value [@cite15].
+There are a variety of reasons as to why a respondent may not want to answer a question, but can only be observed as a non-response by researchers to avoid biased assumptions and inaccurate results.
 
@@
 In this report, the 2867 observations from the 2016 United States General Social Survey are used.
-The survey data was obtained from the University of Chicago National Opinion Research Centre (NORC) \[**cite**\].
+The survey data was obtained from the University of Chicago National Opinion Research Centre (NORC) [@gss].
 
-This report was created using the R statistical programming language \[**cite**\].
-The here package was utilized to retrieve files from another folder within the same R project \[**cite**\].
-For the results and analysis of this report, all figures were created using the tidyverse package \[**cite**\].
-Additionally, the tables were created using the packages vtable \[**cite**\] and kableExtra \[**cite**\], and the graphs were created using the packages lessR \[**cite**\], dplyr \[**cite**\], tidyr \[**cite**\], reshape2 \[**cite**\], and ggplot2 \[**cite**\].
+This report was created using the R statistical programming language [@R].
+The here package was utilized to retrieve files from another folder within the same R project [@here].
+For the results and analysis of this report, all figures were created using the tidyverse package [@tidyverse].
+Additionally, the tables were created using the packages knitr [@knitr] and kableExtra [@kableExtra], and the graphs were created using the packages lessR [@lessR], tidyr [@tidyr], and ggplot2 [@ggplot2].
 
@@
 In this paper, we investigate the influence of these various factors on the total number of hours of weekly Internet usage.
-The packages tidyverse \[**cite**\], haven \[**cite**\], and reshape2 \[**cite**\] were used to clean the dataset by grouping or converting the questionnaire responses into categorical or textual answers.
+The packages tidyverse [@tidyverse], haven [@haven], and reshape2 [@reshape2] were used to clean the dataset by grouping or converting the questionnaire responses into categorical or textual answers.
 
@@
 #| echo: false
+#| tbl-cap: The Variables of Interest
+#| label: tbl-variables
 
@@
 
-Table 1 shows the first 10 rows of the cleaned dataset.
+@tbl-variables shows the first 10 rows of the cleaned dataset.
 The variables, Number of Children and Weekly Internet Hours, are recorded as a numerical value.
@@
 Age is also recorded as a numerical value, but is cleaned to represent ages in groups of ten years.
-The other variables, Sex, Race, Marital Status and Happiness Level, are all recorded as a textual option for respondents to choose from.
+The other variables, Sex, Race, Marital Status, and Happiness Level, are all recorded as a textual option for respondents to choose from.
 
@@
 #| label: fig-agesidebyside
-#| fig-cap: Caption
-#| fig-subcap: ["Subcaption"]
+#| fig-cap: Relationship between Age and Sex and Age and Race
+#| fig-subcap: ["Relationship between Age and Sex", "Relationship Between Age and Race"]
 #| layout-ncol: 2
@@
 The Black and Other racial groups are skewed to the right, illustrating that there are less individuals that identify with these racial groups in the older age groups.
-According to the 2020 US Census surveys, the most common racial group in America is White or Caucasian, which means that the 2016 GSS data on this group provides a relatively accurate representation of American society [cite].
+According to the 2020 US Census surveys, the most common racial group in America is White or Caucasian, which means that the 2016 GSS data on this group provides a relatively accurate representation of American society [@citem3].
 
@@
 #| label: fig-childsandmarital
-#| fig-cap: Caption
+#| fig-cap: Relationship between Marital Status and Number of Children
 #| echo: false
@@
 #| label: fig-happiness
-#| fig-cap: Caption
+#| fig-cap: Happiness Level Responses from Survey Respondents
 #| echo: false
@@
 
-@fig-genderandinternet illustrates the average weekly Internet usage of two sexes Similar to the age and Internet usage graph, the data on Internet usage hours for different genders are averaged to minimize any volunteering bias.
+@fig-genderandinternet illustrates the average weekly Internet usage of two sexes.
+Similar to the age and Internet usage graph, the data on Internet usage hours for different genders are averaged to minimize any volunteering bias.
 The data shows that there is no substantial difference between male and female Internet usage.
@@
 Black individuals have a similar level of Internet usage, also averaging 15.2 hours per week.
-In contrast, white individuals tend to have the lowest Internet usage, with an average of 12.3 hours per week.
+In contrast, White individuals tend to have the lowest Internet usage, with an average of 12.3 hours per week.
 
@@
 Respondents that do not have any children are the group that uses the Internet the most during the week.
+Their average amount of hours of weekly Internet use is approximately 16.5 hours.
 The data demonstrates that there is an inverse relationship between the two variables.
 This means that there is a gradual decrease of Internet use hours as the number of children increases.
-However, the second largest group that uses the Internet are those that reported having 8 children or more, making it an outlier.
+The group that uses the least amount of hours, with an average of approximately 1.5 hours of Internet use weekly, are those with 7 children.
+However, the second largest group that uses the Internet are those that reported having 8 children or more, making this group an outlier.
 
@@
 
-@fig-maritalandinternet displays the relationship between marital status and internet usage in 2016.
+@fig-maritalandinternet displays the relationship between marital status and Internet usage in 2016.
 In accordance with popular opinion, people who have never been married use the Internet the most, with an average of around 17.5 hours per week.
@@
 The three age groups within this range have the three largest Internet usages.
-By observing the tail of the right-skewed distribution in @fig-ageandinternet, the graph illustrates that as the age of respondents increases from the age range of 20-29 years old, the use of the Internet is reduced.
+By observing the tail of the right-skewed distribution in @fig-ageandinternet, the graph illustrates that as the age of respondents increases beginning from the age range of 20-29 years old, the use of the Internet reduces.
 In this era of developing technology and digital services, the Internet has become a widely used source for information, commerce, communication, and entertainment.
@@
 The reason for this may be because, as individuals age, they experience declining changes in their physical, mental, and social abilities, affecting their functional capacities.
-Research has shown that 23% of older adults indicate that having a physical or health condition makes reading difficult or challenging \[**cite**\].
+Research has shown that 23% of older adults indicate that having a physical or health condition makes reading difficult or challenging [@citem4].
 This shows that those in older age groups have barriers when it comes to using the Internet.
-Although using the Internet is valuable to those of older age, as it helps them connect with family remotely and experience socialization, the factors that make using the Internet challenging keeps them from increasing their weekly use.
-Many older adults have expressed that, when using technology and digital services, they would need assistance \[**cite**\].
+Although using the Internet is valuable to those of older age, as it helps them connect with family members remotely and experience socialization, the factors that make using the Internet challenging keeps them from increasing their weekly use.
+Many older adults have expressed that, when using technology and digital services, they would need assistance [@citem4].
 Despite seniors being less likely than the rest of the population to go online, once they understand how to use it, it becomes a part of their everyday lives.
-Research has shown that 71% of seniors go online almost everyday and 11% go online three or five times weekly \[**cite**\].
-While many older adults understand the beneficial aspect of the Internet, there still remain many non-users of the Internet due to disabilities that come with aging \[**cite**\].
+Research has shown that 71% of seniors go online almost everyday and 11% go online three to five times weekly [@citem4].
+While many older adults understand the beneficial aspect of the Internet, there still remains many non-users of the Internet due to disabilities that come with aging [@citem4].
 
@@
 This trend could partially be explained by the correlation between age and being married, as those who have never been married are more likely to be younger.
-In the United States in 2016, at the time this survey data was collected, the median age of marriage was 28 years old for women and 30 years old for men.
-(@cite19) This statistic is consistent with the findings of @fig-ageandinternet, which shows that Internet usage is highest for people aged 21 to 29, people who are just prior to the median age of marriage.
+In the United States in 2016, at the time this survey data was collected, the median age of marriage was 28 years old for women and 30 years old for men [@cite19].
+This statistic is consistent with the findings of @fig-ageandinternet, which shows that Internet usage is highest for people aged 21 to 29, people who are just prior to the median age of marriage.
 This explanation is supported by the finding that widowed people use the Internet the least, out of all of the marital categories.
-Because widowhood is more likely in people who are older, the correlation between age and Internet use is further reflected here.
-(@cite20) Thus, the relationship between marriage vs.
-non-marriage and Internet use, in which those who have never been married use the Internet more than those who are married, is related to the inverse relationship between age and amount of average Internet use stated in Section 4.1 above.
+Because widowhood is more likely in people who are older, the correlation between age and Internet use is further reflected here [@cite20].
+Thus, the relationship between marriage versus non-marriage and Internet use, in which those who have never been married use the Internet more than those who are married, is related to the inverse relationship between age and amount of average Internet use stated in Section 4.1 above.
 
 This trend of younger and non-married people using the Internet more than older, married people could be further explained by the use of online and digital dating apps by younger, non-married people as ways to connect with people romantically.
-The United States is one of the countries that uses online dating sites and apps the most, suggesting that online dating is normalized in American culture and partially explaining why younger, non-married people use the Internet much more than their older, married counterparts.(@cite21) The widespread usage of handheld mobile devices that has become the norm for all age groups, but especially younger people who are more likely to use social media and online dating apps, furthers this.
+The United States is one of the countries that uses online dating sites and apps the most, suggesting that online dating is normalized in American culture and partially explaining why younger, non-married people use the Internet much more than their older, married counterparts [@cite21].
+The widespread usage of handheld mobile devices that has become the norm for all age groups, but especially younger people who are more likely to use social media and online dating apps, furthers this.
 
 A third contributing factor to this trend could be that non-married individuals feel more isolated due to not meeting societal norms of marriage and turn to the Internet to seek connections and community.
-People who live in societies in which marriage is socially expected, such as the United States, can feel isolated, for which using the Internet can help them feel a sense of belonging that they find missing in their lives.(@cite22)
+People who live in societies in which marriage is socially expected, such as the United States, can feel isolated, for which using the Internet can help them feel a sense of belonging that they find missing in their lives [@cite22].
 
@@
 Like Section 4.2.1 above, this could be due to the correlation between age and having children: those who are older are more likely to have children than those who are younger.
-The median age at which women have children is 30 years of age, which is consistent with the findings of @fig-ageandinternet, which states that people in their 20s use the Internet the most.(@cite23) This generally inverse relationship between number of children and Internet use, is related to the inverse relationship between age and amount of average Internet use stated in Section 4.1 above.
+The median age at which women have children is 30 years of age, which is consistent with the findings of @fig-ageandinternet, which states that people in their 20s use the Internet the most [@cite23].
+This general inverse relationship between number of children and Internet use, is related to the inverse relationship between age and amount of average Internet use stated in Section 4.1 above.
 The outlier of the "8+" children category has a high Internet usage because there were only 6 people who responded about their Internet usage in that category (compared to the approximately 500 people who responded about their Internet usage in the "0" children category), such that the result was skewed by one participant who reported 60 hours of Internet use.
@@
 This trend could also be explained by the amount of personal time that people have for themselves.
-Personal use is one of the main activities of Internet use (including instant messaging and social media), and people with children are less likely to have time for themselves as they spend time caring for their children.(@cite24) This likely increases with more children.
+Personal use is one of the main activities of Internet use (including instant messaging and social media), and people with children are less likely to have time for themselves as they spend time caring for their children [@cite24].
+This likely increases with more children.
 Thus, the relatively inverted relationship between number of children and Internet use could be partially explained by the inverted relationship between number of children and personal time.
 
-However, the Internet has increasingly come to be a key resource for parenting, both for getting information and for receiving support.(@cite25) This explains why average Internet use is relatively similar across people with 1 child to 5 children.
+However, the Internet has increasingly come to be a key resource for parenting, both for getting information and for receiving support [@cite25].
+This explains why average Internet use is relatively similar across people with 1 child to 5 children.
 
@@
 
-We suspect this finding may be attributed to various factors related to social media usage, given that people spend an average of 2 hours and 31 minutes daily on social media (@citea1).
+We suspect this finding may be attributed to various factors related to social media usage, given that people spend an average of 2 hours and 31 minutes daily on social media [@citea1].
 Our secondary research indicates that certain aspects of the Internet, such as social media, can negatively impact psychological health.
@@
 Comparing oneself unfavourably with Internet social figures can also lead to low self-esteem and negative body image, while cyberbullying can have potential mental health implications for individuals who spend long hours on the Internet.
-A study by the University of Pennsylvania in 2018 found that reducing social media use to 30 minutes a day resulted in a significant reduction in anxiety, depression, loneliness, and sleep problems (@citea2).
+A study by the University of Pennsylvania in 2018 found that reducing social media use to 30 minutes a day resulted in a significant reduction in anxiety, depression, loneliness, and sleep problems [@citea2].
 
 Additionally, research suggests that spending more time online can make children less happy with their lives.
-For instance, a study by the University of Sheffield concluded that spending an extra hour a day on social networks reduces the probability of being completely happy with life overall by approximately 14 percentage points (@citea3).
+For instance, a study by the University of Sheffield concluded that spending an extra hour a day on social networks reduces the probability of being completely happy with life overall by approximately 14 percentage points [@citea3].
 Thus, we have reason to believe that Internet usage, particularly social media usage, can have a negative impact on happiness levels to some extent and affect the relationship between happiness and Internet usage.
@@
 A central reason as to why participant's may have chosen not to respond to the question about Internet use could be embarrassment: admitting that one spends too much time on the Internet could be embarrassing, so those who have higher Internet usage are more likely not to respond to this question.
-This is a very real concern as Internet addiction is increasing in our increasingly digital world, and several countries have even identified it as a public health concern (@cite26).
+This is a very real concern as Internet addiction is emerging rapidly in our increasingly digital world, and several countries have even identified it as a public health concern [@cite26].
 
@@
 
-In addition, conducting further research on the different uses of the Internet based on population groups would be a reasonable next step, now that we have determined which population groups use the Internet the most and least.
+In addition, conducting further research on the different uses of the Internet based on population groups would be a reasonable next step, now that we have determined which population groups use the Internet the most and the least.
 
@@
 While this approach supports research ethics by respecting individuals' autonomy and right to privacy, it can also result in volunteer bias.
-The GSS sample is from a mix of urban, suburban, and rural geographic areas, but only a few thousand respondents are interviewed in the main study.
+The GSS sample is from a combination of urban, suburban, and rural geographic areas, but only a few thousand respondents are interviewed in the main study.
 The small sample size may lead to chance findings.
-We also suspect potential sampling bias may bias our end result.
+We also suspect potential sampling bias may affect our end results.
 However, with not enough information disclosed, we are unable to confirm that.

### 2023-03-16 outputs/paper/paper.qmd
Final edits to quarto document - removing errors that caused rendering to fail

@@
 
-```{r}
-#| echo: false
-#| tbl-cap: The Variables of Interest
-#| label: tbl-variables
-
-# Table showing the first 10 rows of our cleaned dataset
-cleaned_2016gss_data |> 
-  select(wwwhr, age, sex, race, childs, marital, happy) |> 
-  slice(1:7) |> 
-  kable(caption = "The Variables of Study",
-        col.names = c("Weekly Internet Hours", "Age", "Sex", "Race",
-                      "Number of Children", "Marital Status", "Happiness Level"),
-        digits = 1,
-        booktabs = FALSE,
-        linesep = "") |>
-  kable_styling(full_width = T)
-```
-
-@tbl-variables shows the first 10 rows of the cleaned dataset.
 The variables, Number of Children and Weekly Internet Hours, are recorded as a numerical value.

### 2023-03-16 outputs/paper/paper.qmd
update changes

--- 2023-03-16 outputs/paper/paper.qmd
@@
 date-format: "D MMMM YYYY"
+format: 
+  pdf:
+    documentclass: article
+    geometry: margin = 1in
     abstract: "In this study, we investigated the 2016 United States General Social Survey to gain an understanding of the characteristics of the people that use the Internet the most, such as age, marital status, number of children, and level of happiness.
@@
 "
-format: pdf
 number-sections: true

### 2023-03-16 outputs/paper/paper.tex
update changes

@@
 \documentclass[
-  letterpaper,
-  DIV=11,
-  numbers=noendperiod]{scrartcl}
+]{article}
 
@@
 \usepackage{xcolor}
+\usepackage[margin = 1in]{geometry}
 \setlength{\emergencystretch}{3em} % prevent overfull lines
@@
 \makeatother
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
@@
 \usepackage{xcolor}
-\KOMAoption{captions}{tableheading}
 \makeatletter
@@
 \hypersetup{
-  pdftitle={My title},
+  pdftitle={Younger, Unmarried, Childless, and Less Happy Americans Use the Internet the Most},
   pdfauthor={Sakura Ariga; Aliyah Maxine Ramos; Annie Yan},
@@
 
-\title{My title\thanks{Code and data are available at:
+\title{Younger, Unmarried, Childless, and Less Happy Americans Use the
+Internet the Most\thanks{Code and data are available at:
 https://github.com/AnnieYan0807/GSS-data-analysis.git.}}
@@
 \makeatother
-\subtitle{My subtitle if needed}
+\subtitle{An Analysis of the 2016 US General Social Survey}
 \author{Sakura Ariga \and Aliyah Maxine Ramos \and Annie Yan}
@@
 \begin{abstract}
-First sentence. Second sentence. Third sentence. Fourth sentence.
+In this study, we investigated the 2016 United States General Social
+Survey to gain an understanding of the characteristics of the people
+that use the Internet the most, such as age, marital status, number of
+children, and level of happiness. We did this by comparing the average
+number of weekly Internet use across population groups. We found that
+young adults that have never been married or have children and who are
+not satisfied with their general happiness are those that use the
+Internet the most. In an era in which the Internet is becoming more and
+more used in the US, it is important to understand which population
+group uses the Internet the most in order to inform public policies
+surrounding Internet addiction and mental health.
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[interior hidden, breakable, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, breakable, interior hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, frame hidden, boxrule=0pt]}{\end{tcolorbox}}\fi
 
 \hypertarget{introduction}{%
-\section{1 Introduction}\label{introduction}}
+\section{Introduction}\label{introduction}}
 
-You can and should cross-reference sections and sub-sections. For
-instance, Section~\ref{sec-data} and Section~\ref{sec-first-point}.
+The Internet has become a widely used computer network that allows for
+connection, communication, and access to information. By the mid 1990s,
+the Internet began reaching millions of users from around the world,
+where using a web of information, known as the World Wide Web, was a
+popular way of browsing information and facilitating communication
+online ({``A Short History of the Internet''} 2020). Throughout the
+years, the different ways in which the Internet is used have expanded,
+and now users can also make purchases through electronic commerce
+platforms and share different forms of media on social media platforms.
+
+This report aims to investigate the characteristics of American adults
+that use the Internet the most in comparison to those that use it the
+least. We aim to understand the reasons why these factors are correlated
+with a higher Internet use pattern and a lower Internet use pattern. Our
+estimand is the mean number of weekly hours of Internet usage of
+American adults. Using the survey data from the United States General
+Social Survey (GSS) recorded in 2016, we constructed different models on
+6 factors and their relationship with total weekly hours of Internet
+use: age, race, sex, marital status, number of children, and happiness.
+
+Through examining the relationships between the variables and the weekly
+number of hours of Internet use, we found that young adults tend to use
+the Internet more than older adults. This may be due to physical,
+psychological, and social barriers when using the Internet. We also
+found that those who have never been married use the Internet more than
+others with different marital statuses. This could be related to age and
+the difference in reasons for using the Internet. Additionally, as
+social media is a large part of Internet usage, we found that the using
+these platforms have a negative impact on emotional health,
+demonstrating a possible correlation between high Internet usage and a
+low level of happiness. These findings are important because using the
+Internet more regularly can improve the lives of individuals for its
+convenience and its accessibility. It is beneficial because it allows
+for easier and instantaneous communication, for learning, for increasing
+access to services, for encouraging connections and decreasing
+isolation, and for gathering information (Lane 2022). However, the
+consequences of increased Internet usage, such as Internet addiction and
+mental health issues, should also be kept in mind. Our research on which
+population groups use the Internet the most in the US can lay the
+foundation for subsequent research investigating the pros and cons of
+Internet use on different population groups, and the ways in which the
+pros and cons affect those who use the Internet more.
+
+The remainder of this report is structured as follows: Section 2
+discusses the dataset of interest, including the methodology of the
+survey and its strengths and weaknesses, Section 3 presents the results
+through data visualizations, Section 4 discusses our findings, its
+weaknesses, and next steps, and Section 5 consists of the supplementary
+survey as an extension of the survey data to improve and enhance the
+study.
 
 \hypertarget{sec-data}{%
-\section{2 Data}\label{sec-data}}
+\section{Data}\label{sec-data}}
 
 \hypertarget{survey}{%
-\subsection{2.1 Survey}\label{survey}}
-
-Saku
+\subsection{Survey}\label{survey}}
 
 \hypertarget{key-features}{%
-\subsubsection{2.1.1 Key Features}\label{key-features}}
+\subsubsection{Key Features}\label{key-features}}
 
-Saku
+The General Social Survey (GSS) is a national survey conducted in the
+United States of America that aims to better understand trends in the
+American adult population's social characteristics and attitudes to
+better inform research and public policy ({``About the GSS,''} n.d.).
+Beginning in 1972, this interview-based survey is conducted biennially
+on five key themes: gender and marriage, current affairs, civil
+liberties, politics, and religion and spirituality ({``Key Trends,''}
+n.d.). The 2016 GSS is unique in that it also includes questions about
+Internet-usage behaviours, which is why our analysis focuses on the GSS
+of this year. In 2016, there is data for 2,867 respondents for 961
+variables.
 
 \hypertarget{methodology}{%
-\subsubsection{2.1.2 Methodology}\label{methodology}}
+\subsubsection{Methodology}\label{methodology}}
 
-Saku
+The GSS' target population is adults aged 18 years and older living in
+the United States. The sampling frame for the 2016 GSS is people living
+in the US aged 18+ who can speak English or Spanish and live in
+households ({``Frequently Asked Questions,''} n.d.). Thus, those living
+outside households (e.g.~in university dorms, nursing homes,
+institutions, military quarters) are not included in the GSS ({``GSS
+1972-2018 Cross-Section Codebook: Appendix a - Sampling Design and
+Weighting,''} n.d.). The frame was created using the NORC National
+Sampling Frame, which first uses US Census data to stratify US
+geographic regions by size and then chooses metropolitan areas and
+non-metropolitan counties within these regions, as the first stage of
+selection ({``GSS 1972-2018 Cross-Section Codebook: Appendix a -
+Sampling Design and Weighting,''} n.d.). In the second stage of
+selection, these metropolitan areas and non-metropolitan counties were
+stratified by race and income and further divided into blocks ({``GSS
+1972-2018 Cross-Section Codebook: Appendix a - Sampling Design and
+Weighting,''} n.d.). Then, the sample is gathered by interviewers
+beginning from the northwest corner of a given block and moving from
+household to household until the equal-sex quota has been filled ({``GSS
+1972-2018 Cross-Section Codebook: Appendix a - Sampling Design and
+Weighting,''} n.d.).
+
+Thus, the sample for the 2016 GSS was an area-probability sample
+gathered by the clustered sampling approach, as households are selected
+and then one random member from the household is selected to be included
+in the survey ({``GSS 1972-2018 Cross-Section Codebook: Appendix a -
+Sampling Design and Weighting,''} n.d.). A key tradeoff of this approach
+is that, while this method is much easier than solely random sampling,
+it can lead to bias in that there is more bias if the clusters are
+similar to each other.
+
+Non-response is handled by inputting it in the GSS dataset as one of the
+following options depending on the method of non-response: ``NA'', ``no
+answer'', ``do not know'', or ``skipped''.
 
 \hypertarget{strengths-weaknesses}{%
-\subsubsection{2.1.3 Strengths \&
-Weaknesses}\label{strengths-weaknesses}}
+\subsubsection{Strengths \& Weaknesses}\label{strengths-weaknesses}}
 
-Saku
+A strength of this 2016 GSS survey was that it was delivered both in
+English and in Spanish, allowing for a greater reach than had the survey
+just been conducted in English, like in the years previous to 2006
+({``GSS 1972-2018 Cross-Section Codebook: Appendix a - Sampling Design
+and Weighting,''} n.d.). Of the people who had been excluded from this
+survey due to the English-only delivery, Spanish-speakers made up the
+majority, so this dual language delivery addressed this key exclusion
+({``GSS 1972-2018 Cross-Section Codebook: Appendix a - Sampling Design
+and Weighting,''} n.d.).
 
-\hypertarget{questionnaire}{%
-\subsection{2.2 Questionnaire}\label{questionnaire}}
+A weakness of this sample is the lack of a gender variable, as the
+sample only provides a variable on sex. A gender variable would be more
+useful for data analysis, as it better reflects the respondent's lived
+experience. The lack of a gender variable that better accommodates for
+people's lived experience might lead to those who feel uncomfortable
+with the binary categories of sex to refrain from participating in the
+survey, leading to selection bias.
 
-Saku
+Another weakness of the 2016 GSS survey is that the interviewer
+physically fills out the responses for the respondent. This can
+potentially lead to measurement error. When the interviewer fills out
+the survey on behalf of the respondent, there may be a difference in the
+observed responses of the interviewer and the actual responses of the
+interviewee. This creates difficulty in verifying responses ({``For
+Survey Participants,''} n.d.).
+
+A third weakness of the survey is the role of selection bias that exists
+due to the inability to reach the entire population. The survey may also
+be susceptible to volunteering bias because the data is reliant on
+participants willingly providing their answers, which could lead to
+biased results.
+
+\hypertarget{sec-questionnaire}{%
+\subsection{Questionnaire}\label{sec-questionnaire}}
+
+A strength of the questionnaire was the clear wording of the question
+regarding Internet usage per week in hours. The survey question was
+formatted as follows: ``Not counting e-mail, about how many minutes or
+hours per week do you use the Web? (Include time you spend visiting
+regular web sites and time spent using interactive Internet services
+like chat rooms, Usenet groups, discussion forums, bulletin boards, and
+the like.)'' ({``GSS Data Explorer: NORC at the University of Chicago''}
+(n.d.)). The providing of examples was likely helpful in stimulating the
+respondents' memory of what exactly Internet usage can look like, as if
+one is flat out asked whether they use the Internet, it can be hard to
+conceptualize what that looks like.
+
+A key weakness of this questionnaire is the race variable, as it only
+allows for three options: ``Black'', ``White'', or ``Other'', which does
+not take into account the largest ethnic minority group, Hispanics and
+Latino Americans, as well as other ethnic groups, such as Asians and
+Indigenous Americans in the United States. In comparison, while not
+without fault itself, the US Census identifies 5 minimum categories of
+race (White, Black or African American, American Indian or Alaska
+Native, Asian, Native Hawaiian or Other Pacific Islander) and also
+allows for the reporting of more than one race (Bureau 2022). The
+questionnaire should at least have followed these US Census minimum race
+categories.
+
+Another weakness of this questionnaire is that questions are allowed
+non-responses. This results in truncated data, in which the dataset has
+been incompletely collected. Having no response for a question can only
+be observed as null, despite there being a possible actual value
+(Alexander 2023). There are a variety of reasons as to why a respondent
+may not want to answer a question, but can only be observed as a
+non-response by researchers to avoid biased assumptions and inaccurate
+results.
 
 \hypertarget{overview-of-data}{%
-\subsection{2.3 Overview of Data}\label{overview-of-data}}
+\subsection{Overview of Data}\label{overview-of-data}}
 
 \hypertarget{data-source}{%
-\subsubsection{2.3.1 Data Source}\label{data-source}}
+\subsubsection{Data Source}\label{data-source}}
 
-Max
+In this report, the 2867 observations from the 2016 United States
+General Social Survey are used. The survey data was obtained from the
+University of Chicago National Opinion Research Centre (NORC) ({``GSS
+Data Explorer: NORC at the University of Chicago,''} n.d.).
+
+This report was created using the R statistical programming language (R
+Core Team 2020). The here package was utilized to retrieve files from
+another folder within the same R project (Müller 2020). For the results
+and analysis of this report, all figures were created using the
+tidyverse package (Wickham et al. 2019). Additionally, the tables were
+created using the packages knitr (Xie 2023) and kableExtra (Zhu 2021),
+and the graphs were created using the packages lessR (Gerbing 2021),
+tidyr (Wickham, Vaughan, and Girlich 2023), and ggplot2 (Wickham 2016).
 
 \hypertarget{variables-of-interest}{%
-\subsubsection{2.3.2 Variables of
-Interest}\label{variables-of-interest}}
+\subsubsection{Variables of Interest}\label{variables-of-interest}}
 
-Max
+Our report selects 7 variables for analysis. We focus on 6 particular
+factors that we predicted affects the amount of Internet use: age, sex,
+race, number of children, marital status, and happiness. In this paper,
+we investigate the influence of these various factors on the total
+number of hours of weekly Internet usage. The packages tidyverse
+(Wickham et al. 2019), haven (Wickham, Miller, and Smith 2022), and
+reshape2 (Wickham 2007) were used to clean the dataset by grouping or
+converting the questionnaire responses into categorical or textual
+answers.
 
+\hypertarget{tbl-variables}{}
 \begin{table}
 
-\caption{A subset of key features}
+\caption{\label{tbl-variables}The Variables of Interest }The Variables of Study}
 \centering
-\begin{tabu} to \linewidth {>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedleft}X}
+\begin{tabu} to \linewidth {>{\raggedleft}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X>{\raggedright}X}
 \hline
-Age & Sex & Race & Highest Degree & Number of Children & Marital Status & Happiness Level & Weekly Internet Hours\\
+Weekly Internet Hours & Age & Sex & Race & Number of Children & Marital Status & Happiness Level\\
 \hline
-Ages 40 - 49 & Male & White & Bachelor's & 3 & Married & Pretty happy & 15\\
-Ages 60 - 69 & Male & White & High school & 0 & Never married & Pretty happy & 5\\
-Ages 70 - 79 & Male & White & Bachelor's & 2 & Married & Very happy & NA\\
-Ages 40 - 49 & Female & White & High school & 4 & Married & Pretty happy & 7\\
-Ages 50 - 59 & Female & White & Graduate & 2 & Married & Very happy & NA\\
-Ages 50 - 59 & Female & White & Associate/junior college & 2 & Married & Very happy & 2\\
-Ages 50 - 59 & Male & White & High school & 2 & Married & Pretty happy & 5\\
-Ages 21 - 29 & Female & Other & High school & 3 & Married & Very happy & NA\\
+15 & Ages 40 - 49 & Male & White & 3 & Married & Pretty happy\\
+5 & Ages 60 - 69 & Male & White & 0 & Never married & Pretty happy\\
+NA & Ages 70 - 79 & Male & White & 2 & Married & Very happy\\
+7 & Ages 40 - 49 & Female & White & 4 & Married & Pretty happy\\
+NA & Ages 50 - 59 & Female & White & 2 & Married & Very happy\\
+2 & Ages 50 - 59 & Female & White & 2 & Married & Very happy\\
+5 & Ages 50 - 59 & Male & White & 2 & Married & Pretty happy\\
 \hline
@@
 
-Table :)
+Table~\ref{tbl-variables} shows the first 10 rows of the cleaned
+dataset. The variables, Number of Children and Weekly Internet Hours,
+are recorded as a numerical value. Weekly Internet Hours has a maximum
+value of 168, as there are only 168 hours in a week. Age is also
+recorded as a numerical value, but is cleaned to represent ages in
+groups of ten years. The other variables, Sex, Race, Marital Status, and
+Happiness Level, are all recorded as a textual option for respondents to
+choose from.
 
@@
 
-\subcaption{\label{fig-agesidebyside-1}Subcaption}
+\subcaption{\label{fig-agesidebyside-1}Relationship between Age and Sex}
 \end{minipage}%
@@
 
-\subcaption{\label{fig-agesidebyside-2}Subcaption}
+\subcaption{\label{fig-agesidebyside-2}Relationship Between Age and
+Race}
 \end{minipage}%
 
-\caption{\label{fig-agesidebyside}Caption}
+\caption{\label{fig-agesidebyside}Relationship between Age and Sex and
+Age and Race}
 
@@
 
-Figure~\ref{fig-agesidebyside}
+Most of the respondents of the 2016 GSS are adults ranging from ages 21
+to 69 years old. The size of each age group between that range
+oscillates within the right skewed distribution. The largest age group
+respondent size is 50 to 59 years old. By graphing the variables, age
+and sex in Figure~\ref{fig-agesidebyside}, we observe that there are
+more female adults in each age group participating in this survey than
+there are male adults. The overall distribution is skewed to the right.
+The visualization of age and race in Figure~\ref{fig-agesidebyside}
+demonstrates that the respondents that identify with the White racial
+group comprises most of the respondent sample. This racial group is also
+shown to have a near-symmetrical distribution. Conversely, the other
+racial groups in this survey, Black and Other, are significantly the
+minority of the survey sample. The Black and Other racial groups are
+skewed to the right, illustrating that there are less individuals that
+identify with these racial groups in the older age groups. According to
+the 2020 US Census surveys, the most common racial group in America is
+White or Caucasian, which means that the 2016 GSS data on this group
+provides a relatively accurate representation of American society
+(Jensen 2022).
 
@@
 
-\caption{\label{fig-childsandmarital}Caption}
+\caption{\label{fig-childsandmarital}Relationship between Marital Status
+and Number of Children}
 
@@
 
-Figure~\ref{fig-childsandmarital}
+According to Figure~\ref{fig-childsandmarital}, respondents who are
+married have a right skew distribution of the number of children they
+have, where the mode of the data is having two children. As for
+individuals that responded as never having been married, the
+distribution was exponential, in which the mode of this distribution is
+having zero children. As the number of children increases, the number of
+individuals who have never been married decreases. The distribution of
+the other minority marital groups are skewed to the right. Overall, most
+survey respondents have zero children.
 
@@
 
-\caption{\label{fig-happiness}Caption}
+\caption{\label{fig-happiness}Happiness Level Responses from Survey
+Respondents}
 
@@
 
-Figure~\ref{fig-happiness}
+Figure~\ref{fig-happiness} demonstrates general happiness trends and
+exhibits a left skew distribution. This illustrates that a significant
+proportion of the respondents indicate that they are fairly happy and an
+adequate proportion indicate that they are very happy. With a limited
+number of options to measure happiness quantitatively, it is difficult
+to discern a distribution on varying levels of happiness.
 
 \hypertarget{results}{%
-\section{3 Results}\label{results}}
+\section{Results}\label{results}}
 
@@
 
-Figure~\ref{fig-ageandinternet} depicting the relationship between age
-and average weekly internet usage. The data on internet usage hours for
+Figure~\ref{fig-ageandinternet} depicts the relationship between age and
+average weekly Internet usage. The data on Internet usage hours for
 various age groups are averaged to reduce any bias due to selectively
@@
 with its peak occurring in the 21 to 29 age group, which has the highest
-internet usage of approximately 18 hours per week. Subsequently,
-internet usage gradually declines with age, with the lowest usage
+Internet usage of approximately 18 hours per week. Subsequently,
+Internet usage gradually declines with age, with the lowest usage
 recorded in the 89+ age group at an average of 2 hours per week. This
 graph indicates that young adults, particularly those aged 21 to 29,
-spend more time on the internet. As people age, their internet usage
+spend more time on the Internet. As people age, their Internet usage
 tends to decline gradually. The graph suggests a statistically
-significant correlation between age and internet usage, and the trend is
+significant correlation between age and Internet usage, and the trend is
 relatively clear.
@@
 Figure~\ref{fig-genderandinternet} illustrates the average weekly
-internet usage of two genders. Similarly to the age and internet usage
-graph, the data on internet usage hours for different genders are
+Internet usage of two sexes. Similar to the age and Internet usage
+graph, the data on Internet usage hours for different genders are
 averaged to minimize any volunteering bias. The data shows that there is
-no substantial difference between male and female internet usage. Female
+no substantial difference between male and female Internet usage. Female
 participants have an average of 12.9 hours per week spent on the
-internet, while male participants have an slightly higher average of
-13.3 hours per week spent on the internet. However, the gender selection
-in this survey is limited, and further discussion regarding this
-limitation can be found in the ethics and bias section
-Section~\ref{sec-bias}.
+Internet, while male participants have a slightly higher average of 13.3
+hours per week spent on the Internet. However, the gender selection in
+this survey is limited, and further discussion regarding this limitation
+can be found in the ethics and bias section Section~\ref{sec-bias}.
 
@@
 
-Figure~\ref{fig-raceandinternet} displays the average weekly internet
+Figure~\ref{fig-raceandinternet} displays the average weekly Internet
 usage of individuals belonging to different races. Based on the data, we
 can observe that individuals who do not identify as either Black or
-White have the highest internet usage, with an average of 15.5 hours per
-week. African American individuals have a similar level of internet
-usage, also averaging 15.2 hours per week. In contrast, white
-individuals tend to have the lowest internet usage, with an average of
-12.3 hours per week.
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-personalincomeandinternet-1.pdf}
-
-}
-
-\caption{\label{fig-personalincomeandinternet}Average Weekly Total of
-Internet Use by Personal Income}
-
-\end{figure}
-
-Max - might emit\ldots{}
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-familyincomeandinternet-1.pdf}
-
-}
-
-\caption{\label{fig-familyincomeandinternet-1}Average Weekly Total of
-Internet Use by Family Income}
-
-\end{figure}
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-familyincomeandinternet-2.pdf}
-
-}
-
-\caption{\label{fig-familyincomeandinternet-2}Average Weekly Total of
-Internet Use by Family Income}
-
-\end{figure}
-
-Max - might emit
+White have the highest Internet usage, with an average of 15.5 hours per
+week. Black individuals have a similar level of Internet usage, also
+averaging 15.2 hours per week. In contrast, White individuals tend to
+have the lowest Internet usage, with an average of 12.3 hours per week.
 
@@
 
-Max
+Figure~\ref{fig-childrenandinternet} shows the relationship between
+respondents with a specific number of children and their weekly total
+hours of Internet use. Respondents that do not have any children are the
+group that uses the Internet the most during the week. Their average
+amount of hours of weekly Internet use is approximately 16.5 hours. The
+data demonstrates that there is an inverse relationship between the two
+variables. This means that there is a gradual decrease of Internet use
+hours as the number of children increases. The group that uses the least
+amount of hours, with an average of approximately 1.5 hours of Internet
+use weekly, are those with 7 children. However, the second largest group
+that uses the Internet are those that reported having 8 children or
+more, making this group an outlier.
 
@@
 Figure~\ref{fig-maritalandinternet} displays the relationship between
-marital status and internet usage in 2016. In accordance with popular
-opinion, people who have never been married use the Internet the most.
-Most notably, people who are widowed use the Internet the least, perhaps
-due to the correlation between age and widowhood.
-
-\begin{figure}
-
-{\centering \includegraphics{paper_files/figure-pdf/fig-degreeandinternet-1.pdf}
-
-}
-
-\caption{\label{fig-degreeandinternet}Weekly Total of Internet Use by
-Highest Education Obtained}
-
-\end{figure}
-
-Figure~\ref{fig-degreeandinternet} displays the relationship between
-highest level of education obtained by the respondent and internet usage
-in 2016. Those who have completed a less than high school degree use the
-internet the least.
+marital status and Internet usage in 2016. In accordance with popular
+opinion, people who have never been married use the Internet the most,
+with an average of around 17.5 hours per week. Most notably, people who
+are widowed use the Internet the least, with an average of around 9.5
+hours per week, perhaps due to the correlation between age and
+widowhood. The graph suggests a significant difference in the Internet
+use between these two population groups, with a difference of 8 hours
+between the two.
 
@@
 Figure~\ref{fig-happyandinternet} displays the relationship between
-perceived level of happiness and internet usage in 2016. There seems to
-be a direct decrease in internet usage the more happy the respondent
-measures themselves to be, with a difference of 2.5 hours between the
-happiest respondents and least happy respondents.
+perceived level of happiness and Internet usage in 2016. People who
+reported the lowest level of happiness had the highest Internet usage,
+with an average of around 14 hours per week. People who reported the
+highest level of happiness had the lowest Internet usage, with an
+average of around 12 hours per week. There seems to be a direct decrease
+in Internet usage the more happy the respondent measures themselves to
+be, with a difference of 2 hours between the happiest respondents and
+least happy respondents.
 
 \hypertarget{sec-discussion}{%
-\section{4 Discussion}\label{sec-discussion}}
+\section{Discussion}\label{sec-discussion}}
 
 \hypertarget{sec-first-point}{%
-\subsection{4.1 First discussion point}\label{sec-first-point}}
+\subsection{Aging Reduces the Amount of Hours Spent Using the
+Internet}\label{sec-first-point}}
+
+Based on the results, we find that as aging increases, the amount of
+weekly total hour Internet use decreases. As shown in
+Figure~\ref{fig-ageandinternet}, the majority of respondents that have
+the highest number of weekly hours of Internet use are those between the
+ages of 18 and 39 years old. The three age groups within this range have
+the three largest Internet usages. By observing the tail of the
+right-skewed distribution in Figure~\ref{fig-ageandinternet}, the graph
+illustrates that as the age of respondents increases beginning from the
+age range of 20-29 years old, the use of the Internet reduces. In this
+era of developing technology and digital services, the Internet has
+become a widely used source for information, commerce, communication,
+and entertainment. According to our results, many young adults are
+commonly online. This may be because they have the functional
+capabilities of learning how to use the Internet and actually using the
+Internet. Its ease and convenience allows users to have access to
+instant information and communication, popularly used by young adults.
+In comparison, those of older age tend to use the Internet less. The
+reason for this may be because, as individuals age, they experience
+declining changes in their physical, mental, and social abilities,
+affecting their functional capacities. Research has shown that 23\% of
+older adults indicate that having a physical or health condition makes
+reading difficult or challenging (Smith 2019). This shows that those in
+older age groups have barriers when it comes to using the Internet.
+Although using the Internet is valuable to those of older age, as it
+helps them connect with family members remotely and experience
+socialization, the factors that make using the Internet challenging
+keeps them from increasing their weekly use. Many older adults have
+expressed that, when using technology and digital services, they would
+need assistance (Smith 2019). Despite seniors being less likely than the
+rest of the population to go online, once they understand how to use it,
+it becomes a part of their everyday lives. Research has shown that 71\%
+of seniors go online almost everyday and 11\% go online three to five
+times weekly (Smith 2019). While many older adults understand the
+beneficial aspect of the Internet, there still remains many non-users of
+the Internet due to disabilities that come with aging (Smith 2019).
 
 \hypertarget{sec-second-point}{%
-\subsection{4.2 Second discussion point}\label{sec-second-point}}
+\subsection{Marriage and Number of Children Reduces the Amount of Hours
+Spent Using the Internet}\label{sec-second-point}}
+
+\hypertarget{marital-status}{%
+\subsubsection{Marital Status}\label{marital-status}}
+
+As seen in Figure~\ref{fig-maritalandinternet}, people who have never
+married use the Internet significantly more than those who are married
+or who are widowed. This trend could partially be explained by the
+correlation between age and being married, as those who have never been
+married are more likely to be younger. In the United States in 2016, at
+the time this survey data was collected, the median age of marriage was
+28 years old for women and 30 years old for men ({``Median Age at First
+Marriage (Women),''} n.d.). This statistic is consistent with the
+findings of Figure~\ref{fig-ageandinternet}, which shows that Internet
+usage is highest for people aged 21 to 29, people who are just prior to
+the median age of marriage. This explanation is supported by the finding
+that widowed people use the Internet the least, out of all of the
+marital categories. Because widowhood is more likely in people who are
+older, the correlation between age and Internet use is further reflected
+here (Isherwood, King, and Luszcz 2017). Thus, the relationship between
+marriage versus non-marriage and Internet use, in which those who have
+never been married use the Internet more than those who are married, is
+related to the inverse relationship between age and amount of average
+Internet use stated in Section 4.1 above.
+
+This trend of younger and non-married people using the Internet more
+than older, married people could be further explained by the use of
+online and digital dating apps by younger, non-married people as ways to
+connect with people romantically. The United States is one of the
+countries that uses online dating sites and apps the most, suggesting
+that online dating is normalized in American culture and partially
+explaining why younger, non-married people use the Internet much more
+than their older, married counterparts (Buchholz 2023). The widespread
+usage of handheld mobile devices that has become the norm for all age
+groups, but especially younger people who are more likely to use social
+media and online dating apps, furthers this.
+
+A third contributing factor to this trend could be that non-married
+individuals feel more isolated due to not meeting societal norms of
+marriage and turn to the Internet to seek connections and community.
+People who live in societies in which marriage is socially expected,
+such as the United States, can feel isolated, for which using the
+Internet can help them feel a sense of belonging that they find missing
+in their lives (Himawan et al. 2021).
+
+\hypertarget{number-of-children}{%
+\subsubsection{Number of Children}\label{number-of-children}}
+
+Figure~\ref{fig-childrenandinternet} demonstrates the relationship
+between number of children of respondents and average weekly Internet
+use. This graph shows that people with no children use the Internet more
+than people who have children. Like Section 4.2.1 above, this could be
+due to the correlation between age and having children: those who are
+older are more likely to have children than those who are younger. The
+median age at which women have children is 30 years of age, which is
+consistent with the findings of Figure~\ref{fig-ageandinternet}, which
+states that people in their 20s use the Internet the most (Morse 2022).
+This general inverse relationship between number of children and
+Internet use, is related to the inverse relationship between age and
+amount of average Internet use stated in Section 4.1 above. The outlier
+of the ``8+'' children category has a high Internet usage because there
+were only 6 people who responded about their Internet usage in that
+category (compared to the approximately 500 people who responded about
+their Internet usage in the ``0'' children category), such that the
+result was skewed by one participant who reported 60 hours of Internet
+use.
+
+This trend could also be explained by the amount of personal time that
+people have for themselves. Personal use is one of the main activities
+of Internet use (including instant messaging and social media), and
+people with children are less likely to have time for themselves as they
+spend time caring for their children (Petrosyan 2023). This likely
+increases with more children. Thus, the relatively inverted relationship
+between number of children and Internet use could be partially explained
+by the inverted relationship between number of children and personal
+time.
+
+However, the Internet has increasingly come to be a key resource for
+parenting, both for getting information and for receiving support
+(Duggan et al. 2015). This explains why average Internet use is
+relatively similar across people with 1 child to 5 children.
 
 \hypertarget{sec-third-point}{%
-\subsection{4.3 Third discussion point}\label{sec-third-point}}
+\subsection{Happiness Reduces the Amount of Hours Spent Using the
+Internet}\label{sec-third-point}}
+
+In a previous study, we found a potential correlation between happiness
+and Internet usage. Specifically, individuals who reported lower
+Internet usage tended to have higher levels of happiness. There are a
+few reasons that may contribute to this finding.
+
+We suspect this finding may be attributed to various factors related to
+social media usage, given that people spend an average of 2 hours and 31
+minutes daily on social media (Georgiev 2023). Our secondary research
+indicates that certain aspects of the Internet, such as social media,
+can negatively impact psychological health. Excessive use of social
+media can result in addiction, anxiety, depression, or isolation.
+Furthermore, social media can become a substitute for real-life social
+interaction, causing individuals to feel lonely and disconnected.
+Comparing oneself unfavourably with Internet social figures can also
+lead to low self-esteem and negative body image, while cyberbullying can
+have potential mental health implications for individuals who spend long
+hours on the Internet. A study by the University of Pennsylvania in 2018
+found that reducing social media use to 30 minutes a day resulted in a
+significant reduction in anxiety, depression, loneliness, and sleep
+problems (Robinson and Smith 2023).
+
+Additionally, research suggests that spending more time online can make
+children less happy with their lives. For instance, a study by the
+University of Sheffield concluded that spending an extra hour a day on
+social networks reduces the probability of being completely happy with
+life overall by approximately 14 percentage points (Sheffield 2017).
+Thus, we have reason to believe that Internet usage, particularly social
+media usage, can have a negative impact on happiness levels to some
+extent and affect the relationship between happiness and Internet usage.
+
+Another factor that could contribute to the correlation between
+happiness and Internet usage is a fulfilling real life. Engaging in
+offline activities, such as spending time with loved ones, pursuing
+hobbies, or achieving personal goals, can be more rewarding than
+spending time online. This can lead individuals to prioritize fulfilling
+activities over aimless scrolling through the Internet and decrease
+their need for validation or connection through social media and other
+online platforms. Thus, individuals who are fulfilled in their offline
+lives may have lower Internet usage hours and higher happiness levels.
+
+\hypertarget{sec-weaknessesandnextsteps}{%
+\subsection{Weaknesses and Next
+Steps}\label{sec-weaknessesandnextsteps}}
 
 \hypertarget{sec-weaknesses}{%
-\subsection{4.4 Weaknesses and next steps}\label{sec-weaknesses}}
+\subsubsection{Weakness}\label{sec-weaknesses}}
+
+A key weakness in our analysis was that we removed non-responses from
+our data, which may have made our data for Internet use not as accurate
+in reflecting what the actual population's Internet use looks like. A
+central reason as to why participant's may have chosen not to respond to
+the question about Internet use could be embarrassment: admitting that
+one spends too much time on the Internet could be embarrassing, so those
+who have higher Internet usage are more likely not to respond to this
+question. This is a very real concern as Internet addiction is emerging
+rapidly in our increasingly digital world, and several countries have
+even identified it as a public health concern (Cash et al. 2012).
+
+Another weakness in our analysis is the self-reported nature of the
+results, meaning there was some bias in questions with ambiguous word
+choice, such as our happiness variable. The definition of the different
+response options to the happiness variable survey question of ``not so
+happy'', ``fairly happy'', and ``very happy'' will vary depending on the
+individual, as well as the day or time of day. Thus, our analysis of the
+relationship between happiness and Internet use may be biased.
+
+\hypertarget{next-steps}{%
+\subsubsection{Next Steps}\label{next-steps}}
+
+To address our second identified weakness in
+Section~\ref{sec-weaknesses} above, implementing a supplementary survey
+with more detailed questions, particularly about race and gender (as
+mentioned in Section~\ref{sec-questionnaire}) and more straightforward
+question answers (e.g.~a number scale for happiness variable) would
+allow for more in-depth analysis.
+
+In addition, conducting further research on the different uses of the
+Internet based on population groups would be a reasonable next step, now
+that we have determined which population groups use the Internet the
+most and the least.
+
+Finally, looking at how COVID-19 impacted Internet usage would be a
+particularly interesting avenue of research to pursue, especially with
+the increase in online activities (e.g.~work from home, online classes,
+widespread use of Zoom, etc.). It would be interesting to compare our
+analysis of American population groups that used the Internet the most
+in 2016, with 2020 (during the COVID-19 pandemic) and with 2022
+(post-COVID-19 pandemic).
 
 \hypertarget{sec-bias}{%
-\subsection{4.5 Ethics and Bias}\label{sec-bias}}
+\subsection{Ethics and Bias}\label{sec-bias}}
 
@@
 specific age group, our analysis may be biased with respect to the age
-factor. Gss also claimed to be strictly voluntary. While this approach
+factor. GSS also claimed to be strictly voluntary. While this approach
 supports research ethics by respecting individuals' autonomy and right
-to privacy, it can also result in volunteer bias. GSS sample are from a
-mix of urban, suburban, and rural geographic areas, but only a few
-thousand respondents are interviewed in the main study. The small sample
-size may be lead to chance findings. It is likely not statistically
-significant enough. We also suspect potential sampling bias may screw
-our end result. However, with not enough information disclosed, we are
-unable to confirm that. The gender and race options provided by the GSS
-survey are limited. Participants are only given the options of selecting
-either ``Female'' or ``Male'' for gender, and ``Blacks,'' ``Whites,'' or
-``Others'' for race. This narrow selection does not provide an adequate
-range of options for survey participants.
+to privacy, it can also result in volunteer bias. The GSS sample is from
+a combination of urban, suburban, and rural geographic areas, but only a
+few thousand respondents are interviewed in the main study. The small
+sample size may lead to chance findings. We also suspect potential
+sampling bias may affect our end results. However, with not enough
+information disclosed, we are unable to confirm that. The gender and
+race options provided by the GSS survey are limited. Participants are
+only given the options of selecting either ``Female'' or ``Male'' for
+gender, and ``Black,'' ``White,'' or ``Other'' for race. This narrow
+selection does not provide an adequate range of options for survey
+participants.
 
 \hypertarget{appendix}{%
-\section*{5 Appendix}\label{appendix}}
-\addcontentsline{toc}{section}{5 Appendix}
-
-\hypertarget{additional-details}{%
-\section{6 Additional details}\label{additional-details}}
+\section{Appendix}\label{appendix}}
 
 \hypertarget{references}{%
-\section{7 References}\label{references}}
+\section*{References}\label{references}}
+\addcontentsline{toc}{section}{References}
+
+\hypertarget{refs}{}
+\begin{CSLReferences}{1}{0}
+\leavevmode\vadjust pre{\hypertarget{ref-citem1}{}}%
+{``A Short History of the Internet.''} 2020. National Science; Media
+Museum.
+\url{https://www.scienceandmediamuseum.org.uk/objects-and-stories/short-history-internet\#:~:text=Consequently\%2C\%20the\%20number\%20of\%20websites,around\%2010\%20million\%20global\%20users}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite3}{}}%
+{``About the GSS.''} n.d. NORC.
+\url{https://gss.norc.org/About-The-GSS}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite15}{}}%
+Alexander, Rohan. 2023. {``Telling Stories with Data.''}
+\url{https://tellingstorieswithdata.com/06-farm.html\#measurement}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite21}{}}%
+Buchholz, Katharina. 2023. {``How the World Dates Online.''}
+\emph{Statista}.
+\url{https://www.statista.com/chart/24165/online-dating-penetration-rate-revenue-selected-countries/\#:~:text=The\%20United\%20States\%20is\%20the,of\%20\%242.5\%20billion\%20in\%202023.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite14}{}}%
+Bureau, US Census. 2022. {``About the Topic of Race.''}
+\url{https://www.census.gov/topics/population/race/about.html}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite26}{}}%
+Cash, Hilarie, Cosette D Rae, Ann H Steel, and Alexander Winkler. 2012.
+{``Internet Addiction: A Brief Summary of Research and Practice.''}
+\emph{Current Psychiatry Reviews}.
+\url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC3480687/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite25}{}}%
+Duggan, Maeve, Amanda Lenhart, Cliff Lampe, and Nicole B. Elisson. 2015.
+{``Parents and Social Media.''} Pew Research Center.
+\url{https://www.pewresearch.org/internet/2015/07/16/parents-and-social-media/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite13}{}}%
+{``For Survey Participants.''} n.d. NORC.
+\url{https://gss.norc.org/For-Survey-Participants}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite5}{}}%
+{``Frequently Asked Questions.''} n.d. NORC.
+\url{https://gss.norc.org/faq}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-citea1}{}}%
+Georgiev, Deyan. 2023. {``How Much Time Do People Spend on Social Media
+in 2023?''} Techjury.
+\url{https://techjury.net/blog/time-spent-on-social-media/\#gref}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-lessR}{}}%
+Gerbing, David W. 2021. {``Enhancement of the Command-Line Environment
+for Use in the Introductory Statistics Course and Beyond.''}
+\emph{Journal of Statistics and Data Science Education} 29 (3): 251--56.
+\url{https://doi.org/10.1080/26939169.2021.1999871}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite6}{}}%
+{``GSS 1972-2018 Cross-Section Codebook: Appendix a - Sampling Design
+and Weighting.''} n.d. \url{https://gss.norc.org/Get-Documentation}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-gss}{}}%
+{``GSS Data Explorer: NORC at the University of Chicago.''} n.d. NORC.
+\url{https://gssdataexplorer.norc.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite22}{}}%
+Himawan, Karel Karsten, Mair Underwood, Matthew Bambling, and Sisira
+Edirippulige. 2021. {``Being Single When Marriage Is the Norm: Internet
+Use and the Well-Being of Never-Married Adults in Indonesia - Current
+Psychology.''} \emph{Current Psychology}. Springer US.
+\url{https://link.springer.com/article/10.1007/s12144-021-01367-6}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite20}{}}%
+Isherwood, L. M., D. S. King, and M. A. Luszcz. 2017. {``Widowhood in
+the Fourth Age: Support Exchange, Relationships and Social
+Participation: Ageing \&Amp; Society.''} \emph{Ageing \& Society}.
+Cambridge University Press.
+\url{https://www.cambridge.org/core/journals/ageing-and-society/article/abs/widowhood-in-the-fourth-age-support-exchange-relationships-and-social-participation/357209AB1A6F356266FEEA0B7B604A9D}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-citem3}{}}%
+Jensen, Eric. 2022. {``The Chance That Two People Chosen at Random Are
+of Different Race or Ethnicity Groups Has Increased Since 2010.''} US
+Census.
+\url{https://www.census.gov/library/stories/2021/08/2020-united-states-population-more-racially-ethnically-diverse-than-2010.html}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite4}{}}%
+{``Key Trends.''} n.d. \emph{NORC}.
+\url{https://gssdataexplorer.norc.org/trends}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-citem2}{}}%
+Lane, Anna Beth. 2022. {``14 Ways the Internet Improves Our Lives.''}
+Community Tech Network.
+\url{https://communitytechnetwork.org/blog/14-ways-the-internet-improves-our-lives/\#:~:text=Not\%20only\%20is\%20access\%20to,with\%20large\%20numbers\%20of\%20people}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite19}{}}%
+{``Median Age at First Marriage (Women).''} n.d. Population Reference
+Bureau.
+\url{https://www.prb.org/usdata/indicator/marriage-age-women/snapshot/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite23}{}}%
+Morse, Anne. 2022. {``Stable Fertility Rates 1990-2019 Mask Distinct
+Variations by Age.''} US Census Bureau.
+\url{https://www.census.gov/library/stories/2022/04/fertility-rates-declined-for-younger-women-increased-for-older-women.html}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-here}{}}%
+Müller, Kirill. 2020. \emph{Here: A Simpler Way to Find Your Files}.
+\url{https://CRAN.R-project.org/package=here}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-cite24}{}}%
+Petrosyan, Ani. 2023. {``Internet Activities of u.s. Users 2021.''}
+\emph{Statista}.
+\url{https://www.statista.com/statistics/183910/internet-activities-of-us-users/\#:~:text=As\%20of\%20November\%202021\%2C\%20it,the\%20country\%20used\%20messaging\%20services.}
+
+\leavevmode\vadjust pre{\hypertarget{ref-R}{}}%
+R Core Team. 2020. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-citea2}{}}%
+Robinson, Lawrence, and Melinda Smith. 2023. {``Social Media and Mental
+Health.''} HelpGuide.org.
+\url{https://www.helpguide.org/articles/mental-health/social-media-and-mental-health.htm\#:~:text=A\%202018\%20University\%20of\%20Pennsylvania,to\%20improve\%20your\%20mental\%20health}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-citea3}{}}%
+Sheffield, University of. 2017. {``More Time Spent Online Makes Children
+Less Happy with Their Lives, Research Finds.''} \emph{More Time Spent
+Online Makes Children Less Happy with Their Lives, Research Finds -
+Archive - News Archive - The University of Sheffield}.
+\url{https://www.sheffield.ac.uk/news/nr/social-media-economics-research-happiness-1.694959}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-citem4}{}}%
+Smith, Aaron. 2019. {``Attitudes, Impacts, and Barriers to Adoption.''}
+Pew Research Center.
+\url{https://www.pewresearch.org/internet/2014/04/03/attitudes-impacts-and-barriers-to-adoption/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-reshape2}{}}%
+Wickham, Hadley. 2007. {``Reshaping Data with the {reshape} Package.''}
+\emph{Journal of Statistical Software} 21 (12): 1--20.
+\url{http://www.jstatsoft.org/v21/i12/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-ggplot2}{}}%
+---------. 2016. \emph{Ggplot2: Elegant Graphics for Data Analysis}.
+Springer-Verlag New York. \url{https://ggplot2.tidyverse.org}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tidyverse}{}}%
+Wickham, Hadley, Mara Averick, Jennifer Bryan, Winston Chang, Lucy
+D'Agostino McGowan, Romain François, Garrett Grolemund, et al. 2019.
+{``Welcome to the {tidyverse}.''} \emph{Journal of Open Source Software}
+4 (43): 1686. \url{https://doi.org/10.21105/joss.01686}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-haven}{}}%
+Wickham, Hadley, Evan Miller, and Danny Smith. 2022. \emph{Haven: Import
+and Export 'SPSS', 'Stata' and 'SAS' Files}.
+\url{https://CRAN.R-project.org/package=haven}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-tidyr}{}}%
+Wickham, Hadley, Davis Vaughan, and Maximilian Girlich. 2023.
+\emph{Tidyr: Tidy Messy Data}.
+\url{https://CRAN.R-project.org/package=tidyr}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-knitr}{}}%
+Xie, Yihui. 2023. \emph{Knitr: A General-Purpose Package for Dynamic
+Report Generation in r}. \url{https://yihui.org/knitr/}.
+
+\leavevmode\vadjust pre{\hypertarget{ref-kableExtra}{}}%
+Zhu, Hao. 2021. \emph{kableExtra: Construct Complex Table with 'Kable'
+and Pipe Syntax}. \url{https://CRAN.R-project.org/package=kableExtra}.
+
+\end{CSLReferences}
 

### 2023-03-16 outputs/paper/paper.qmd

@@
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-  geom_bar(position = "dodge2")
+  geom_bar(position = "dodge2")+
+  labs(x = "Age", y = "Count", fill="Sex")
 
@@
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-  geom_bar(position = "dodge2")
+  geom_bar(position = "dodge2")+
+  labs(x = "Age", y = "Count", fill="Race")
 ```

### 2023-03-16 outputs/paper/paper.qmd
Adjusting the labels for graphs on the quarto document

--- 2023-03-16 outputs/paper/paper.qmd
@@
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-  geom_bar(position = "dodge2")
+  geom_bar(position = "dodge2")+
+  labs(x = "Age", y = "Number of Respondents", fill="Sex")
 
@@
   theme(axis.text.x = element_text(angle = 45,hjust=1)) +
-  geom_bar(position = "dodge2")
+  geom_bar(position = "dodge2")+
+  labs(x = "Age", y = "Number of Respondents", fill="Race")
 ```
@@
   geom_bar(position = "dodge2")
+  labs(x = "Number of Children", y = "Number of Respondents", fill="Marital Status")
 ```

### 2023-03-16 outputs/paper/paper.qmd
add google forms link to the appendix
adjusted the graph labels for childs and marital

@@
   ggplot(mapping = aes(x = childs, fill = marital)) + 
-  geom_bar(position = "dodge2")
+  geom_bar(position = "dodge2") +
   labs(x = "Number of Children", y = "Number of Respondents", fill="Marital Status")
@@
 
+Please find our supplementary survey to the GSS 2016 questionnaire at the following link: https://docs.google.com/forms/d/e/1FAIpQLSe0H6LMKnAehmWwiag4u4cBW27ttiRh_kY1SfmOc7pQWlNrrQ/viewform?usp=sf_link
+
 # References

### 2023-03-16 outputs/paper/paper.qmd
Final edits to the quarto document - adding supplementary survey link in appendix

@@
 
+\newpage
+
 ```{r}
@@
 With a limited number of options to measure happiness quantitatively, it is difficult to discern a distribution on varying levels of happiness.
+
+\newpage
 
@@
 In contrast, White individuals tend to have the lowest Internet usage, with an average of 12.3 hours per week.
+
+\newpage
 
@@
 The graph suggests a significant difference in the Internet use between these two population groups, with a difference of 8 hours between the two.
+
+\newpage
 
@@
 
+\newpage
+
 # Appendix
 
-Please find our supplementary survey to the GSS 2016 questionnaire at the following link: https://docs.google.com/forms/d/e/1FAIpQLSe0H6LMKnAehmWwiag4u4cBW27ttiRh_kY1SfmOc7pQWlNrrQ/viewform?usp=sf_link
+Please find our supplementary survey to the GSS 2016 questionnaire at the following footnote link.^[https://docs.google.com/forms/d/e/1FAIpQLSe0H6LMKnAehmWwiag4u4cBW27ttiRh_kY1SfmOc7pQWlNrrQ/viewform?usp=sf_link]
+
+\newpage
 
